### 2023-12-29 paper/paper.tex
add paper text

% \documentclass[ams]{U-AizuGT}
\documentclass{jarticle}
% \usepackage{pifont}
% \usepackage{graphicx}
% \usepackage{cite}

\bibliographystyle{ieice}

\author{Ryuki Hiwada}
% \studentid{s1280076}
% \supervisor{Naohito Nakasato}
\title{Domain Specific Language for high performance computing}
\begin{document}
\maketitle
\section{Introduction}
test
\section{Abstruct}
\section{Conclusion}
\section{Acknowledgement}
\bibliography{biblist}

\end{document}

### 2023-12-29 dsl/gen/Var.py

@@ -7,8 +7,8 @@ import sympy
 # type_name = 'F64'
 # vec_name = 'vec3'
 # var_name = 'xi'
-# SIMD = 'AVX2'
-SIMD  = None
+SIMD = 'AVX2'
+# SIMD  = None
 class Variable:
     struct_name = ""
     memb_name = ""
@@ -101,10 +101,6 @@ class Variable:
             s = check_pat.group()
             self.name = s
             self.symbol = sympy.sympify(s)
-            if self.struct_name != "":
-                self.tmp_name = s + '_tmp'
-            else:
-                self.tmp_name = s
 
     def typeinfo_assign_(self, other):
         self.type_name = other.type_name
@@ -137,7 +133,7 @@ class Variable:
     def get_tmp_name(self, i):
 
         if SIMD:
-            ret_name = self.tmp_name
+            ret_name = self.name + '_tmp'
 
             if self.vec == 1:
                 return ret_name 
@@ -145,7 +141,7 @@ class Variable:
             return ret_name + f'_v{i}'
         else:
 
-            ret_name = self.name
+            ret_name = self.name + '_tmp'
             if self.index_name != '':
                 ret_name += f'[{self.index_name}]'
                 if self.vec == 1:

### 2024-01-05 paper/clean_copy/paper.tex
laptop 20240105

\documentclass[ams]{U-AizuGT}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{cite}

\bibliographystyle{ieice}
\author{Ryuki Hiwada}
\studentid{s1280076}
\supervisor{Naohito Nakasato}
\title{Domain Specific Language for high performance computing}
\begin{document}
\maketitle
\section{Abstract}
\section{Introduction}
\subsection{Background}
In astrophysics and astronomy, to numerically calculate 
the dynamical evolution of N particles interacting gravitationally, 
N-body simulations are required. Figure 1 shows the equation for 
interparticle interactions in N-body simulations. If the equation 
is naively computed, the time complexity of calculation of 
interparticle interactions is \begin{math}O(N^2) \end{math}, where N is the number of
particles. Therefore, parallelization is required to speed up 
numerical simulations. To write a parallelized code for a numerical
simulation, a user needs to understand the architecture of computer
systems in detail. If a parallelized code is automatically
generated by only describing the formulas and data of the numerical
simulation, the above problems are solved.

\section{Conclusion}
\section{Acknowledgement}
\bibliography{biblist}

\end{document}

### 2024-01-05 paper/paper.tex
laptop 20240105

@@
 % \documentclass[ams]{U-AizuGT}
-\documentclass{jarticle}
+\documentclass[twocolumn, a4j]{article}
 % \usepackage{pifont}
@@
 
+% \twocolumn[
 \bibliographystyle{ieice}
-
 \author{Ryuki Hiwada}
@@
 % \supervisor{Naohito Nakasato}
+% ]
 \title{Domain Specific Language for high performance computing}
@@
 \maketitle
+\section{Abstract}
 \section{Introduction}
-test
-\section{Abstruct}
+\subsection{Background}
+In astrophysics and astronomy, to numerically calculate the dynamical 
+evolution of N particles interacting gravitationally, N-body simulations 
+are required. Figure 1 shows the equation for interparticle interactions 
+in N-body simulations. If the equation is naively computed, the time
+complexity of calculation of interparticle interactions is 
+\begin{math}O(N^2) \end{math}, where 
+N is the number of particles. Therefore, parallelization is required to
+speed up numerical simulations. To write a parallelized code for a 
+numerical simulation, a user needs to understand the architecture of 
+computer systems in  detail. If a parallelized code is automatically
+generated by only describing the formulas and data of the numerical
+simulation, the above problems are solved. To realize the parallelization,
+we will develop Domain Specific Language \lparen DSL \rparen, which is a 
+programming language specialized to a domain, for example, SQL and HTML.
+\subsection{implemented DSL}
+
+\subsection{parallelization}
+
+\subsection{Aim of this paper}
+
+\section{Method}
+\subsection{Use Sympy for DSL development.}
+
 \section{Conclusion}
@@
 \bibliography{biblist}
-
 \end{document}

### 2024-01-05 dsl/gen/gravity_code.hpp

@@ -36,14 +36,8 @@ int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3],
          x0_tmp_v0 = _mm256_sub_pd(xj_tmp_v0, xi_tmp_v0);
          x0_tmp_v1 = _mm256_sub_pd(xj_tmp_v1, xi_tmp_v1);
          x0_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
-         ai_tmp_v0 = _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(g_tmp, mass_tmp), x0_tmp_v0),
-                      _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v0, x0_tmp_v0))), 
-                      _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v0, x0_tmp_v0))), 
-                                    _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v0, x0_tmp_v0))))));
-
-   
-         ai_tmp_v1 = _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(g_tmp, mass_tmp), x0_tmp_v1), 
-         _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1))), _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1))), _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1))))));
[…]

### 2024-01-05 dsl/gen/pykg.py

@@ -219,7 +219,6 @@ def EPI_load(v, i):
 
 #TODO 単精度少数の場合も
 def avx2_load(v, i):
-
     var_name = v.name
     tmp_name = v.get_tmp_name(i)
     
@@ -557,8 +556,6 @@ def type_inference(expr_list, name_variable_map):
             elif type(arg) in operator_list or arg is Integer(-1) or arg is Rational(1, 2) or type(arg) is Integer:
                 continue
 
-            
-                
             else:
                 #エラー
                 print('error', arg)
@@ -608,9 +605,7 @@ def main():
 
     # check_name_table(name_variable_map)
     #type_inferenceのテスト用
-    # check_type_infer(prim_map)
-
-    
+    # check_type_infer(prim_map) 
 
     # 木構造のチェック
     check_tree(biexpr_list)

### 2024-01-05 paper/paper.tex
desk

--- 2023-12-29 paper/paper.tex
@@
 \maketitle
+\section{Abstract}
 \section{Introduction}
-test
-\section{Abstruct}
+\subsection{Background}
+
+天文物理学や天文学において、重力相互作用するN個の粒子の力学的な進化を数値的に計算するには、N体シミュレーションが必要になる。N体シミュレーションの相互作用を求める式はfigure1に示す。
+この計算にはナイーブな実装の場合、粒子の数Nに対してO(N^2)で計算量が増加していく。したがって、高速に計算するための並列化が求められる。だが、プログラムを並列化するにはコンピュータシステム
+のアーキテクチャを詳細に理解する必要がある。もし並列化コードを式と粒子のデータを記述するだけで自動的に生成することができたら、上の問題は解決する。上の解決方法を実現するために、
+私たちはPKGというDomain Specific Language(DSL)を作成した。DSLとは、特定の作業や問題解決のために作られた言語のことで、
+今回の場合は粒子間相互作用の計算がそれにあたる。この論文では、私たちは並列化の手法としてSIMDをDSLの実装に適応した。
+なぜなら、現代の多くのCPUにSIMD命令があり，汎用性が高いためである。次のセクションではどのようにして並列化するかについて説明する
+% In astrophysics and astronomy, to numerically calculate the dynamical 
+% evolution of N particles interacting gravitationally, N-body simulations 
+% are required. Figure 1 shows the equation for interparticle interactions 
+% in N-body simulations. If the equation is naively computed, the time
+% complexity of calculation of interparticle interactions is 
+% \begin{math}O(N^2) \end{math}, where 
+% N is the number of particles. Therefore, parallelization is required to
+% speed up numerical simulations. To write a parallelized code for a 
+% numerical simulation, a user needs to understand the architecture of 
+% computer systems in  detail. If a parallelized code is automatically
+% generated by only describing the formulas and data of the numerical
+% simulation, the above problems are solved. To realize the parallelization,
+% we will develop Domain Specific Language \lparen DSL \rparen, which is a 
+% programming language specialized to a domain, for example, SQL and HTML.
+\subsection{parallelization}
+SIMDは、フリンの分類[1]の中の一つで、コンピュータ算術処理に関するものです。SIMDを用いると、算術演算を複数のデータに同時に適用することができます。この論文では、
+複数の粒子を計算し並列化する。例えば、Figure 1の場合、
+異なる粒子の加速度の計算は互いに独立しているため、並列化できます。これにより、例えば、粒子の変数が倍精度浮動小数点数であると仮定すると、
+AVX2命令を用いる場合、図1に示すように4要素の演算を実行することができます。したがって、並列化されていないコードと比較して、計算を4倍速く加速する可能性があります。
+このような並列化されたコードを粒子間相互作用の式の記述から生成するために以下のようなDSLを設計しました。
+\subsection{???}
+
+\subsection{Aim of this paper}
+
+\section{Method}
+\subsection{Overview of DSL}
+私たちはDSLの名前というDSLを作成しました。この言語の処理系は粒子相互作用の式を記述したコードを読み込み、その計算を高速化するようなコードを生成することが出来る。
+この言語は変数を定義と相互作用の式を記述できる。変数を定義する部分では、粒子の質量や位置、結果を保存する変数、それ以外に必要となる変数を定義できる。
+式の部分では、相互作用の式に必要な四則演算やsqrt，べき乗，ベクトルのノルムを計算できるようにした。この記述からkernel関数を生成し、それを呼び出して使う。
+\subsection{parallelization}
+
+\subsection{Use Sympy for DSL development.}
+
 \section{Conclusion}

### 2024-01-05 dsl/gen/gravity_code.hpp

@@ -1,0 +1,58 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double g, double eps2){
+   int i;
+   int j;
+   __m256d xi_tmp_v0;
+   __m256d xi_tmp_v1;
+   __m256d xi_tmp_v2;
+   __m256d xj_tmp_v0;
+   __m256d xj_tmp_v1;
+   __m256d xj_tmp_v2;
+   __m256d mass_tmp;
+   __m256d ai_tmp_v0;
+   __m256d ai_tmp_v1;
+   __m256d ai_tmp_v2;
+   __m256d g_tmp;
+   __m256d eps2_tmp;
+   __m256d x0_tmp_v0;
+   __m256d x0_tmp_v1;
+   __m256d x0_tmp_v2;
+
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
+      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
+      for (j = 0; j < n; j += 1) {
+         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
+         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
+         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
+         mass_tmp = _mm256_set1_pd(mass[j]);
[…]

### 2024-01-17 dsl/gen/gravity_code.hpp
20240117

@@ -4,12 +4,13 @@ int kernel(int n, double xi[][3], double xj[][3], double eps2, double g){
    int i;
    int j;
    double eps2;
+   double g;
    double rij;
    for (i = 0; i < n; i += 1) {
       ;
       for (j = 0; j < n; j += 1) {
          ;
-         rij = g/pow(eps2 + ((xi[i][2] - xj[j][2])*(xi[i][2] - xj[j][2]) + ((xi[i][0] - xj[j][0])*(xi[i][0] - xj[j][0]) + (xi[i][1] - xj[j][1])*(xi[i][1] - xj[j][1]))), 3.0/2.0);
+         rij = pow(eps2 + ((xi[i][2] - xj[j][2])*(xi[i][2] - xj[j][2]) + ((xi[i][0] - xj[j][0])*(xi[i][0] - xj[j][0]) + (xi[i][1] - xj[j][1])*(xi[i][1] - xj[j][1]))), 3.0/2.0);
       };
       ;
    };

### 2024-01-17 dsl/gen/pykg.py

@@ -955,7 +955,7 @@ def main():
 
     arg_ret_map_list = get_arg_ret_map_list(expr_list, name_variable_map)
     #ここでdot演算子を変換
-    new_op_expr_list = trans_new_op(after_cse_expr_list, arg_ret_map_list) 
+    new_op_expr_list = trans_new_op(after_cse_expr_list, arg_ret_map_list)
     arg_ret_map_list = get_arg_ret_map_list(new_op_expr_list, name_variable_map)
     check_tree(new_op_expr_list)
 

### 2024-01-22 dsl/gen/Var.py
0122

@@ -19,6 +19,8 @@ class Variable:
     symbol = None
     tmp_name = ''
     index_name = ''
+    prime = None
+    argument = None
 
     def index_def(self):
         if self.struct_name == 'EPI' or self.struct_name == 'FORCE':
@@ -101,6 +103,7 @@ class Variable:
             s = check_pat.group()
             self.name = s
             self.symbol = sympy.sympify(s)
+            self.argument = True
 
     def typeinfo_assign_(self, other):
         self.type_name = other.type_name

### 2024-01-22 dsl/gen/clock_time.hpp

@@ -1,0 +1,18 @@
+#include <math.h>
+#include <iostream>
+#include<time.h>
+using namespace std;
+
+template<class funcp>
+double get_sec_func(funcp f){
+    
+    clock_t st, e;
+    st = clock();
+    for(int i = 0;i < n;i++) {
+        ans_pow[i] = check_pow(i);
+    }
+    e = clock();
+    double get_pow_time = (double)(e - st) / CLOCKS_PER_SEC;
+    printf("time = %lf\n", get_pow_time);
+
+}

### 2024-01-22 dsl/gen/for_check_asenble_gravity_code.cpp

@@ -1,0 +1,25 @@
+#include<stdio.h>
+#include <x86intrin.h>
+#include<algorithm>
+#include<math.h>
+#include <immintrin.h>
+#include <random>
+#include<time.h>
+#include<iostream>
+#include<set>
+using namespace std;
+
+#include "gravity_code.hpp"
+
+
+int main() {
+    int n = 10;
+    double xi[n][3];
+    double m[n];
+    double ai[n][3];
+    double eps2 = pow(2, -5);
+    double g = 1;
+    
+    kernel(n, xi, xi, m, ai, eps2, g);
+    
+}

### 2024-01-22 dsl/gen/gravity_code.hpp

@@ -1,23 +1,62 @@
 #include<math.h>
-;
-int kernel(int n, double xi[][3], double xj[][3], double eps2, double g, double x0[3]){
+#include<x86intrin.h>;
+int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   double rij_v0;
-   double rij_v1;
-   double rij_v2;
-   for (i = 0; i < n; i += 1) {
-      ;
+   __m256d xi_tmp_v0;
+   __m256d xi_tmp_v1;
+   __m256d xi_tmp_v2;
+   __m256d xj_tmp_v0;
+   __m256d xj_tmp_v1;
+   __m256d xj_tmp_v2;
+   __m256d mass_tmp;
+   __m256d ai_tmp_v0;
+   __m256d ai_tmp_v1;
+   __m256d ai_tmp_v2;
+   __m256d eps2_tmp;
+   eps2_tmp = _mm256_set1_pd(eps2);
+   __m256d g_tmp;
+   g_tmp = _mm256_set1_pd(g);
+   __m256d x0_tmp_v0;
+   __m256d x0_tmp_v1;
+   __m256d x0_tmp_v2;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
[…]

### 2024-01-22 dsl/gen/pykg.py

@@ -2,6 +2,7 @@ from sympy import *
 from sympy.codegen.ast import (CodeBlock, For, Variable, Declaration, FunctionDefinition,
                                 Assignment, FunctionCall, String, IntBaseType,
                                FunctionPrototype, integer,Return)
+from sympy.codegen.ast import aug_assign
 from sympy.core.numbers import Integer
 import Var
 # SIMD = 'AVX2'
@@ -185,8 +186,15 @@ def trans_mid_expr(arg, name_variable_map, i):
                             trans_mid_expr(arg.args[1], name_variable_map, i))
 
     elif type(arg) is Assignment:
-        return Assignment(trans_mid_expr(arg.lhs, name_variable_map, i),
-                            trans_mid_expr(arg.rhs, name_variable_map, i))
+        left_arg = arg.lhs
+        left_v = get_name_variable(left_arg, name_variable_map)
+        left_mid_expr = trans_mid_expr(arg.lhs, name_variable_map, i)
+        right_mid_expr = trans_mid_expr(arg.rhs, name_variable_map, i)
+        if left_v.struct_name == 'FORCE':
+            mid_expr = aug_assign(left_mid_expr, '+', right_mid_expr)
+        else:
+            mid_expr = Assignment(left_mid_expr, right_mid_expr)
+        return mid_expr
     elif type(arg) is FunctionCall:
         func_name = get_func_name(arg)
         if func_name == 'dot3':
@@ -255,6 +263,9 @@ def EPI_load(v, i):
         tmp_name = v.name + "_tmp"
         return Assignment(Symbol(tmp_name), FunctionCall(function_name + type_name, [Symbol(var_name)]))
 
+def init_(tmp):
+    return Assignment(Symbol(tmp), 
+            FunctionCall('_mm256_set1_pd', [Symbol('0.0')]))
 
 #TODO 単精度少数の場合も
 def avx2_load(v, i):
@@ -267,6 +278,8 @@ def avx2_load(v, i):
     elif v.struct_name == 'EPJ':
         var_name += '[j]'
         function_name = '_mm256_set1_'
+    elif v.struct_name == 'FORCE':
+        return init_(tmp_name)
     else:
         function_name = '_mm256_set1_'
 
@@ -366,6 +379,7 @@ def in_prim_map(v, prim_map):
     else:
         return False
 
+
 def declear_tmp_var(name_variable_map, prim_map):
 
     dec_list = []
@@ -389,9 +403,11 @@ def declear_tmp_var(name_variable_map, prim_map):
                 
[…]

### 2024-01-22 dsl/gen/test_pow.cpp

@@ -1,0 +1,46 @@
+#include <math.h>
+#include <iostream>
+#include<time.h>
+using namespace std;
+
+double aa = 3.0;
+
+double check_pow(double x){
+   return aa / pow(x, 3/2); 
+}
+double check_op(double x){
+    double sx = 1.0 / sqrt(x);
+    return sx * sx * sx;
+}
+
+int main() {
+    int n = 10000;
+
+    double ans_pow[n], ans_sqrt[n];
+
+    for(int i = 0;i < n;i++) {
+        ans_pow[i] = i;
+        ans_sqrt[i] = i;
+    }
+
+    clock_t st, e;
+    st = clock();
+    for(int i = 0;i < n;i++) {
+        ans_pow[i] = check_pow(i * 10);
+    }
+    e = clock();
+    double get_pow_time = (double)(e - st) / CLOCKS_PER_SEC;
+    printf("time = %lf\n", get_pow_time);
+
+
+    st = clock();
+    for(int i = 0;i < n;i++) {
+        ans_sqrt[i] = check_op(i);
+    }
+    e = clock();
+    double get_op_time = (double)(e - st) / CLOCKS_PER_SEC;
+    printf("get op time = %lf\n", get_op_time);
+
+    printf("op_time - pow_time = %lf\n", get_op_time - get_pow_time);
+
+}

### 2024-01-22 dsl/simd/interparticle.cpp

@@ -29,7 +29,6 @@ for (int i = 0; i < ni; i++) {
     double az = 0.0;
 
     for (int j = 0; j < nj; j++) {
-        if(i == j) continue;
         double dx = double(posj[j][0] - xi);
         double dy = double(posj[j][1] - yi);
         double dz = double(posj[j][2] - zi);
@@ -122,6 +121,53 @@ void print_vec(vector<vector<double>> a, int n, FILE *fp) {
     fprintf(fp, "\n");
 }
 
+//aiy が確かめたいデータの配列
+vector<double> check_particles_v3_v3(double aix[][3], double aiy[][3], int n){
+    bool flag = true;
+    double eps = 0.000001;
+    double max_relerr = 0.0;
+    double min_relerr = 10000000.0;
+    vector<double> ans = {0, 0};
+    for(int i = 0;i < n;i++) {
+
+        
+        double ai0 = aiy[i][0];
+        double ai1 = aiy[i][1];
+        double ai2 = aiy[i][2];
+
+        //真値が0の時，相対誤差は絶対誤差になるため
+        if(ai0 == 0) {
+            ai0 = 1;
+        }
+        if(ai1 == 0) {
+            ai1 = 1;
+        }
+        if(ai2 == 0) {
+            ai2 = 1;
+        }
+
+
+        max_relerr = max({max_relerr, abs(aiy[i][0] - aix[i][0]) / abs(ai0),
+                                      abs(aiy[i][1] - aix[i][1]) / abs(ai1),
+                                      abs(aiy[i][2] - aix[i][2]) / abs(ai2)});
+
+        min_relerr = min({min_relerr, abs(aiy[i][0] - aix[i][0]) / abs(ai0),
+                                      abs(aiy[i][1] - aix[i][1]) / abs(ai1),
+                                      abs(aiy[i][2] - aix[i][2]) / abs(ai2)});
+        if(i % 1000 == 0){
+            // cout << "max is " << max_relerr << endl;
+            // cout << "min is " << min_relerr << endl;
+            // cout << aix[i][0] << endl;
+            // cout << aiy[i][0] << endl;
+        }
+    }
+
+
+    ans[0] = max_relerr;
+    ans[1] = min_relerr;
+    return ans;
+}
+
 vector<double> check_particles(double axi[], double ayi[],
                      double azi[], double acci[][3],
                      int n) {
[…]

### 2024-01-25 paper/paper.tex
20240117
0122
20240125

--- 2024-01-05 paper/paper.tex
@@
-% \documentclass[ams]{U-AizuGT}
-\documentclass[twocolumn, a4j]{article}
-% \usepackage{pifont}
-% \usepackage{graphicx}
-% \usepackage{cite}
+\documentclass[ams]{U-AizuGT}
+\usepackage{pifont}
+\usepackage{graphicx}
+\usepackage{cite}
+\usepackage{mathtools}
+\usepackage{listings,jvlisting}
 
-% \twocolumn[
+\lstset{
+    frame=single,
+    numbers=left,
+    tabsize=2
+}
 \bibliographystyle{ieice}
 \author{Ryuki Hiwada}
-% \studentid{s1280076}
-% \supervisor{Naohito Nakasato}
-% ]
+\studentid{s1280076}
+\supervisor{Naohito Nakasato}
+
 \title{Domain Specific Language for high performance computing}
@@
 programming language specialized to a domain, for example, SQL and HTML.
-\subsection{implemented DSL}
+\subsection{parallelization}
+SIMD is one of the categories in Flynn's taxonomy 1, related to computer arithmetic
+ processing. Using SIMD, arithmetic operations can be applied simultaneously to
+multiple data. In this paper, we compute and parallelize multiple particles. For example, 
+as shown in Figure 1, the computation of acceleration for different particles is independent
+of each other, allowing the process to be parallelized. As a result, for instance Assuming 
+that the variables for particles are double-precision floating-point numbers, we can execute 
+an operation on four elements simultaneously using the AVX2 instruction, it is possible to 
+perform operations on four elements. Therefore, compared to non-parallelized code, there is
+a potential to accelerate the computation by four times. We will describe the design of a 
+DSL in the next section to generate such parallelized code from the formulation of particle-particle interactions.
+\subsection{Overview of DSL}
 
-\subsection{parallelization}
-
+We have created a Domain Specific Language \lparen DSL \rparen named \lparen DSL name \rparen. This language's 
+processor can read code describing particle interaction formulas and generate code 
+that accelerates these computations. The language allows for the definition of 
+variables and the description of interaction formulas. In the variable definition 
+section, it's possible to define variables such as the mass and position of 
+particles, variables for storing results, and other necessary variables. For the formula
+part, we have enabled calculations including basic arithmetic operations, sqrt, power 
+functions, and computing the norm of vectors. From this description, a kernel function 
+is generated, which can then be called and used. We have created a Domain Specific 
+Language \lparen DSL \rparen named \lparen DSL name\rparen. This language's processor can read code describing particle 
+interaction formulas and generate code that accelerates these computations. The language allows
+for the definition of variables and the description of interaction formulas. In the variable
+definition section, it's possible to define variables such as the mass and position of 
+particles, variables for storing results, and other necessary variables. For the formula part, 
+we have enabled calculations including basic arithmetic operations, sqrt, power functions, and 
+computing the norm of vectors. From this description, a kernel function is generated, which can then be called and used.
 \subsection{Aim of this paper}
 
-\section{Method}
-\subsection{Use Sympy for DSL development.}
+\section{implementation}
+We use Sympy, a library in Python for implementing  the implementation of our \lparen DSL\rparen .
+SymPy supports various operations, and the formulas using these operations are internally treated as 
+syntax trees. We leveraged this functionality to read formulas and generate code capable of parallel execution.
+For parallelization, we used an instruction set named Advanced Vector Extensions 2 (AVX2). AVX2 is one of the 
+extended instruction sets implemented in Intel's CPUs. The next section will explain how parallelization is carried out using AVX2.
+
+\subsection{AVX2 for parallelization}
+To execute SIMD operations, SIMD-specific registers are used, 
+and multiple data are computed simultaneously to match the bit 
+size of the registers. For example, in the case of CPUs that 
+support AVX2 instructions, the registers are 256 bits, allowing 
+four double-precision floating-point numbers to be stored and 
+computed at the same time. To explicitly handle SIMD instructions
+ in high-level programming languages like C and C++, intrinsic 
+ functions are used. Additionally, to handle SIMD-specific registers, 
+ specialized types are used. For C++, the file immintrin.h, 
+ which is available as a standard in the language, is included to 
+ handle these. As an example of parallelization, the paper explains
+  the parallelization of the gravitational interaction formula shown 
+  in Figure 1.
+
+\subsection{design of (name of DSL)}
+
+\begin{lstlisting}[language=c++]
+#include <iostream>
+
+int main(){
+    std::cout << "Hello, world!" << std::endl;
+    return 0;
+}
+\end{lstlisting}
+\subsection{implementation of (name of DSL)}
+
+\subsection{Use Sympy for DSL development}
 

### 2024-01-25 dsl/gen/gen_0122_goodscore.hpp

@@ -19,7 +19,8 @@ int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3],
          x0_v1 = xj[j][1] - xi[i][1];
          x0_v2 = xj[j][2] - xi[i][2];
          double r = 1.0f / sqrt(eps2 + (x0_v2*x0_v2 + (x0_v0*x0_v0 + x0_v1*x0_v1)));
-         double r2 = g*mass[j] * r * r * r;
+         double r2 = g * mass[j] * pow(r, 3);
+         // double r2 = g*mass[j] * r * r * r;
 
          ax += x0_v0*r2;
          ay += x0_v1*r2;

### 2024-01-25 dsl/gen/gen_0122_simd_correctans.hpp

@@ -43,8 +43,10 @@ int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3],
          x0_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
          __m256d r = _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(x0_tmp_v0, x0_tmp_v0), _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1)), _mm256_mul_pd(x0_tmp_v2, x0_tmp_v2));
          ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(g_tmp, mass_tmp), x0_tmp_v0), _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, r)), _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, r)), _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, r)))));
-         ai_tmp_v1 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(g_tmp, mass_tmp), x0_tmp_v1), _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(x0_tmp_v0, x0_tmp_v0), _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1)), _mm256_mul_pd(x0_tmp_v2, x0_tmp_v2)))), _mm256_mul_pd(_mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(x0_tmp_v0, x0_tmp_v0), _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1)), _mm256_mul_pd(x0_tmp_v2, x0_tmp_v2)))), _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(x0_tmp_v0, x0_tmp_v0), _mm256_mul_pd(x0_tmp_v1, x0_tmp_v1)), _mm256_mul_pd(x0_tmp_v2, x0_tmp_v2)))))));
[…]

### 2024-01-25 dsl/gen/gravity_code.hpp

@@ -1,62 +1,24 @@
 #include<math.h>
-#include<x86intrin.h>;
+;
 int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   __m256d xi_tmp_v0;
-   __m256d xi_tmp_v1;
-   __m256d xi_tmp_v2;
-   __m256d xj_tmp_v0;
-   __m256d xj_tmp_v1;
-   __m256d xj_tmp_v2;
-   __m256d mass_tmp;
-   __m256d ai_tmp_v0;
-   __m256d ai_tmp_v1;
-   __m256d ai_tmp_v2;
-   __m256d eps2_tmp;
-   eps2_tmp = _mm256_set1_pd(eps2);
-   __m256d g_tmp;
-   g_tmp = _mm256_set1_pd(g);
-   __m256d x0_tmp_v0;
-   __m256d x0_tmp_v1;
-   __m256d x0_tmp_v2;
-   for (i = 0; i < n; i += 4) {
-      int index_gather_0[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
-      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
-      int index_gather_1[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
-      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
-      int index_gather_2[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
-      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
-      ai_tmp_v0 = _mm256_set1_pd(0.0);
-      ai_tmp_v1 = _mm256_set1_pd(0.0);
-      ai_tmp_v2 = _mm256_set1_pd(0.0);
[…]

### 2024-01-25 dsl/gen/pykg.py

@@ -134,7 +134,7 @@ def pow_pattern(left_arg, right_arg):
                 #TODO 整数ではなく、変数**変数の場合　とりあえず保留
                 return FunctionCall(POW_FUNCTION_NAME, [left_arg, right_arg])
     else:
-        
+         
         return Pow(left_arg, right_arg)
 
 def get_func_name(expr):
@@ -956,12 +956,40 @@ def trans_sub(expr):
     else:
         return expr
 
+
+def sqrt_pat(expr):
+    if type(expr) is Pow and type(expr.exp) is Rational:
+        r = expr.exp
+        if r.denominator == 2:
+            return True
+        
+    return False
+
+
+
+#sqrtであるような要素を探し、変換する. 
+#Rationalの分母が2だったらsqrtに変換する。
+def trans_sqrt(expr, arg_ret_map):
+    if sqrt_pat(expr):
+        r = expr.exp
+        pow_num = r.numerator
+        b = expr.base
+        new_expr = trans_sqrt(b, arg_ret_map)
+        if pow_num == 2:
+             return Mul(new_expr, new_expr)
+        return 
+    elif not_op(expr):
+        return expr
+    return
+    
+
 #構文木(expr)を自分で定義した演算子に変換する。
 def trans_new_op(expr_list, arg_ret_map_list):
     new_expr_list = []
     for expr in expr_list:
         arg_ret_map = arg_ret_map_list[expr.lhs]
         # new_expr = trans_sub(expr.rhs)
+
         new_expr = trans_dot(expr.rhs, arg_ret_map)
         new_expr_list.append(Assignment(expr.lhs, new_expr))
          

### 2024-01-25 dsl/simd/interparticle.cpp

@@ -1,5 +1,5 @@
 #include<stdio.h>
-#include <x86intrin.h>
+// #include <x86intrin.h> これは全部のint命令が使えるようになる奴
 #include<algorithm>
 #include<math.h>
 #include <immintrin.h>
@@ -9,7 +9,9 @@
 #include<set>
 using namespace std;
 
-#include "../gen/gravity_code.hpp"
+// #include "../gen/gravity_code.hpp"
+#include "../gen/gen_0122_goodscore.hpp"
+// #include "../gen/gen_0122_simd_correctans.hpp"
 
 void evaluate_gravity(
 int ni,
@@ -294,7 +296,7 @@ int main() {
 
     printf("evaluate_gravity_simd of elapsed time = %lfsec\n", simd_elapsed);
 
-    printf("%lf times\n", non_simd_elapsed / simd_elapsed);
+    // printf("%lf times\n", non_simd_elapsed / simd_elapsed);
 
     FILE *non_simd_fp, *simd_fp;
     non_simd_fp = fopen("non_simd_result.txt", "w");

### 2024-01-26 paper/paper.tex
20240126

@@
 syntax trees. We leveraged this functionality to read formulas and generate code capable of parallel execution.
-For parallelization, we used an instruction set named Advanced Vector Extensions 2 (AVX2). AVX2 is one of the 
+For parallelization, we used an instruction set named Advanced Vector Extensions 2 \lparen AVX2\rparen. AVX2 is one of the 
 extended instruction sets implemented in Intel's CPUs. The next section will explain how parallelization is carried out using AVX2.
@@
 \subsection{AVX2 for parallelization}
-To execute SIMD operations, SIMD-specific registers are used, 
-and multiple data are computed simultaneously to match the bit 
-size of the registers. For example, in the case of CPUs that 
-support AVX2 instructions, the registers are 256 bits, allowing 
-four double-precision floating-point numbers to be stored and 
-computed at the same time. To explicitly handle SIMD instructions
- in high-level programming languages like C and C++, intrinsic 
- functions are used. Additionally, to handle SIMD-specific registers, 
- specialized types are used. For C++, the file immintrin.h, 
- which is available as a standard in the language, is included to 
- handle these. As an example of parallelization, the paper explains
-  the parallelization of the gravitational interaction formula shown 
-  in Figure 1.
+To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
+and the results are stored. However, in the case of SIMD, computations are performed using SIMD-specific registers, so the 
+methods of loading, computing, and storing differ. When loading, multiple elements that will undergo the same instruction are
+stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
+each. For instance, consider a calculation like C = X + Y, where elements of double-precision floating arrays x and y are computed
+. When using AVX2 for SIMD, since the registers are 256 bits, four elements from x and y are loaded each. These are then added 
+simultaneously, and the results are stored in the array C. When loading into SIMD registers, if it's a 1-dimensional array, 
+contiguous memory access is sufficient, but for data structures like Array of Structures \lparen AoS \rparen shown in Figure a., elements need
+to be loaded individually. For example, when considering the 3-dimensional coordinates of particles as double-precision floats 
+in pos\lbrack n\rbrack \lbrack 3\rbrack  \lparen where n is the total number of particles, and pos\lbrack i \rbrack \lbrack 0\rbrack , pos\lbrack i\rbrack \lbrack 1\rbrack , 
+pos\lbrack i\rbrack \lbrack 2\rbrack  represent the x, y, z coordinates 
+of the i-th particle, respectively\rparen, and calculating the difference in x coordinates between particles i and j, it becomes dx = 
+pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack .
+However, for parallelization with SIMD, desiring dx0 = pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j \rbrack \lbrack 0\rbrack , dx1 = pos\lbrack i+1\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack
+, dx2 = pos\lbrack i+2\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , dx3 = pos\lbrack i+3\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , 
+the data are packed as \lparen pos\lbrack i\rbrack \lbrack 0\rbrack , pos\lbrack i+1\rbrack \lbrack 0\rbrack , pos\lbrack i+2\rbrack \lbrack  0\rbrack , pos\lbrack  i+3\rbrack \lbrack  0\rbrack \rparen,
+\lparen pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rparen, \lparen dx0, dx1, dx2, dx3\rparen and subtraction is performed simultaneously.
+However, since data needs
+to be loaded onto SIMD registers all at once, the gather instruction is used to load data for particle i. The gather instruction is used
+to read non-contiguous data elements from memory addresses by specifying addresses. An explanation of the gather instruction is shown in 
+Figure x. Data loaded in this way are computed simultaneously using SIMD instructions. When storing computation results, addresses may 
+not be contiguous. In such cases, there is an instruction called scatter, which is the counterpart to gather, but it is not supported 
+in AVX2, so data are stored using pointers individually. In this way, parallelization is achieved with SIMD. Moreover, these instructions
+can be explicitly handled in high-level programming languages like C and C++ using intrinsic functions. To handle intrinsic functions 
+in C and C++, include the file immintrin.h, which is available as a standard in the language.
+An example of C++ code that calculates the difference in x coordinates, simd\_tmp.cpp, is shown.
+{ DSL name}  generates C++ code capable of executing SIMD instructions like simd\_tmp.cpp
+from the described formulas. The next section will explain the design of { DSL name}.
 
-\subsection{design of (name of DSL)}
+\subsection{design of name of DSL}
 

### 2024-01-26 dsl/simd/interparticle.cpp

@@ -232,6 +232,7 @@ int main() {
     double acci[n][3];
     int id[n];
 
+    //__attribute__((aligned(32))) 
     //pykg用のデータ
     __attribute__((aligned(32))) double xij[n][3];
     __attribute__((aligned(32))) double pykg_m[n];

### 2024-01-31 paper/paper.tex
paper write at Parsing

@@
-\documentclass[ams]{U-AizuGT}
+\documentclass[ams, a4j]{U-AizuGT}
 \usepackage{pifont}
@@
 \usepackage{listings,jvlisting}
-
+% \documentclass[a4j]{jarticle} %ここは関係ない
+\usepackage{listings,jvlisting} 
 \lstset{
@@
 }
+
+% \usepackage{listings,jlisting}
+
+% \lstset{%
+%   language={C},
+%   basicstyle={\small},%
+%   identifierstyle={\small},%
+%   commentstyle={\small\itshape},%
+%   keywordstyle={\small\bfseries},%
+%   ndkeywordstyle={\small},%
+%   stringstyle={\small\ttfamily},
+%   frame={tb},
+%   breaklines=true,
+%   columns=[l]{fullflexible},%
+%   numbers=left,%
+%   xrightmargin=0zw,%
+%   xleftmargin=3zw,%
+%   numberstyle={\scriptsize},%
+%   stepnumber=1,
+%   numbersep=1zw,%
+%   lineskip=-0.5ex%
+% }
+% \lstset{
+%   basicstyle={\ttfamily},
+%   identifierstyle={\small},
+%   commentstyle={\smallitshape},
+%   keywordstyle={\small\bfseries},
+%   ndkeywordstyle={\small},
+%   stringstyle={\small\ttfamily},
+%   frame={tb},
+%   breaklines=true,
+%   columns=[l]{fullflexible},
+%   numbers=left,
+%   xrightmargin=0zw,
+%   xleftmargin=3zw,
+%   numberstyle={\scriptsize},
+%   stepnumber=1,
+%   numbersep=1zw,
+%   lineskip=-0.5ex
+% }
+
 \bibliographystyle{ieice}
@@
 simulation, the above problems are solved. To realize the parallelization,
-we will develop Domain Specific Language \lparen DSL \rparen, which is a 
+we will develop Domain Specific Language  DSL \rparen, which is a 
 programming language specialized to a domain, for example, SQL and HTML.
@@
 
-We have created a Domain Specific Language \lparen DSL \rparen named \lparen DSL name \rparen. This language's 
+We have created a Domain Specific Language  DSL \rparen named  Pyker \rparen. This language's 
 processor can read code describing particle interaction formulas and generate code 
@@
 is generated, which can then be called and used. We have created a Domain Specific 
-Language \lparen DSL \rparen named \lparen DSL name\rparen. This language's processor can read code describing particle 
+Language  DSL  named  Pyker. This language's processor can read code describing particle 
 interaction formulas and generate code that accelerates these computations. The language allows
@@
 
-\section{implementation}
-We use Sympy, a library in Python for implementing  the implementation of our \lparen DSL\rparen .
+\section{Construction}
+We use Sympy, a library in Python for implementing  the implementation of pyker.
 SymPy supports various operations, and the formulas using these operations are internally treated as 
@@
 stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
-each. For instance, consider a calculation like C = X + Y, where elements of double-precision floating arrays x and y are computed
+each.
+
+For instance, consider a calculation like C = X + Y, where elements of double-precision floating arrays x and y are computed
 . When using AVX2 for SIMD, since the registers are 256 bits, four elements from x and y are loaded each. These are then added 
@@
 contiguous memory access is sufficient, but for data structures like Array of Structures \lparen AoS \rparen shown in Figure a., elements need
-to be loaded individually. For example, when considering the 3-dimensional coordinates of particles as double-precision floats 
+to be loaded individually.
+
+For example, when considering the 3-dimensional coordinates of particles as double-precision floats 
 in pos\lbrack n\rbrack \lbrack 3\rbrack  \lparen where n is the total number of particles, and pos\lbrack i \rbrack \lbrack 0\rbrack , pos\lbrack i\rbrack \lbrack 1\rbrack , 
@@
 to read non-contiguous data elements from memory addresses by specifying addresses. An explanation of the gather instruction is shown in 
-Figure x. Data loaded in this way are computed simultaneously using SIMD instructions. When storing computation results, addresses may 
+Figure x. Data loaded in this way are computed simultaneously using SIMD instructions.
+
+When storing computation results, addresses may 
 not be contiguous. In such cases, there is an instruction called scatter, which is the counterpart to gather, but it is not supported 
@@
 An example of C++ code that calculates the difference in x coordinates, simd\_tmp.cpp, is shown.
-{ DSL name}  generates C++ code capable of executing SIMD instructions like simd\_tmp.cpp
-from the described formulas. The next section will explain the design of { DSL name}.
+{ Pyker}  generates C++ code capable of executing SIMD instructions like simd\_tmp.cpp
+from the described formulas. The next section will explain the Pyker.
 
-\subsection{design of name of DSL}
+\subsection{Pyker}
+In this DSL, code is generated by writing and compiling two definitions: the definition of variables and the definition of interaction formulas. First, let us explain the variable definition.
 
-\begin{lstlisting}[language=c++]
-#include <iostream>
+In this DSL, variables are classified into classes: EPI, EPJ, FORCE, and others. EPI represents particles that receive interactions, 
+while EPJ represents particles that provide interactions. FORCE holds the results of the interaction calculations, and other variables 
+include softening parameters and the like. To perform calculations using these variables, in C++, it would be similar to \ref{fuga}.
 
-int main(){
-    std::cout << "Hello, world!" << std::endl;
-    return 0;
+\begin{lstlisting}[caption=hoge,label=fuga]
+int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
+	// (1).preprocess
+	for(int i = 0;i < n;i += 1) {
+		// (2).load EPI 
+		// (3).Initialization of tmporary force
+		for(int j = 0;j < n;j += 1) {
+				// (4). calculate interparticle interactions
+		}
+		// (5). Store calculation result in the FORCE
+	}
 }
 \end{lstlisting}
-\subsection{implementation of (name of DSL)}
 
-\subsection{Use Sympy for DSL development}
+(1) involves preparatory steps such as defining variables necessary for the calculation. (2) 
+involves loading the variables of EPI. (3) is about initializing variables that temporarily
+ hold the results of the interaction calculation. (4) involves performing the interaction 
+ calculation and saving the results in the primary variable of force. (5) involves storing the results in the FORCE variables.
+To generate this code, in variable definition, information about the class of the variable,
+ its type, and its dimension is necessary. Therefore, in pyker, variable definitions are written as follows. .
+The first column, if it is a class, writes the name of the class and its member variable
+ name. The second column explicitly writes the dimensions of the vector if there are any, 
+ specifying 3 or 4 dimensions, and the type is either 32-bit or 64-bit floating-point. The 
+ third column becomes the name of the variable handled on pykg. For example, "EPI.pos vec3<F64> xi" 
+ would be a member variable of EPI named pos, a 3-dimensional 64-bit floating-point variable named xi.
+The definition of interaction formulas is written to accumulate the results in the FORCE variable using
+ the defined variables. Primary variables necessary for the mathematical description can be newly defined 
+ using previously defined variables. Available operations include basic arithmetic, sqrt, and the power 
+ symbol "**". The result is stored in the FORCE variable using '='.For instance, to generate code that c
+ alculates the gravitational interaction formula shown in Figure 1, it would be written in this DSL as figure1.pyker.
+
+\begin{lstlisting}
+EPI.pos vec3<F64> xi
+EPJ.pos vec3<F64> xj
+EPJ.m F64 mass
+FORCE.acc vec3<F64> ai
+F64 eps2
+F64 g
+dr = xj - xi
+ai = g * mass *  dr / sqrt(dr ** 2 + eps2) ** 3
+\end{lstlisting}
+\subsection{Implementation}
+The process of generating code is illustrated in the following flowchart. In Parsing, the information
+of the variables defined in the DSL code is converted into a hash with the variable names as keys. 
+Formulas are converted into syntax trees using the sympify() method of Sympy, and a list of these 
+trees is obtained. Next, Common Subexpression Elimination (CSE) is performed on the syntax trees of the converted formulas. CSE is the process 
+of reducing the number of operations by pre-calculating common subexpressions in formulas and using 
+their results in subsequent calculations. In type inference, the types of the primary variables in the 
+formulas are inferred. Afterward, all syntax trees are converted into binary trees to align them with 
+SIMD operations. Finally, the code for calculating interactions is generated by traversing the processed 
+syntax trees. The following sections describe how the implementation was carried out in the order of
+Parsing, CSE, type inference, conversion to binary trees, and Code generation.
+
+\includegraphics[width=50mm]{flowchartver3.jpg}
+\subsubsection{Parsing}
+In Parsing, the process is divided between variable definition and formula handling. In variable definition, 
+objects with class, vector, type, and variable name are created respectively. A hash with the variable name
+as the key is then made (name\_variable\_map). Formulas use the sympify() method from the Sympy library to convert
+the code read as a string into a syntax tree of formulas, obtaining a list of these syntax trees (expr\_list). Next, 
+Common Subexpression Elimination (CSE) is performed.
+\subsubsection{CSE}
+
+\subsubsection{type inference}
+\subsubsection{convert to binary trees}
+\subsubsection{code generate}
+
+\subsection{Experiments}
 

### 2024-01-31 dsl/gen/gravity_code.hpp

@@ -3,20 +3,20 @@
 int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   double x0_v0;
-   double x0_v1;
-   double x0_v2;
+   double dr_v0;
+   double dr_v1;
+   double dr_v2;
    for (i = 0; i < n; i += 1) {
       ;
       ;
       for (j = 0; j < n; j += 1) {
          ;
-         x0_v0 = -xi[i][0] + xj[j][0];
-         x0_v1 = -xi[i][1] + xj[j][1];
-         x0_v2 = -xi[i][2] + xj[j][2];
-         ai[i][0] += (x0_v0*(g*mass[j]))/pow(eps2 + (x0_v2*x0_v2 + (x0_v0*x0_v0 + x0_v1*x0_v1)), 3.0/2.0);
-         ai[i][1] += (x0_v1*(g*mass[j]))/pow(eps2 + (x0_v2*x0_v2 + (x0_v0*x0_v0 + x0_v1*x0_v1)), 3.0/2.0);
-         ai[i][2] += (x0_v2*(g*mass[j]))/pow(eps2 + (x0_v2*x0_v2 + (x0_v0*x0_v0 + x0_v1*x0_v1)), 3.0/2.0);
+         dr_v0 = -xi[i][0] + xj[j][0];
+         dr_v1 = -xi[i][1] + xj[j][1];
+         dr_v2 = -xi[i][2] + xj[j][2];
+         ai[i][0] += (mass[j]*(dr_v0*g))/pow(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)), 3.0/2.0);
+         ai[i][1] += (mass[j]*(dr_v1*g))/pow(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)), 3.0/2.0);
+         ai[i][2] += (mass[j]*(dr_v2*g))/pow(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)), 3.0/2.0);
       };
       ;
    };

### 2024-01-31 dsl/gen/pykg.py

@@ -87,6 +87,7 @@ def mul_pattern(left_arg, right_arg):
             return FunctionCall(MUL_FUNCTION_NAME, [left_arg, right_arg])
         
     else:
+        # print(left_arg, right_arg)
         return Mul(left_arg, right_arg, evaluate=False)
     
 def sqrt_op(left_arg, right_arg):
@@ -1009,7 +1010,7 @@ def main():
 
     
 
-    with open('rij.pykg', 'r', encoding='utf-8') as f:
+    with open('test.pykg', 'r', encoding='utf-8') as f:
         s = f.read()
         expr_list, name_variable_map = Parse(s)
     

### 2024-02-01 paper/paper.tex
last laptop write_paper

@@
 \usepackage{pifont}
-\usepackage{graphicx}
+% \usepackage{graphicx}
 \usepackage{cite}
@@
 \usepackage{listings,jvlisting} 
+\usepackage[dvipdfmx]{graphicx}
 \lstset{
@@
 \title{Domain Specific Language for high performance computing}
+
 \begin{document}
 \maketitle
-\section{Abstract}
+\begin{abstract}
+
+\end{abstract}
 \section{Introduction}
+
+test
+
 \subsection{Background}
@@
 
-\begin{lstlisting}[caption=hoge,label=fuga]
+\begin{lstlisting*}[caption=hoge,label=fuga]
 int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
@@
 }
-\end{lstlisting}
+\end{lstlisting*}
 
@@
 Parsing, CSE, type inference, conversion to binary trees, and Code generation.
-
-\includegraphics[width=50mm]{flowchartver3.jpg}
+% \includegraphics[width=\columnwidth]{flowchartver3.jpg}
 \subsubsection{Parsing}

### 2024-02-01 paper/ja_paper.tex
paper add jp pattern 20240201

\documentclass[ams, a4j]{U-AizuGT}
\usepackage{pifont}
% \usepackage{graphicx}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{listings,jvlisting}
% \documentclass[a4j]{jarticle} %ここは関係ない
\usepackage{listings,jvlisting} 
\usepackage[dvipdfmx]{graphicx}
\lstset{
    frame=single,
    numbers=left,
    tabsize=2
}

% \usepackage{listings,jlisting}

% \lstset{%
%   language={C},
%   basicstyle={\small},%
%   identifierstyle={\small},%
%   commentstyle={\small\itshape},%
%   keywordstyle={\small\bfseries},%
%   ndkeywordstyle={\small},%
%   stringstyle={\small\ttfamily},
%   frame={tb},
%   breaklines=true,
%   columns=[l]{fullflexible},%
%   numbers=left,%
%   xrightmargin=0zw,%
%   xleftmargin=3zw,%
%   numberstyle={\scriptsize},%
%   stepnumber=1,
%   numbersep=1zw,%
%   lineskip=-0.5ex%
% }
\lstset{
  basicstyle={\ttfamily},
  identifierstyle={\small},
  commentstyle={\smallitshape},
  keywordstyle={\small\bfseries},
  ndkeywordstyle={\small},
  stringstyle={\small\ttfamily},
  frame={tb},
  breaklines=true,
  columns=[l]{fullflexible},
  numbers=left,
  xrightmargin=0zw,
  xleftmargin=3zw,
  numberstyle={\scriptsize},
  stepnumber=1,
  numbersep=1zw,
  lineskip=-0.5ex
}

\bibliographystyle{ieice}
\author{Ryuki Hiwada}
\studentid{s1280076}
\supervisor{Naohito Nakasato}

\title{Domain Specific Language for high performance computing}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}
\section{Introduction}
テスト

\section{Implementation}

SIMDを行うには通常の計算と同じように、まずメモリからデータをloadし、そのデータをもとに計算し、結果をstoreする。
しかし、SIMDの場合は、SIMD用のレジスタを使って計算をするためloadや計算、storeの仕方が違う. loadをするとき、SIMD用の\
レジスタに同じ命令を行う複数の要素を格納する。そしてそれを使って同時に計算し、計算結果をそれぞれstoreする。\

 例えば、倍精度小数の配列x,yの要素を計算するC=X + Yのような計算を考えるとき,AVX2を使用してSIMDを行う\
場合レジスタは256ビットのレジスタなので、xとyの要素をそれぞれ4つずつloadする。そしてそれを同時に足し、
結果を格納する配列Cにstoreする。SIMDレジスタにloadをするとき、1次元配列なら連続するメモリをアクセスすればいいが、Figure 
a.に示すArray of Structures(AoS)のデータ構造の場合、要素ごとにロードしてこなくてはいけない.

例えば、粒子の3次元の座標を倍精度小数でpos[n][3](nは粒子の総数とし、pos[i][0],pos[i][1],pos[i][2]をそれぞれi番目の粒子
のx座標,y座標,z座標)とするとき、粒子i, jのx座標の差を求めるとき、dx = pos[i][0] - pos[j][0]のようになるが、これをSIMDで
並列化するとき、dx0 = pos[i][0] - pos[j][0], dx1 = pos[i+1][0] - pos[j][0], dx2 = pos[i+2][0] - pos[j][0],dx3 = 
pos[i+3][0] - pos[j][0]としたいので、(pos[i][0], pos[i+1][0], pos[i+2][0], pos[i+3][0]), (pos[j][0],pos[j][0],pos[j][0],
pos[j][0]),(dx0,dx1,dx2,dx3)とそれぞれパックして、同時に引き算を行う。しかし、SIMDレジスタにデータを一度にそれぞれ乗せなくては
いけないので、gather命令を使い粒子iのデータをloadする。gather命令とは、アドレスを指定してメモリアドレス上の連続していないデータ
要素を読み込むのに使用する。gather命令の説明を図xに示す。このようにloadしたデータをSIMDの命令を実行し同時に計算する。

計算結果をstoreする際もアドレスが連続していない場合がある。その時は、scatter命令と呼ばれるgather命令と対象になる命令があるが、
AVX2にはサポートされていないため、それぞれポインタを使ってデータをstoreする。このようにしてSIMDによる並列化をする。

また、これらの命令はinstrinsincs関数を使うことでC,C++などの**high-level programming languageにおいて**明示的に扱える。
C,C++においてinstrinsincs関数を扱うには、言語標準で使用できるimmintrin.hというファイルをインクルードする。そしてデータは
simd_tmp.cppをx座標の差を計算するC++のコードを例として示す。{DSLの名前}は記述された数式をsimd_tmp.cppのようにSIMD命令を実行で
きるようなC++のコードを生成する。次のセクションでは、{DSLの名前}の設計を説明する。

\end{document}

### 2024-02-01 paper/paper.tex
paper add jp pattern 20240201

@@
 % }
-% \lstset{
-%   basicstyle={\ttfamily},
-%   identifierstyle={\small},
-%   commentstyle={\smallitshape},
-%   keywordstyle={\small\bfseries},
-%   ndkeywordstyle={\small},
-%   stringstyle={\small\ttfamily},
-%   frame={tb},
-%   breaklines=true,
-%   columns=[l]{fullflexible},
-%   numbers=left,
-%   xrightmargin=0zw,
-%   xleftmargin=3zw,
-%   numberstyle={\scriptsize},
-%   stepnumber=1,
-%   numbersep=1zw,
-%   lineskip=-0.5ex
-% }
+\lstset{
+  basicstyle={\ttfamily},
+  identifierstyle={\small},
+  commentstyle={\smallitshape},
+  keywordstyle={\small\bfseries},
+  ndkeywordstyle={\small},
+  stringstyle={\small\ttfamily},
+  frame={tb},
+  breaklines=true,
+  columns=[l]{fullflexible},
+  numbers=left,
+  xrightmargin=0zw,
+  xleftmargin=3zw,
+  numberstyle={\scriptsize},
+  stepnumber=1,
+  numbersep=1zw,
+  lineskip=-0.5ex
+}
 
@@
 
-\begin{lstlisting*}[caption=hoge,label=fuga]
+\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
 int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
@@
 }
-\end{lstlisting*}
+\end{lstlisting}
 
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
 EPI.pos vec3<F64> xi

### 2024-02-03 dsl/gen/gravity_code.hpp
implementing last cse when simd

@@ -1,24 +1,66 @@
 #include<math.h>
-;
+#include<x86intrin.h>;
 int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   double dr_v0;
-   double dr_v1;
-   double dr_v2;
-   for (i = 0; i < n; i += 1) {
-      ;
-      ;
+   __m256d xi_tmp_v0;
+   __m256d xi_tmp_v1;
+   __m256d xi_tmp_v2;
+   __m256d xj_tmp_v0;
+   __m256d xj_tmp_v1;
+   __m256d xj_tmp_v2;
+   __m256d mass_tmp;
+   __m256d ai_tmp_v0;
+   __m256d ai_tmp_v1;
+   __m256d ai_tmp_v2;
+   __m256d eps2_tmp;
+   eps2_tmp = _mm256_set1_pd(eps2);
+   __m256d g_tmp;
+   g_tmp = _mm256_set1_pd(g);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d x0_tmp;
+   __m256d x1_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
+      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
+      ai_tmp_v0 = _mm256_set1_pd(0.0);
[…]

### 2024-02-03 dsl/gen/pyker.py

@@ -118,25 +118,45 @@ def or_Integer(left_arg, right_arg):
     else:
         return None
 
+def pow_to_mul(expr, num):
+    new_expr = expr
+    for i in range(num - 1):
+        new_expr = Mul(new_expr, expr, evaluate=False)
 
-def pow_pattern(left_arg, right_arg):
-    arg = sqrt_op(left_arg, right_arg)
+    return new_expr
+
+def pow_pattern(base_arg, exp_arg):
+    arg = sqrt_op(base_arg, exp_arg)
+    
     if SIMD:
         if arg:
             return FunctionCall(SQRT_FUNCTION_NAME, [arg])
         else:
             #片方だけが整数だった場合
-            new_expr = or_Integer(left_arg, right_arg)
+            new_expr = or_Integer(base_arg, exp_arg)
 
             #べき乗の数だけ掛け算に変換
             if new_expr:
                 return new_expr
             else:
                 #TODO 整数ではなく、変数**変数の場合　とりあえず保留
-                return FunctionCall(POW_FUNCTION_NAME, [left_arg, right_arg])
+                return FunctionCall(POW_FUNCTION_NAME, [base_arg, exp_arg])
     else:
-         
-        return Pow(left_arg, right_arg)
+        if type(exp_arg) is Integer: 
+            new_expr = pow_to_mul(base_arg, int(exp_arg))
+            
+        elif type(exp_arg) is Rational:
+            num = exp_arg.numerator
+            deno = exp_arg.denominator
+            if num == 1:
+                new_expr = Pow(base_arg, exp_arg)
+            else:
+                new_expr = pow_to_mul(base_arg, num)
+                new_exp_arg = Rational(Integer(1), deno)
+                new_expr = Pow(new_expr, new_exp_arg, evaluate=False)
+        else:
+            new_expr = Pow(base_arg, exp_arg, evaluate=False)
+        return new_expr
 
 def get_func_name(expr):
     return str(expr.name)
@@ -183,8 +203,12 @@ def trans_mid_expr(arg, name_variable_map, i):
                             trans_mid_expr(arg.args[1], name_variable_map, i))
     
     elif type(arg) is Pow:
-        return pow_pattern(trans_mid_expr(arg.args[0], name_variable_map, i),
-                            trans_mid_expr(arg.args[1], name_variable_map, i))
+        exp = arg.exp
[…]

### 2024-02-03 dsl/simd/interparticle.cpp

@@ -9,8 +9,8 @@
 #include<set>
 using namespace std;
 
-// #include "../gen/gravity_code.hpp"
-#include "../gen/gen_0122_goodscore.hpp"
+#include "../gen/gravity_code.hpp"
+// #include "../gen/gen_0122_goodscore.hpp"
 // #include "../gen/gen_0122_simd_correctans.hpp"
 
 void evaluate_gravity(

### 2024-02-05 paper/check_paper.tex
write paper at Code generate section

\documentclass{jarticle}
\usepackage[margin=20truemm]{geometry}
\usepackage{setspace}
\usepackage[mathlines]{lineno} %% <- remove [mathlines] to omit equation line numbers
\usepackage{amsmath}
\usepackage[dvipdfmx]{graphicx}

\usepackage{mathtools}

\usepackage{listings,jvlisting} 
\usepackage{etoolbox} %% <- for \pretocmd, \apptocmd and \patchcmd

\doublespacing

%% Patch 'normal' math environments:
\newcommand*\linenomathpatch[1]{%
  \cspreto{#1}{\linenomath}%
  \cspreto{#1*}{\linenomath}%
  \csappto{end#1}{\endlinenomath}%
  \csappto{end#1*}{\endlinenomath}%
}
%% Patch AMS math environments:
\newcommand*\linenomathpatchAMS[1]{%
  \cspreto{#1}{\linenomathAMS}%
  \cspreto{#1*}{\linenomathAMS}%
  \csappto{end#1}{\endlinenomath}%
  \csappto{end#1*}{\endlinenomath}%
}

%% Definition of \linenomathAMS depends on whether the mathlines option is provided
\expandafter\ifx\linenomath\linenomathWithnumbers
  \let\linenomathAMS\linenomathWithnumbers
  %% The following line gets rid of an extra line numbers at the bottom:
  \patchcmd\linenomathAMS{\advance\postdisplaypenalty\linenopenalty}{}{}{}
\else
  \let\linenomathAMS\linenomathNonumbers
\fi

\linenomathpatch{equation}
\linenomathpatchAMS{gather}
\linenomathpatchAMS{multline}
\linenomathpatchAMS{align}
\linenomathpatchAMS{alignat}
\linenomathpatchAMS{flalign}

\linenumbers
\title{My Document}
\author{Anonymous Anteater}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}
\section{Introduction}

\subsection{Background}
In astrophysics and astronomy, to numerically calculate the dynamical 
evolution of N particles interacting gravitationally, N-body simulations 
are required. Figure 1 shows the equation for interparticle interactions 
in N-body simulations. If the equation is naively computed, the time
complexity of calculation of interparticle interactions is 
\begin{math}O(N^2) \end{math}, where 
N is the number of particles. Therefore, parallelization is required to
speed up numerical simulations. To write a parallelized code for a 
numerical simulation, a user needs to understand the architecture of 
computer systems in  detail. If a parallelized code is automatically
generated by only describing the formulas and data of the numerical
simulation, the above problems are solved. To realize the parallelization,
we will develop Domain Specific Language  DSL \rparen, which is a 
programming language specialized to a domain, for example, SQL and HTML.

\subsection{parallelization}
SIMD is one of the categories in Flynn's taxonomy 1, related to computer arithmetic
 processing. Using SIMD, arithmetic operations can be applied simultaneously to
multiple data. In this paper, we compute and parallelize multiple particles. For example, 
as shown in Figure 1, the computation of acceleration for different particles is independent
of each other, allowing the process to be parallelized. As a result, for instance Assuming 
that the variables for particles are double-precision floating-point numbers, we can execute 
an operation on four elements simultaneously using the AVX2 instruction, it is possible to 
perform operations on four elements. Therefore, compared to non-parallelized code, there is
a potential to accelerate the computation by four times. We will describe the design of a 
DSL in the next section to generate such parallelized code from the formulation of particle-particle interactions.

\subsection{Overview of DSL}
私たちはPykerというDSLを作成しました。この言語の処理系は粒子相互作用の式を記述したコードを読み込み、
その計算を高速化するC++言語のコードを生成することが出来る。この言語は変数を定義と相互作用の式を記述できる。
変数を定義する部分では、粒子の質量や位置、結果を保存する変数、それ以外に必要となる変数を定義できる。
式の部分では、相互作用の式に必要な四則演算やsqrt,べき乗,ベクトルの内積を計算できるようにした。
この記述からkernel関数を生成し、それを呼び出して使う。

\section{Construction}
私たちはDSLの実装にPythonの代数計算ライブラリのSympyを使った。
Sympyには、様々な演算がサポートされていて、これらを用いた数式は内部で構文木として扱われている。
私たちはその機能を用いて数式を読み込み、並列化に実行できるコードを生成することが出来る。並列化には、
並列化をAdvanced Vector Extensions 2(AVX2)という命令セットを用いた。AVX2とは、
インテル社のCPUに実装された拡張命令セットの一つである。次のセクションでは、どのようにAVX2で並列化を行うかを説明する。

\subsection{AVX2 for parallelization}

SIMDを行うには通常の計算と同じように、まずメモリからデータをloadし、そのデータをもとに計算し、結果をstoreする。
しかし、SIMDの場合は、SIMD用のレジスタを使って計算をするためloadや計算、storeの仕方が違う.loadをするとき,
SIMD用のレジスタに同じ命令を行う複数の要素を格納する。そしてそれを使って同時に計算し、計算結果をそれぞれstoreする。

 例えば、倍精度小数の配列x,yの要素を計算するC=X + Yのような計算を考えるとき,AVX2を使用してSIMDを行う場合レジスタは
256ビットのレジスタなので、xとyの要素をそれぞれ4つずつloadする。そしてそれを同時に足し、結果を格納する配列Cにstoreする。
SIMDレジスタにloadをするとき、1次元配列なら連続するメモリをアクセスすればいいが、Figure a.に示すArray of Structures\lparen AoS \rparen
のデータ構造の場合、要素ごとにロードしてこなくてはいけない。

 例えば、粒子の3次元の座標を倍精度小数でpos [n] \lbrack 3\rbrack 
 \lparen nは粒子の総数とし、pos \lbrack i \rbrack \lbrack 0\rbrack ,pos\lbrack i \rbrack \lbrack 1 \rbrack, pos \lbrack i \rbrack \lbrack 2 \rbrack をそれぞれi番目の粒子のx座標,y座標,z座標 \rparen
  とするとき、粒子i, jのx座標の差を求めるとき、dx = pos \lbrack i \rbrack \lbrack 0 \rbrack - pos\lbrack j \rbrack \lbrack 0 \rbrack のようになるが,
これをSIMDで並列化するとき、
\begin{lstlisting}[frame=single]
dx0 = pos[i][0] - pos[j][0]
dx1 = pos[i + 1][0] - pos[j][0]
dx2 = pos[i + 2][0] - pos[j][0]
dx3 = pos[i + 3][0] - pos[j][0]
\end{lstlisting}

としたいので、\lparen pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rparen, \lparen
,\lparen dx0,dx1,dx2,dx3 \rparen とそれぞれパックして、同時に引き算を行う。しかし、SIMDレジスタにデータを一度にそれぞれ乗せなくてはいけないので、
gather命令を使い粒子iのデータをloadする。gather命令とは、アドレスを指定してメモリアドレス上の連続していないデータ要素を読み込むのに使用する。
gather命令の説明を図xに示す。このようにloadしたデータをSIMDの命令を実行し同時に計算する。

計算結果をstoreする際もアドレスが連続していない場合がある。その時は、scatter命令と呼ばれるgather命令と対象になる命令があるが、
AVX2にはサポートされていないため、それぞれポインタを使ってデータをstoreする。このようにしてSIMDによる並列化をする。

また、これらの命令はinstrinsincs関数を使うことでC,C++などの**high-level programming languageにおいて**明示的に扱える。
C,C++においてinstrinsincs関数を扱うには、言語標準で使用できるimmintrin.hというファイルをインクルードする。
そしてデータはtemplate.cppをx座標の差を計算するC++のコードを例として示す。Pykerは記述された数式をtemplate.cpp
のようにSIMD命令を実行できるようなC++のコードを生成する。次のセクションでは、Pykerの説明する。

\subsection{Pyker}
このDSLでは、変数の定義と相互作用の式の定義の２つを記述しそれをコンパイルすることでコードを生成する。最初に変数定義について説明する。

このDSLでは、変数にはclassがあり、EPI,EPJ,FORCE,その他と分かれる。EPIは相互作用を受ける粒子を示し、EPJが相互作用を与える粒子になる。
FORCEは相互作用の計算結果を保持し、そのほかの変数はソフトニングパラメータ等である。これらの変数を使って計算をするには、
C++では、template.cppのようになる。

\begin{lstlisting}[frame=single, caption=template.cpp, language=c++]
  int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
    // (1).preprocess
    for(int i = 0;i < n;i += 1) {
      // (2).load EPI 
      // (3).Initialization of tmporary force
      for(int j = 0;j < n;j += 1) {
          // (4). calculate interparticle interactions
      }
      // (5). Store calculation result in the FORCE
    }

  }
  \end{lstlisting}

  (1)では、計算に必要な変数の定義などの前準備。(2)では、EPIの変数をロードする。(3)では、相互作用の計算結果を一時的に保持する変数を初期化。
  (4)では、相互作用の計算を行い、結果をforceの一次変数に保存。(5)で，FORCEの変数に結果をstoreする。

  このコードを生成するためには、変数の定義では、変数のclassと、型、次元の情報がそれぞれ必要になる。そのためpykerでは、変数の定義を以下とする。
  \begin{lstlisting}
  ((EPI|EPJ|FORCE).(\w+))? (vec(3|4)<)?(F(32|64))>? \w+
  \end{lstlisting}

  1列目はclassであれば、classの名前とそのメンバ変数名を書く。2列目はベクトルの次元があれば、3次元と4次元を明示的に書き、
  型は32bitと64bit浮動小数を書く。3列目では、pykg上で扱う変数の名前になる。例えば、”EPI.pos vec3<F64> xi”は、EPIのposというメンバ変数で、
  3次元の64bit浮動小数型のxiという変数名となる。

  相互作用の式の定義は、定義した変数を使って、FORCEの変数に結果をアキュムレートしていくように記述する。
  数式の記述に必要な一次変数はそれまでに定義された変数を用いてを新たに定義できる。使用できる演算は、四則演算とsqrtとべき乗を表す'**'を使うことが出来る。
  結果はFORCEの変数に'='でstoreすることを表す。

  例えば、Figure 1の重力相互作用の式を計算するコードを生成する場合、このDSLで記述するとtemplate.pykerとなる。

\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
  EPI.pos vec3<F64> xi
  EPJ.pos vec3<F64> xj
  EPJ.m F64 mass
  FORCE.acc vec3<F64> ai
  F64 eps2
  F64 g
  dr = xj - xi
  ai = g * mass *  dr / sqrt(dr ** 2 + eps2) ** 3
\end{lstlisting}

次のセクションでは、どのようにして、このコードから目標のコードを生成するかを説明する。

\subsection{Implementation}
コードを生成する流れは以下のflowchartに示す。Parseでは、DSLのコードから定義された変数の情報を変数名をkeyに持つハッシュに変換する。
数式は、Sympy形式の構文木に変換し、そのリストを取得する。次に構文木に変換した数式に対してCommon subexpression elimination(CSE)を行う。
CSEとは、数式に含まれる共通部分式をあらかじめ計算し、その計算結果を使って数式を計算することによって演算回数を減らすことである。type inferenceでは、
数式の一次変数の型推論を行う。その後数式をSIMD演算に合わせるため構文木をすべて二分木にする。最後に以上の処理を行った構文木を辿り、相互作用の計算を行うコードを生成する。
以下は、ParseからCSE,type inference, convert to binary tree, Codegenerateの順にどのように実装を行ったかを説明していく。
\includegraphics[width=100mm]{flowchartver3.jpg}

\subsubsection{Parsing}
Parseでは、変数定義と数式で処理を分ける。変数定義では,class, ベクトル、型、変数名を持つ自作したVarというクラスのオブジェクトをそれぞれ生成する。
そのオブジェクトとkeyを変数名に持つハッシュを作る(name\_variable\_map)。数式はSympyのライブラリにあるメソッドのsympify()を使い、
文字列として読み込んだコードを数式の構文木に変換し、それらの構文木のリスト(expr\_list)を取得する。次にCSEを行う。

\subsubsection{CSE}

CSEとは数式にある共通する部分式を先に計算し、その結果を使うことで演算回数を減らすこと。これにはsympyにあるcse()という関数に数式を渡して行う。これにより新たに部分式の数式が生成されて、その部分式の結果を使った計算式に変換される。

\subsubsection{translate to dot method}
このDSLでは、ベクトル同士の積を内積として扱う。そのために、構文木をたどっていき該当する部分式を見つけてそこを置き換えて木を再構築する。
sympyの構文木の構造は演算子が親となり、その子としてほかの演算子やシンボルがある。例えば、x,y,z を変数としてx + y * z は図1のような構文木になる。
しかしこの要素らがベクトルであるかがsympyが知らないため例えば、v1,v2をベクトル、v3をスカラーととこのDSL上で定義されていたとすると、(v1 * v2) * v3
は一つのMulが親となり、v1,v2,v3が子となる構文木になる。そのため、完全二分木にする際、どこが内積に該当するのかわからない。なので内積をdot関数に置き換える。
sympyにはFunctionCallというclassがあり、独自に定義した関数を構文木に組み込むことが出来る。そのため、構文木をたどり該当する部分木をFunctionCallでdot関数に置き換えていく。
その構文木をたどる際、ノードが部分式の場合、その部分式が返すのがベクトルかどうかわからない。
そのためkeyにノードを持ちvalueにベクトルかスカラーかの情報を持つhash(arg\_ret\_map)を作り、それを使って判定する。そして、dotに置き換え更新した部分式はarg\_ret\_mapにその都度更新する。
こうしてdot演算に置き換え再構築した構文木のリストを次の処理に渡す。

\subsubsection{type inference}
一時変数は数式の結果を一時的に保存する。その一時変数の型やベクトルを判断するには、数式の結果がどんな型なのかどんなvecなのかでわかる。
またこのDSLでは型は倍精度少数しか実装していないので、ベクトルかどうかだけが分かればいい。そのため、CSEのセクションで説明したarg\_ret\_mapを使う。

\subsubsection{convert to binary trees}
simd演算はinstrcin関数で行う際2項演算なので引数が2つの関数を使って数式を計算するコードにしなければならない。そのため、数式の構文木を完全二分木である必要がある。
しかし、sympyの数式の構文木では演算の順序を考えなくてよい場合、一つの演算子を親としてその項をまとめる。そのため、子を3つ以上持つような演算子のノードでは、
その演算子で二分木に変換する。例を図1に示す。このときsympyが自動で簡約化して二分木をまとめてしまわないように、演算子に置き換えるときに演算子の関数を使い、
オプションでevaluate=Falseにする。例えばa * b * c はMul(a, Mul(b, c, evaluate=False), evaluate=False)となる。

\subsubsection{code generate}
% - このセクションでは、実行可能なコードを生成する。
% - コードを生成するには、Codegenというモジュールを使う。
%     - このモジュールはsympyの数式から実行可能なコードを生成するモジュールである。
%     - このDSLでは、関数を作成するのに**FunctionDefinition**というクラスのオブジェクトを生成し、それを出力する。FunctionDefinitionでは、関数のsympyで定義した計算内容とFunctionPrototypeというクラスのオブジェクトを引数としてfrom\_FunctionPrototypeというFunctionDefinitionのメンバ関数によってFunctionDefinitionのオブジェクトを生成する。そして最後に、必要なinclude文を追加し,hppのファイルとして出力する。
%     - FunctionDefinitionの生成
%         - FunctionPrototypeと計算内容が必要
%     - FunctionPrototypeの生成
%         - 関数の引数と戻り値と名前が必要
%         - 引数は、DSL上で定義した変数
%         - 戻り値は、今回はintで0を返すようにする
%         - 名前はkernelとする
%     - 計算内容
%         - template.cppの(1)~(5)
%         - (1)は計算に必要な一時変数の定義する文を作成
%         - (2)でgather命令を用いたload。ここでは、FunctionCall()を使ってintrinsics関数のgather命令に対応する関数を呼び、それを代入する文を作成する
%         - (3)で計算結果を保持する一時変数を初期化
%         - (4)数式のリストから演算子をSIMD命令に置き換えていく。
%         - またここで、引き算、割り算、sqrt、べき乗は単純に置き換えられない。
%             - 引き算の場合は、sympyは構文木にすると引き算をx + ((-1) * y)のようになっていて演算子の引き算がノードとなっていない。そのため、今探索しているノードがAddだった場合、子に-1がかかっている要素があれば、引き算のSIMD命令に置き換える。
%             - 割り算の場合は、引き算の場合と同様に、構文木に割り算がないため、\begin{math}x / y \end{math} を \begin{math}
%               x * (y ^(-1))
%             \end{math}と表現されているので、探索しているノードが掛け算のとき、子に-1乗されてるノードがあれば割り算のSIMD命令にする。
%             - sqrtの場合は、例えばsqrt(x)は構文木上では、\begin{math}x^(1/2) \end{math}と表されているので、同様にべき乗の演算子Powのの時, expが1/2であれば、sqrtのSIMD命令に置き換える。
%         - 計算に必要な一時変数
%     - CodeBlockというクラスのオブジェクトを生成する
%     - 
%     - forループ,load,結果を一時保存する初期化、
%     - Loadパート
%     - そもそも

\end{document}

### 2024-02-05 paper/paper.tex
implementing last cse when simd
write paper at Code generate section

@@
 \usepackage{mathtools}
-\usepackage{listings,jvlisting}
+% \usepackage{listings,jvlisting}
 % \documentclass[a4j]{jarticle} %ここは関係ない
@@
 \section{Introduction}
-
-test
 
@@
 \begin{lstlisting}[frame=single, caption=hoge, label=fuga]
-int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
+int kernel(double xi[][3], double xj[][3], double ai[][3], double eps2, int n){
 	// (1).preprocess
-	for(int i = 0;i < n;i += 1) {
+	for(int i = 0;i < n;i += 4) {
 		// (2).load EPI 
@@
 Parsing, CSE, type inference, conversion to binary trees, and Code generation.
-% \includegraphics[width=\columnwidth]{flowchartver3.jpg}
+\includegraphics[width=\columnwidth]{flowchartver3.jpg}
 \subsubsection{Parsing}
@@
 
-\subsection{Experiments}
+\begin{lstlisting}[frame=single, caption=hoge]
+//(1) include part
+#include<math>
+#include<immintrin.h>
+int kernel( (2) double xi[][3], double xj[][3], double eps2 ...) {
+  //(3) decleare tmp variable
+  int i;
+  int j;
+  __m256d xi_tmp_v0;
+  __m256d xi_tmp_v1;  
+  __m256d xi_tmp_v2;
+  __m256d eps2_tmp;
+  . 
+  .
+  .
+
+  // (4) loop increment
+  for(i = 0;i < (n);i += 4) {
+    // (5) Load EPI variable part and initialize result temporary variable
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      .
+      .
+      .
+
+    for(j = 0;j < (n);j += 1) {
+      // (6) Load EPJ variable part
+         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
+         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
+         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
+
+      // (7) calculate interparticle
+    }
+
+    // (8) Store result part
+
+  }
+  return 0;
+}
+
+\end{lstlisting}
+
+\section{Experiments}
 

### 2024-02-05 dsl/gen/Var.py

@@ -9,7 +9,7 @@ import sympy
 # var_name = 'xi'
 # SIMD = 'AVX2'
 SIMD = None
-class Variable:
+class Var:
     struct_name = ""
     memb_name = ""
     type_name = ""
@@ -19,7 +19,7 @@ class Variable:
     symbol = None
     tmp_name = ''
     index_name = ''
-    prime = None
+    prime = False
     argument = None
 
     def index_def(self):

### 2024-02-05 dsl/gen/gravity_code.hpp

@@ -40,14 +40,14 @@ int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3],
          xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
          xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
          mass_tmp = _mm256_set1_pd(mass[j]);
-         x0 = _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)), _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2))));
-         x1 = _mm256_mul_pd(x0, _mm256_mul_pd(x0, x0));
          dr_tmp_v0 = _mm256_sub_pd(xj_tmp_v0, xi_tmp_v0);
          dr_tmp_v1 = _mm256_sub_pd(xj_tmp_v1, xi_tmp_v1);
          dr_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
-         ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(dr_tmp_v0, g_tmp), mass_tmp), x1);
-         ai_tmp_v1 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(dr_tmp_v1, g_tmp), mass_tmp), x1);
-         ai_tmp_v2 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(dr_tmp_v2, g_tmp), mass_tmp), x1);
+         x0_tmp = _mm256_sqrt_pd(_mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)), _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2))));
+         x1_tmp = _mm256_mul_pd(x0_tmp, _mm256_mul_pd(x0_tmp, x0_tmp));
+         ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(_mm256_mul_pd(dr_tmp_v0, g_tmp), mass_tmp), x1_tmp);
[…]

### 2024-02-05 dsl/gen/pyker.py

@@ -47,7 +47,7 @@ def Parse(file_str):
             #空白等の式や変数宣言でない部分の処理を書く
             
             #変数宣言だった場合型の情報をVariableから取得
-            v = Var.Variable(col)
+            v = Var.Var(col)
             name_variable_map[v.name] = v
 
     return expr_list, name_variable_map
@@ -480,7 +480,7 @@ def CodeGen(expr_list, name_variable_map, prim_map):
 
     #引数の作成
     for v in name_variable_map.values():
-        if v.name in prim_map:
+        if v.prime == True:
             continue        
 
         sym_name = v.name
@@ -669,7 +669,7 @@ def type_inference(expr_list, name_variable_map, arg_ret_map_list):
                 prim_map[str(expr.lhs)] = v
             continue
 
-        prim_var = Var.Variable()
+        prim_var = Var.Var()
         prim_var.name = str(expr.lhs)
         prim_var.tmp_name = str(expr.lhs)
         #TODO とりあえず全部浮動小数
@@ -697,12 +697,18 @@ def type_inference(expr_list, name_variable_map, arg_ret_map_list):
                 
                 elif type(arg) in operator_list or arg is Integer(-1) or arg is Rational(1, 2) or type(arg) is Integer or type(arg) is Rational:
                     continue
+
+                
                 
                 else:
                     #エラー
                     print('error!! in type_interference', arg)
+                    # print(arg_ret_map_list)
+                    print(expr_list)
                     return 
-
+        if str(expr.lhs) == 'dr_v0':
+            print(prim_var)
+            
         prim_map[str(expr.lhs)] = prim_var
         name_variable_map[str(expr.lhs)] = prim_var
 
@@ -714,6 +720,13 @@ def apply_cse(expr_list, name_variable_map):
     new_list = []
     for expr in pre_culc:
         new_list.append(Assignment(expr[0], expr[1]))
+        # tmp_v = expr[0]
+        # for pre_expr in pre_culc:
+        #     rhs_expr = pre_expr.rhs
+        #     if tmp_v in rhs_expr.args:
+                
+        #ここに、pre_culcのなかに初めて一時変数が出てきたら、その直前に数式を挿入する処理を入れる
+        
     new_list += cse_list[1]
     prim_map = type_inference(new_list, name_variable_map, None)
     return new_list

### 2024-02-05 dsl/simd/gravity_code.hpp

@@ -1,0 +1,24 @@
+#include<math.h>
+;
+int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
+   int i;
+   int j;
+   double dr_v0;
+   double dr_v1;
+   double dr_v2;
+   for (i = 0; i < n; i += 1) {
+      ;
+      ;
+      for (j = 0; j < n; j += 1) {
+         ;
+         dr_v0 = -xi[i][0] + xj[j][0];
+         dr_v1 = -xi[i][1] + xj[j][1];
+         dr_v2 = -xi[i][2] + xj[j][2];
+         ai[i][0] += (mass[j]*(dr_v0*g))/(((sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1))))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))));
+         ai[i][1] += (mass[j]*(dr_v1*g))/(((sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1))))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))));
+         ai[i][2] += (mass[j]*(dr_v2*g))/(((sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1))))*sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)))));
+      };
+      ;
+   };
+   return 0;
+};

### 2024-02-05 paper/paper.tex
20240205

@@
 \subsection{AVX2 for parallelization}
+% _mm256dの説明はここですべきか？ codegen で説明すべきか
 To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
@@
 #include<immintrin.h>
-int kernel( (2) double xi[][3], double xj[][3], double eps2 ...) {
+int kernel( (2) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
   //(3) decleare tmp variable
@@
   __m256d eps2_tmp;
-  . 
-  .
-  .
+  // ... 
+  // ... 
+  // ... 
+  //(4) def not class variables
+  eps2_tmp = _mm256_set1_pd(eps2);
+  // ... 
+  // ... 
+  // ...
 
-  // (4) loop increment
+  // (5) loop increment
   for(i = 0;i < (n);i += 4) {
-    // (5) Load EPI variable part and initialize result temporary variable
+    // (6) Load EPI variable part
     int index_gather_0[4] = {0, 3, 6, 9};
     __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
-      .
-      .
-      .
+      // ... 
+      // ... 
+      // ... 
+    // (7) initialize result temporary variable
 
     for(j = 0;j < (n);j += 1) {
-      // (6) Load EPJ variable part
+      // (8) Load EPJ variable part
          xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
@@
          xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
+        // ... 
+        // ... 
+        // ...
 
-      // (7) calculate interparticle
+      // (9) calculate interparticle
     }
 
-    // (8) Store result part
+    // (10) Store result part
 
@@
 }
-
 \end{lstlisting}

### 2024-02-06 paper/jp_check/check_paper.tex
20240206 write in type inference

--- 2024-02-05 paper/check_paper.tex
@@
 私たちはDSLの実装にPythonの代数計算ライブラリのSympyを使った。
-Sympyには、様々な演算がサポートされていて、これらを用いた数式は内部で構文木として扱われている。
-私たちはその機能を用いて数式を読み込み、並列化に実行できるコードを生成することが出来る。並列化には、
-並列化をAdvanced Vector Extensions 2(AVX2)という命令セットを用いた。AVX2とは、
+Sympyでは、数式をシンボルと演算子を用いて構文木として扱うことが出来る。
+そしてその構文木から実行可能なコードを生成するモジュールがある。このDSLでは、それらの機能を用いて数式を読み込み、
+並列に実行できるコードを生成する。並列化には、Advanced Vector Extensions 2(AVX2)という命令セットを用いた。AVX2とは、
 インテル社のCPUに実装された拡張命令セットの一つである。次のセクションでは、どのようにAVX2で並列化を行うかを説明する。
@@
 
-  このコードを生成するためには、変数の定義では、変数のclassと、型、次元の情報がそれぞれ必要になる。そのためpykerでは、変数の定義を以下とする。
+  このコードを生成するためには、変数の定義では、変数のclassと、型、次元の情報がそれぞれ必要になる。そのためpykerでは、変数の定義を正規表現で表すと以下のようになる。
   \begin{lstlisting}
-  ((EPI|EPJ|FORCE).(\w+))? (vec(3|4)<)?(F(32|64))>? \w+
+  ((EPI|EPJ|FORCE).(\w+))? (vec3<)?(F64)>? \w+
   \end{lstlisting}
 
-  1列目はclassであれば、classの名前とそのメンバ変数名を書く。2列目はベクトルの次元があれば、3次元と4次元を明示的に書き、
-  型は32bitと64bit浮動小数を書く。3列目では、pykg上で扱う変数の名前になる。例えば、”EPI.pos vec3<F64> xi”は、EPIのposというメンバ変数で、
+  1列目はclassであれば、classの名前とそのメンバ変数名を書く。2列目はベクトルの次元があれば、明示的に書き、
+  型は'F64'と書き、64bit浮動小数を表す。3列目では、pykg上で扱う変数の名前になる。例えば、”EPI.pos vec3<F64> xi”は、EPIのposというメンバ変数で、
   3次元の64bit浮動小数型のxiという変数名となる。
@@
 
-\subsubsection{code generate}
+\subsubsection{code generation of SIMD}
+CodeGenでは、c++で実行可能な関数のコードを生成する。生成するコードの疑似コードをtemplate.cppに示す。
+
+\begin{lstlisting}[frame=single, caption=template.cpp]
+  //(1) include part
+  #include<math>
+  #include<immintrin.h>
+  int kernel( (2) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
+    //(3) decleare tmp variable
+    int i;
+    int j;
+    __m256d xi_tmp_v0;
+    __m256d xi_tmp_v1;  
+    __m256d xi_tmp_v2;
+    __m256d eps2_tmp;
+    // ... 
+    // ... 
+    // ... 
+    //(4) def not class variables
+    eps2_tmp = _mm256_set1_pd(eps2);
+    // ... 
+    // ... 
+    // ...
+
+    // (5) loop increment
+    for(i = 0;i < (n);i += 4) {
+      // (6) Load EPI variable part
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
+      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
+      // ... 
+      // ... 
+      // ... 
+      // (7) initialize result temporary variable
+      ai_tmp_v0 = _mm256_set1_pd(0.0);
+      ai_tmp_v1 = _mm256_set1_pd(0.0);
+      ai_tmp_v2 = _mm256_set1_pd(0.0);
+
+      for(j = 0;j < (n);j += 1) {
+        // (8) Load EPJ variable part
+           xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
+           xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
+           xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
+          // ... 
+          // ... 
+          // ...
+
+        // (9) calculate interparticle
+      }
+
+      // (10) Store result part
+
+    }
+    return 0;
+  }
+  \end{lstlisting}
+
+コード生成の際に必要な要素をtemplate.cppに書かれた(1), (2),(3)の順に説明する。それぞれは(1)インクルード文の挿入、(2)関数の引数の定義、(3)相互作用の計算に必要な一時変数,(4)EPI,EPJ,FORCEでない変数の定義、(5)ループのインクリメント幅、(6)EPIの変数をloadする部分、(7)結果を一時的に保持する変数の初期化、(8) EPJの変数をロードする部分、(9)実際に計算する内容、(10)SIMDのstore部分である。またDSL上で定義したEPI,EPJ,FORCEの変数は、ソースコード上では単なる変数として扱われる。
+
+(1)では、SIMD演算などで必要となるインクルード文を挿入する。math.hは、SIMD化しない場合に、sqrt()を実行するために、immintrin.hでは、SIMD演算のための関数を呼び出すために必要となる.
+
+(2)では、DSLのコードで変数定義されていた変数を引数とする。そのために変数をすべてみて、DSLのコードで変数定義されていれば引数に追加する。
+
+(3)Sympyでは、変数の定義をVariableというクラスのオブジェクトをDeclarationというクラスのコンストラクタに渡して生成したオブジェクトで表す。
+
+一時変数の名前はベクトルであれば、(DSL上で記述した名前)\_tmp\_v{i}(iは次元数に合わせて0インデックスで定義), スカラーであれば、(DSL上で記述した名前) \_tmpとする。変数の型は今回は倍精度少数だけなので、\_\_m256dにする。\_\_m256dはAVX2の256bitのレジスタで要素が倍精度少数をセットできる型である.
+
+(4)では、classでない変数の定義では、定義とともにその変数の値を並列する数分初期化する。それには,\_mm256\_set1\_pd()という関数を使う。この関数は引数で与えられた倍精度少数の値を\_\_m256dに4つセットする関数で、eps2\_tmpのデータ構造は(eps2, eps2, eps2, eps2)のようになっている。これとループで使用するインデックスである,iとjを定義する.
+
+(5)では、並列数分だけインクリメントするようにする。今回は倍精度少数しか実装していないので並列数は常に4にする.
+
+(6)では、EPIの変数のloadを行う。loadには、AVX2 for Parallelizationのセクションで説明したようにgather命令を使用する。gather命令は、
+(6)に書かれている3行のコードはgather命令によるloadの一連の流れである。index\_gather\_0[]は\& xi[i][0]から何個分のメモリにあるかを示している。\&xi[i][0]から\&xi[i + 1][0]
+はdouble型の変数の3つ分先のメモリアドレスになる。\&xi[i + 2][0]も同様になるのでindex\_gather\_0[]には、{0, 3, 6,9}となる。vindex\_gather\_0はindex\_gather\_0を128ビットレジスタに乗せていて、
+これで\_mm256\_i32gather\_pdを使うことが出来る。\_mm256\_i32gather\_pdの第3引数の8は、要素が何バイトであるかを表し、double型なので8byteとしている。これにより、
+\&xi[i][0],\&xi[i + 1][0],\&xi[i + 2][0],\&xi[i + 3][0]をロードする。またEPIの要素がスカラーであれば、\_mm256\_load\_pd(\&m[i])という関数を使い、連続するm[i],m[i+1],m[i+2],m[i+3]を256ビットのレジスタにloadする。
+これをEPIの変数すべてに行う。
 % - このセクションでは、実行可能なコードを生成する。

### 2024-02-06 paper/paper.tex
20240206 write in type inference

@@
 Parsing, CSE, type inference, conversion to binary trees, and Code generation.
-\includegraphics[width=\columnwidth]{flowchartver3.jpg}
+\includegraphics[width=0.2\textwidth]{flowchartver3.jpg}
 \subsubsection{Parsing}
@@
 \subsubsection{convert to binary trees}
-\subsubsection{code generate}
+
+\subsubsection{code generatation of non SIMD}
+
+\begin{lstlisting}[frame=single, caption=hoge]
+
+#include<math>
+int kernel( (1) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
+  //(2)
+  int i;
+  int j;
+  double dr_v0;
+  double dr_v1;
+  double dr_v2;
+  // ... 
+  // ... 
+  // ...
+
+  for(i = 0;i < n;i += 1) {
+    for(j = 0;j < n;j += 1) {
+      //(3)
+      dr_v0 = -xi[i][0] + xj[j][0];
+      dr_v1 = -xi[i][1] + xj[j][1];
+      dr_v2 = -xi[i][2] + xj[j][2];
+      // ... 
+      // ... 
+      // ... 
+    }
+  }
+}
+\end{lstlisting}
+
+\subsubsection{code generatation of SIMD}
 
@@
   // (5) loop increment
-  for(i = 0;i < (n);i += 4) {
+  for(i = 0;i < n;i += 4) {
     // (6) Load EPI variable part
@@
     // ...
+
     // (7) initialize result temporary variable
+    ai_tmp_v0 = _mm256_set1_pd(0.0);
+    ai_tmp_v1 = _mm256_set1_pd(0.0);
+    ai_tmp_v2 = _mm256_set1_pd(0.0);
 
-    for(j = 0;j < (n);j += 1) {
+    for(j = 0;j < n;j += 1) {
       // (8) Load EPJ variable part
@@
       // (9) calculate interparticle
+        dr_tmp_v0 = _mm256_sub_pd(xj_tmp_v0, xi_tmp_v0);
+        dr_tmp_v1 = _mm256_sub_pd(xj_tmp_v1, xi_tmp_v1);
+        dr_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
+        ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(//.....));
+        ai_tmp_v1 += _mm256_div_pd(_mm256_mul_pd(//.....));
+        ai_tmp_v2 += _mm256_div_pd(_mm256_mul_pd(//.....));
+
     }

### 2024-02-06 dsl/experiment/harp_pyker_code.hpp

@@ -1,0 +1,63 @@
+#include<math.h>
+;
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   double dr_v0;
+   double dr_v1;
+   double dr_v2;
+   double dv_v0;
+   double dv_v1;
+   double dv_v2;
+   double r2_v0;
+   double r2_v1;
+   double r2_v2;
+   double rv_v0;
+   double rv_v1;
+   double rv_v2;
+   double x0_v0;
+   double x0_v1;
+   double x0_v2;
+   double af_v0;
+   double af_v1;
+   double af_v2;
+   double jf_v0;
+   double jf_v1;
+   double jf_v2;
+   for (i = 0; i < n; i += 1) {
+      ;
+      ;
+      for (j = 0; j < n; j += 1) {
+         ;
+         dr_v0 = ri[i][0] - rj[j][0];
+         dr_v1 = ri[i][1] - rj[j][1];
+         dr_v2 = ri[i][2] - rj[j][2];
+         dv_v0 = vi[i][0] - vj[j][0];
+         dv_v1 = vi[i][1] - vj[j][1];
+         dv_v2 = vi[i][2] - vj[j][2];
+         r2_v0 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
+         r2_v1 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
+         r2_v2 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
+         rv_v0 = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
+         rv_v1 = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
+         rv_v2 = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
+         x0_v0 = sqrt(r2_v0);
+         x0_v1 = sqrt(r2_v1);
+         x0_v2 = sqrt(r2_v2);
[…]

### 2024-02-06 dsl/gen/gravity_code.hpp

@@ -1,66 +1,22 @@
 #include<math.h>
-#include<x86intrin.h>;
-int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
+;
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
    int i;
    int j;
-   __m256d xi_tmp_v0;
-   __m256d xi_tmp_v1;
-   __m256d xi_tmp_v2;
-   __m256d xj_tmp_v0;
-   __m256d xj_tmp_v1;
-   __m256d xj_tmp_v2;
-   __m256d mass_tmp;
-   __m256d ai_tmp_v0;
-   __m256d ai_tmp_v1;
-   __m256d ai_tmp_v2;
-   __m256d eps2_tmp;
-   eps2_tmp = _mm256_set1_pd(eps2);
-   __m256d g_tmp;
-   g_tmp = _mm256_set1_pd(g);
-   __m256d dr_tmp_v0;
-   __m256d dr_tmp_v1;
-   __m256d dr_tmp_v2;
-   __m256d x0_tmp;
-   __m256d x1_tmp;
-   for (i = 0; i < n; i += 4) {
-      int index_gather_0[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
-      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
-      int index_gather_1[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
-      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
-      int index_gather_2[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
-      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
-      ai_tmp_v0 = _mm256_set1_pd(0.0);
[…]

### 2024-02-06 dsl/gen/pyker.py

@@ -54,7 +54,7 @@ def Parse(file_str):
 
 def inv_op(arg, func_name, inv_func_name):
     
-    if type(arg) is Symbol or arg is Integer(-1):
+    if type(arg) is Symbol or arg is Integer(-1) or type(arg) is Float:
         return arg, None
     try:
         if str(arg.name) == func_name and Integer(-1) in arg.function_args:
@@ -70,11 +70,14 @@ def add_pattern(left_arg, right_arg):
         #SIMD演算
         left_arg, func_name1 = inv_op(left_arg, MUL_FUNCTION_NAME, SUB_FUNCTION_NAME)
         right_arg, func_name2 = inv_op(right_arg,MUL_FUNCTION_NAME, SUB_FUNCTION_NAME)
-        if func_name1 == SUB_FUNCTION_NAME or func_name2 == SUB_FUNCTION_NAME:
+        if func_name1 == SUB_FUNCTION_NAME:
+            return FunctionCall(SUB_FUNCTION_NAME, [right_arg, left_arg])
+        elif func_name2 == SUB_FUNCTION_NAME:
             return FunctionCall(SUB_FUNCTION_NAME, [left_arg, right_arg])
         else:
             return FunctionCall(ADD_FUNCTION_NAME, [left_arg, right_arg])
     else:
+        
         return Add(left_arg, right_arg, evaluate=False)
 
 def mul_pattern(left_arg, right_arg):
@@ -149,12 +152,13 @@ def pow_pattern(base_arg, exp_arg):
             num = exp_arg.numerator
             deno = exp_arg.denominator
             if num == 1:
-                new_expr = Pow(base_arg, exp_arg)
+                new_expr = Pow(base_arg, exp_arg, evaluate=False)
             else:
                 new_expr = pow_to_mul(base_arg, num)
                 new_exp_arg = Rational(Integer(1), deno)
                 new_expr = Pow(new_expr, new_exp_arg, evaluate=False)
         else:
+            # print(f'pow_pattern {base_arg} {exp_arg}')
             new_expr = Pow(base_arg, exp_arg, evaluate=False)
         return new_expr
 
@@ -191,8 +195,13 @@ def trans_mid_expr(arg, name_variable_map, i):
             ret = Symbol(v.get_tmp_name(i))
         # elif str(arg) in prim_map:
         return ret
-    elif arg is Integer(-1) or arg is Rational(1, 2) or type(arg) is Integer:
[…]

### 2024-02-06 dsl/simd/test_mm_op.cpp

@@ -27,6 +27,10 @@ int main() {
     int n = 1000;
     double a[n], b[n], c[n];
 
-    
 
+    int index_gather_0[4] = {0, 3, 6, 9};
+    __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
+    // printf("%lld %lld %lld \n", vindex_gather_0[0], vindex_gather_0[1], vindex_gather_0[2]);
+    printf("%d\n", vindex_gather_0);
+    // _mm256d xs = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
 }

### 2024-02-07 dsl/experiment/LennardJones/check_code.cpp
20240207

@@ -1,0 +1,127 @@
+#include<x86intrin.h>
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+
+struct EPI{
+  double rx,ry,rz;
+};
+
+struct EPJ{
+   double rx,ry,rz,eps;
+};
+
+struct FORCE{
+  double fx,fy,fz;
+  double p;
+};
+
+#include "pikg_kernel.hpp"
+// #include "harp_pyker_code.hpp"
+// #include "pyker_code.hpp"
+// #include "avx2_code.hpp"
+#include "pyker_simd_code.hpp"
+
+// 乱数を生成するための関数
+double rand_double(double min, double max) {
+   return min + (double)rand() / ((double)RAND_MAX / (max - min));
+}
+
+
+double calculate_difference(double a, double b) {
+   double diff = 0.0;
+   diff += fabs(a - b);   
+   return diff;
+}
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n = 10;
+
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI* epi = new EPI[n];
+   EPJ* epj = new EPJ[n];
+   FORCE* force = new FORCE[n];
+   Kernel pikg_kernel;
+
+   double (*ri)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
+   double (*rj)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
+   double (*fr)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
+   double (*p) = static_cast<double(*)>(aligned_alloc(32, n * 3 * sizeof(double)));
+   double eps = pow(2, -5);
+   // epiとepjの変数を乱数で初期化
+   for(int i = 0; i < nepi; ++i) {
+      epi[i].rx = rand_double(-1.0, 1.0);
+      epi[i].ry = rand_double(-1.0, 1.0);
+      epi[i].rz = rand_double(-1.0, 1.0);
+      epj[i].eps = pow(2, -5);
+      epj[i].rx = epi[i].rx;
[…]

### 2024-02-07 dsl/experiment/LennardJones/correct_code/pyker_simd_code.hpp

@@ -1,0 +1,78 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double ri[][3], double rj[][3], double fr[][3], double p[], double eps){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d fr_tmp_v0;
+   __m256d fr_tmp_v1;
+   __m256d fr_tmp_v2;
+   __m256d p_tmp;
+   __m256d eps_tmp;
+   eps_tmp = _mm256_set1_pd(eps);
+   __m256d float_4_tmp;
+   float_4_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(48.0);
+   __m256d float_2_tmp;
+   float_2_tmp = _mm256_set1_pd(24.0);
+   __m256d float_3_tmp;
+   float_3_tmp = _mm256_set1_pd(4.0);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r2i_tmp;
+   __m256d f_tmp;
+   __m256d x0_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      ri_tmp_v1 = _mm256_i32gather_pd(&ri[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
[…]

### 2024-02-07 dsl/experiment/LennardJones/pikg_code.hpp

@@ -1,0 +1,154 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EP* __restrict__ epi,const int ni,const EP* __restrict__ epj,const int nj,Force* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EP) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EP) == 24,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(Force) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+Force* force_tmp = new Force[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I1_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I1_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
+delete[] force_tmp;
+} // if(kernel_id == 0)
+if(kernel_id == 1) Kernel_I1_J1(epi,ni,epj,nj,force);
[…]

### 2024-02-07 dsl/experiment/LennardJones/pikg_kernel.hpp

@@ -1,0 +1,157 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I1_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I1_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
+delete[] force_tmp;
+} // if(kernel_id == 0)
+if(kernel_id == 1) Kernel_I1_J1(epi,ni,epj,nj,force);
+} // operator() definition 
[…]

### 2024-02-07 dsl/experiment/LennardJones/pyker_code.hpp

@@ -1,0 +1,33 @@
+#include<math.h>
+;
+int kernel(int n, double ri[][3], double rj[][3], double fr[][3], double p[], double eps){
+   int i;
+   int j;
+   double dr_v0;
+   double dr_v1;
+   double dr_v2;
+   double r2;
+   double r2i;
+   double f;
+   double x0;
+   for (i = 0; i < n; i += 1) {
+      ;
+      ;
+      for (j = 0; j < n; j += 1) {
+         ;
+         dr_v0 = ri[i][0] - rj[j][0];
+         dr_v1 = ri[i][1] - rj[j][1];
+         dr_v2 = ri[i][2] - rj[j][2];
+         r2 = eps + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
+         r2i = 1.0/r2;
+         x0 = r2i*(r2i*r2i);
+         f = (r2i*(r2i*(r2i*r2i)))*(48.0*x0 - 24.0);
+         fr[i][0] += dr_v0*f;
+         fr[i][1] += dr_v1*f;
+         fr[i][2] += dr_v2*f;
+         p[i] += (4.0*x0)*(x0 - 1.0);
+      };
+      ;
+   };
+   return 0;
+};

### 2024-02-07 dsl/gen/Var.py

@@ -22,6 +22,7 @@ class Var:
     argument = None
     vec_index = 1
     origin = None
+    tmp_name = None
 
     def index_def(self):
         if self.struct_name == 'EPI' or self.struct_name == 'FORCE':
@@ -62,13 +63,13 @@ class Var:
     def set_var(self, word_lst):
 
         #EPI,EPJ,FORCEを正規表現で判定する
-        struct_name_pattern = r'(EP(I|J)|FORCE).\w+'
+        struct_name_pattern = r'(EP(I|J)|FORCE)'
         check_pat = re.match(struct_name_pattern, word_lst[0])
 
         #合えば、メンバー変数と構造体名をセットし、その後、変数宣言の処理
         if check_pat:
             s = check_pat.group()
-            self.struct_name, self.memb_name = s.split('.')
+            self.struct_name = s
             self.set_type(word_lst[1:])
         #合わなければ、変数宣言の処理
         else:

### 2024-02-07 dsl/gen/gen_0122_simd_correctans.hpp

@@ -1,4 +1,3 @@
-#include<math.h>
 #include<x86intrin.h>;
 int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;

### 2024-02-07 dsl/gen/gravity_code.hpp

@@ -1,115 +1,70 @@
 #include<math.h>
 #include<x86intrin.h>;
-int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   __m256d ri_tmp_v0;
-   __m256d ri_tmp_v1;
-   __m256d ri_tmp_v2;
-   __m256d vi_tmp_v0;
-   __m256d vi_tmp_v1;
-   __m256d vi_tmp_v2;
-   __m256d rj_tmp_v0;
-   __m256d rj_tmp_v1;
-   __m256d rj_tmp_v2;
-   __m256d vj_tmp_v0;
-   __m256d vj_tmp_v1;
-   __m256d vj_tmp_v2;
-   __m256d mj_tmp;
+   __m256d xi_tmp_v0;
+   __m256d xi_tmp_v1;
+   __m256d xi_tmp_v2;
+   __m256d xj_tmp_v0;
+   __m256d xj_tmp_v1;
+   __m256d xj_tmp_v2;
+   __m256d mass_tmp;
+   __m256d ai_tmp_v0;
+   __m256d ai_tmp_v1;
+   __m256d ai_tmp_v2;
    __m256d eps2_tmp;
-   __m256d F_tmp_v0;
-   __m256d F_tmp_v1;
-   __m256d F_tmp_v2;
-   __m256d J_tmp_v0;
-   __m256d J_tmp_v1;
-   __m256d J_tmp_v2;
+   eps2_tmp = _mm256_set1_pd(eps2);
+   __m256d g_tmp;
+   g_tmp = _mm256_set1_pd(g);
    __m256d float_0_tmp;
-   float_0_tmp = _mm256_set1_pd(3.0);
+   float_0_tmp = _mm256_set1_pd(1.0);
    __m256d dr_tmp_v0;
    __m256d dr_tmp_v1;
    __m256d dr_tmp_v2;
-   __m256d dv_tmp_v0;
-   __m256d dv_tmp_v1;
-   __m256d dv_tmp_v2;
-   __m256d r2_tmp;
-   __m256d rv_tmp;
[…]

### 2024-02-07 dsl/gen/pyker.py

@@ -50,6 +50,9 @@ def Parse(file_str):
             #変数宣言だった場合型の情報をVariableから取得
             v = Var.Var(col)
             name_variable_map[v.name] = v
+    
+    if SIMD:
+        num_var_def(expr_list, name_variable_map)
 
     return expr_list, name_variable_map
 
@@ -83,6 +86,8 @@ def add_pattern(left_arg, right_arg):
 
 def mul_pattern(left_arg, right_arg):
     if SIMD:
+        # if type(left_arg) is Integer(-1) and type(right_arg) is Float:
+            
         left_arg, func_name1 = inv_op(left_arg, POW_FUNCTION_NAME, DIV_FUNCTION_NAME)
         right_arg, func_name2 = inv_op(right_arg, POW_FUNCTION_NAME, DIV_FUNCTION_NAME)
         if func_name1 == DIV_FUNCTION_NAME or func_name2 == DIV_FUNCTION_NAME:
@@ -388,8 +393,9 @@ def avx2_store(v, i):
             code_list.append(Assignment(Symbol(f'{v.name}[i{inc}][{i}]'), 
                                         Symbol(tmp_vec_name + f'[{ii}]')))
     else:
+        
         code_list.append(FunctionCall('_mm256_store_' + type_name, 
-                            [Symbol(f'&{v.name}[i]'), Symbol(v.tmp_name + tmp_vec_name)]))
+                            [Symbol(f'&{v.name}[i]'), Symbol(tmp_vec_name)]))
  
     return CodeBlock(*code_list)
 
@@ -429,8 +435,10 @@ def in_prim_map(v, prim_map):
         return False
 
 
+float_num = 0
 def declear_tmp_var(name_variable_map, prim_map):
-
+    # global float_num
+    # float_num = 0
     dec_list = []
 
     for v in name_variable_map.values():
@@ -452,13 +460,19 @@ def declear_tmp_var(name_variable_map, prim_map):
                 
                 # if tmp_var == '':
                     #debag
+                # if type(v.symbol) is Float:
+                #     tmp_var += str(float_num)
+                #     v.tmp_name = tmp_var
+                    
                 tmp = Variable(Symbol(tmp_var), type=type_)
 
                 tmp_dec = Declaration(Variable(Symbol(tmp_var), type=type_))
                 dec_list.append(tmp_dec)
                 if type(v.symbol) is Float:
                     set_method = FunctionCall('_mm256_set1_pd', [v.symbol])
+                    
[…]

### 2024-02-08 paper/paper.tex
20240207
before interprinta

@@
 \usepackage[dvipdfmx]{graphicx}
+
 \lstset{
@@
 
+\begin{lstlisting}[frame=single]
+  dx0 = pos[i][0] - pos[j][0]
+  dx1 = pos[i + 1][0] - pos[j][0]
+  dx2 = pos[i + 2][0] - pos[j][0]
+  dx3 = pos[i + 3][0] - pos[j][0]
+\end{lstlisting}
+
+\begin{lstlisting}[frame=single]
+  (x1, x2, x3, x4) + (y1, y2, y3, y)
+
+\end{lstlisting}
+
 When storing computation results, addresses may 
@@
 
-\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
+\begin{lstlisting}[frame=single, caption=skeleton code, label=fuga]
 int kernel(double xi[][3], double xj[][3], double ai[][3], double eps2, int n){
 	// (1).preprocess
-	for(int i = 0;i < n;i += 4) {
-		// (2).load EPI 
-		// (3).Initialization of tmporary force
+	for(int i = 0;i < n;i += 4) { // (2)Increment the number of parallels
+		// (3).load EPI
+		// (4).Initialization of tmporary force
 		for(int j = 0;j < n;j += 1) {
-				// (4). calculate interparticle interactions
+        // (5) load EPJ
+				// (6) calculate interparticle interactions
 		}
-		// (5). Store calculation result in the FORCE
+		// (7). Store calculation result in the FORCE
 	}

### 2024-02-08 dsl/gen/gen_0122_simd_correctans.hpp

@@ -62,3 +62,11 @@ int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3],
    };
    return 0;
 };
+
+void test_simd(double A[], double B[], double C[], int n){
+   for(int i = 0;i < n;i += 4) {
+      __m256d vec_a = _mm256_load_pd(&A[i]);
+      __m256d vec_b = _mm256_load_pd(&B[i]);
+      __m256d vec_a = _mm256_load_pd(&A[i]);
+   }
+}

### 2024-02-08 dsl/gen/gravity_code.hpp

@@ -1,70 +1,31 @@
 #include<math.h>
-#include<x86intrin.h>;
+;
 int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
    int i;
    int j;
-   __m256d xi_tmp_v0;
-   __m256d xi_tmp_v1;
-   __m256d xi_tmp_v2;
-   __m256d xj_tmp_v0;
-   __m256d xj_tmp_v1;
-   __m256d xj_tmp_v2;
-   __m256d mass_tmp;
-   __m256d ai_tmp_v0;
-   __m256d ai_tmp_v1;
-   __m256d ai_tmp_v2;
-   __m256d eps2_tmp;
-   eps2_tmp = _mm256_set1_pd(eps2);
-   __m256d g_tmp;
-   g_tmp = _mm256_set1_pd(g);
-   __m256d float_0_tmp;
-   float_0_tmp = _mm256_set1_pd(1.0);
-   __m256d dr_tmp_v0;
-   __m256d dr_tmp_v1;
-   __m256d dr_tmp_v2;
-   __m256d nor_inv_tmp_v0;
-   __m256d nor_inv_tmp_v1;
-   __m256d nor_inv_tmp_v2;
-   for (i = 0; i < n; i += 4) {
-      int index_gather_0[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
-      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
-      int index_gather_1[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
-      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
-      int index_gather_2[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
-      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
[…]

### 2024-02-08 dsl/gen/pyker.py

@@ -1161,7 +1161,7 @@ def trans_new_op(expr_list, arg_ret_map_list):
     for expr in expr_list:
         arg_ret_map = arg_ret_map_list[expr.lhs]
         # new_expr = trans_sub(expr.rhs)
-
+        print(f'trans new op{arg_ret_map}')
         new_expr = trans_dot(expr.rhs, arg_ret_map)
         new_expr_list.append(Assignment(expr.lhs, new_expr))
          
@@ -1384,33 +1384,21 @@ def main():
     # print(arg_ret_map_list)
     new_op_expr_list = trans_new_op(expr_list, arg_ret_map_list)
     # arg_ret_map_list = get_arg_ret_map_list(new_op_expr_list, name_variable_map)
-    # check_tree(new_op_expr_list)
+    check_tree(new_op_expr_list)
 
     after_cse_expr_list = apply_cse(new_op_expr_list, name_variable_map)
-    prim_map = type_inference(biexpr_list, name_variable_map, arg_ret_map_list)
     #型推論　それから一次変数の型を決定
     # check_prim_map(prim_map) 
      
     #構文木を完全2分木にする処理
     biexpr_list = expr_binary_tree(after_cse_expr_list)
+    prim_map = type_inference(biexpr_list, name_variable_map, arg_ret_map_list)
     
-    # expr_binary_treeのテスト用
-    # check_new_bitree(biexpr_list)
-
-
-    # check_name_table(name_variable_map)
-    #type_inferenceのテスト用
-    # check_type_infer(prim_map) 
 
     # 木構造のチェック
     # check_tree(biexpr_list)
     mid_expr_list = trans_mid_expr_list(biexpr_list, name_variable_map)
-    # print('mid_expr_list')
-    # check_tree(mid_expr_list)
-    # if SIMD:
-    #     mid_expr_list = trans_var_names(mid_expr_list, name_variable_map)
-    # print(f'exe_expr_list {mid_expr_list}')
-    # check_tree(mid_expr_list[0])
+    
     s = CodeGen(mid_expr_list, name_variable_map, prim_map)
 
     file_name = 'gravity_code'

### 2024-02-09 paper/paper.tex
Lennard Jones data

@@
 
-\begin{lstlisting}[frame=single, caption=hoge]
-//(1) include part
-#include<math>
-#include<immintrin.h>
-int kernel( (2) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
-  //(3) decleare tmp variable
-  int i;
-  int j;
-  __m256d xi_tmp_v0;
-  __m256d xi_tmp_v1;  
-  __m256d xi_tmp_v2;
-  __m256d eps2_tmp;
-  // ... 
-  // ... 
-  // ... 
-  //(4) def not class variables
-  eps2_tmp = _mm256_set1_pd(eps2);
-  // ... 
-  // ... 
-  // ...
+\section{Experiments}
 
-  // (5) loop increment
-  for(i = 0;i < n;i += 4) {
-    // (6) Load EPI variable part
-    int index_gather_0[4] = {0, 3, 6, 9};
-    __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
-    // ... 
-    // ... 
-    // ...
+\subsection{gravity interparticle}
+ほぼ同じコードで実行
 
-    // (7) initialize result temporary variable
-    ai_tmp_v0 = _mm256_set1_pd(0.0);
-    ai_tmp_v1 = _mm256_set1_pd(0.0);
-    ai_tmp_v2 = _mm256_set1_pd(0.0);
-
-    for(j = 0;j < n;j += 1) {
-      // (8) Load EPJ variable part
-         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
-         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
-         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
-        // ... 
-        // ... 
-        // ...
-
-      // (9) calculate interparticle
-        dr_tmp_v0 = _mm256_sub_pd(xj_tmp_v0, xi_tmp_v0);
-        dr_tmp_v1 = _mm256_sub_pd(xj_tmp_v1, xi_tmp_v1);
-        dr_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
-        ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(//.....));
-        ai_tmp_v1 += _mm256_div_pd(_mm256_mul_pd(//.....));
-        ai_tmp_v2 += _mm256_div_pd(_mm256_mul_pd(//.....));
-
-    }
-
-    // (10) Store result part
-
-  }
-  return 0;
-}
+\begin{lstlisting}[frame=single, caption=Nbody-kernel.pyker, label=Nbody-kernel.pyker]
+  EPI vec3<F64> ri
+  EPJ vec3<F64> rj
+  EPJ F64 mass
+  EPJ F64 eps2
+  FORCE vec3<F64> ai
+  rij = ri - rj
+  r2 = rij * rij + eps2
+  r_inv = 1.0 / sqrt(r2)
+  r2_inv = r_inv * r_inv
+  mr_inv = mass * r_inv
+  mr3_inv = r2_inv * mr_inv
+  ai = mr3_inv * rij
   \end{lstlisting}
 
-\section{Experiments}
+\begin{lstlisting}[frame=single, caption=Nbody-kernel.pikg, label=Nbody-kernel.pikg]
+  EPI F64vec ri:r
+  EPJ F64vec rj:r
+  EPJ F64 mj:m
+
+  EPJ F64 eps2:eps
+
+  FORCE F64vec ai:acc
+
+  rij = ri - rj
+  r2 = rij * rij + eps2
+  r_inv  = rsqrt(r2)
+  r2_inv = r_inv * r_inv
+  mr_inv  = mj * r_inv
+  mr3_inv = r2_inv * mr_inv
+  ai += mr3_inv * rij
+
+\end{lstlisting}
+
+non-simd
+
+g++ -O3
+
+\begin{tabular}{|l|r|r|} \hline
+  N & Pyker & PIKG \\ \hline
+  25000 & 6.725156 & 4.444766 \\
+  10000 & 0.738918sec & 0.517324sec \\
+
+ \\ \hline
+\end{tabular}
+
+\begin{lstlisting}[frame=single, caption=Nbody-kernel.pikg, label=Nbody-kernel.pikg]
+  g++ -O3 -I ~/school/PIKG/PIKG/inc -mavx2 -mfma gravity_interparticle.cpp
+
+  \end{lstlisting}
+
+  \begin{tabular}{|l|r|r|} \hline
+    N & Pyker(sec) & PIKG(sec) \\ \hline
+    50000 & 5.119071 & 3.333270\\
+    25000 & 1.218129 & 1.148511 \\
+    10000 & 0.143777 & 0.101594 \\
+    1000 &  0.003521 & 0.002168 \\ \hline
+  \end{tabular}
+
+% \begin{tabular}{lrr}
+%   N & pyker & PIKG \\
+%   10000 & 0.143777sec & 0.101594sec \\
+%   x & y & z 
+%  \end{tabular}
+
+\subsection{LennardJones}
+
+\begin{lstlisting}[frame=single, caption=LennardJones-kernel.pyker, label=LennardJones-kernel.pyker]
+EPI F64 rix
+EPI F64 riy
+EPI F64 riz
+EPJ F64 rjx
+EPJ F64 rjy
+EPJ F64 rjz
+EPJ F64 eps
+
+FORCE F64 fx
+FORCE F64 fy
+FORCE F64 fz
+FORCE F64 p
+dx = rix - rjx
+dy = riy - rjy
+dz = riz - rjz
+r2 = dx * dx + dy * dy + dz * dz + eps
+r2i = 1.0 / r2
+r6i = r2i * r2i * r2i
+f = (48.0* r6i - 24.0) * r6i * r2i
+fx = f * dx
+fy = f * dy
+fz = f * dz
+p = 4.0 * (r6i) * (r6i - 1.0)
+\end{lstlisting}
+\begin{lstlisting}[frame=single, caption=LennardJones-kernel.pyker, label=LennardJones-kernel.pyker]
+  EPI F64 rix:rx
+  EPI F64 riy:ry
+  EPI F64 riz:rz
+
+  EPJ F64 rjx:rx
+  EPJ F64 rjy:ry
+  EPJ F64 rjz:rz
+  EPJ F64 eps2:eps
+
+  FORCE F64 fx:fx
+  FORCE F64 fy:fy
+  FORCE F64 fz:fz
+  FORCE F64 p:p
+
+  dx  = rix - rjx
+  dy = riy - rjy
+  dz  = riz - rjz
+  r2  = dx * dx + dy * dy + dz * dz + eps2
+  r2i = 1.0 / r2
+  r6i = r2i * r2i * r2i
+  f = (48.0 * r6i - 24.0) * r6i * r2i
+  fx += f * dx
+  fy += f * dy
+  fz += f * dz
+  p += 4.0 * r6i*(r6i - 1.0)
+
+\end{lstlisting}
+
+non-simd
+\begin{tabular}{|l|r|r|} \hline
+  N & Pyker & PIKG \\ \hline
+  50000 & 40.736862 & 11.656278 \\
+  25000 & 10.662050 & 3.521253 \\
+  10000 & 0.985475 & 0.442775 \\
+ \\ \hline
+\end{tabular}
+
+simd
+\begin{tabular}{|l|r|r|} \hline
+  N & Pyker & PIKG \\ \hline
+  50000 & 3.702871  & 2.838773\\
+  25000 & 0.838122 & 0.9904373 \\
+  10000 & 0.134388 & 0.215270 \\
+
+ \\ \hline
+\end{tabular}
 

### 2024-02-09 dsl/experiment/Hermite/LennardJones.cpp

@@ -25,10 +25,10 @@ struct FORCE {
    pikg_f64vec3 j;
 };
 
-#include "sample1_kernel.hpp"
-// #include "harp_pyker_code.hpp"
-#include "harp_pyker_simdcode.hpp"
-// #include "avx2_code.hpp"
+// #include "pikg_kernel.hpp"
+// #include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel.hpp"
+// #include "pyker_kernel_AVX2.hpp"
 
 // 乱数を生成するための関数
 double rand_double(double min, double max) {
@@ -56,14 +56,20 @@ int main() {
    Kernel pikg_kernel;
 
 
-   double (*ri)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
-   double (*vi)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
+   double (*rix) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjx) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
    double (*rj)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double (*vj)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double *mj = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
    double *eps2 = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
-   double (*F)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
-   double (*J)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
+   double (*fx) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
[…]

### 2024-02-09 dsl/experiment/LennardJones_ver2/LennardJones.cpp

@@ -1,0 +1,142 @@
+#include<x86intrin.h>
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+// using namespace std;
+
+
+struct EPI{
+  double rx,ry,rz;
+};
+
+struct EPJ{
+   double rx,ry,rz;
+   double eps;
+};
+
+struct FORCE{
+  double fx,fy,fz;
+  double p;
+};
+
+// #include "pikg_kernel.hpp"
+// #include "pyker_kernel.hpp"
+#include "pikg_kernel_AVX2.hpp"
+#include "pyker_kernel_AVX2.hpp"
+
+// 乱数を生成するための関数
+double rand_double(double min, double max) {
+   return min + (double)rand() / ((double)RAND_MAX / (max - min));
+}
+
+
+double calculate_difference(double a, double b) {
+   double diff = 0.0;
+   diff += fabs(a - b);   
+   return diff;
+}
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n;
+
+   std::cin >> n;
+
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI *epi = new EPI[nepi];
+   EPJ *epj = new EPJ[nepj];
+   FORCE *force = new FORCE[n];
+   Kernel pikg_kernel;
+
+
+   double (*rix) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjx) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double *mj = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
[…]

### 2024-02-09 dsl/experiment/LennardJones_ver2/pikg/pikg_kernel.hpp

@@ -10,8 +10,8 @@ void initialize(){
 int kernel_id = 0;
 void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
 static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
-static_assert(sizeof(EPJ) == 40,"check consistency of EPJ member variable definition between PIKG source and original source");
-static_assert(sizeof(FORCE) == 24,"check consistency of FORCE member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
 if(kernel_select>=0) kernel_id = kernel_select;
 if(kernel_id == 0){
 std::cout << "ni: " << ni << " nj:" << nj << std::endl;
@@ -38,29 +38,45 @@ void Kernel_I1_J1(const EPI* __restrict__ epi,const PIKG::S32 ni,const EPJ* __re
 PIKG::S32 i;
 PIKG::S32 j;
 for(i = 0;i < ni;++i){
-PIKG::F64vec ri;
+PIKG::F64 rix;
 
-ri.x = epi[i+0].r.x;
-ri.y = epi[i+0].r.y;
-ri.z = epi[i+0].r.z;
-PIKG::F64vec ai;
+rix = epi[i+0].rx;
+PIKG::F64 riy;
 
-ai.x = 0.0;
-ai.y = 0.0;
-ai.z = 0.0;
+riy = epi[i+0].ry;
+PIKG::F64 riz;
+
+riz = epi[i+0].rz;
+PIKG::F64 fx;
+
[…]

### 2024-02-09 dsl/experiment/LennardJones_ver2/pikg/pikg_kernel_AVX2.hpp

@@ -1,0 +1,748 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+#include <pikg_avx2.hpp>
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I4_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I4_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
[…]

### 2024-02-09 dsl/experiment/LennardJones_ver2/pyker_kernel_AVX2.hpp

@@ -1,0 +1,63 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
+   int i;
+   int j;
+   __m256d rix_tmp;
+   __m256d riy_tmp;
+   __m256d riz_tmp;
+   __m256d rjx_tmp;
+   __m256d rjy_tmp;
+   __m256d rjz_tmp;
+   __m256d eps_tmp;
+   __m256d fx_tmp;
+   __m256d fy_tmp;
+   __m256d fz_tmp;
+   __m256d p_tmp;
+   __m256d float_4_tmp;
+   float_4_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(48.0);
+   __m256d float_2_tmp;
+   float_2_tmp = _mm256_set1_pd(24.0);
+   __m256d float_3_tmp;
+   float_3_tmp = _mm256_set1_pd(4.0);
+   __m256d dx_tmp;
+   __m256d dy_tmp;
+   __m256d dz_tmp;
+   __m256d r2_tmp;
+   __m256d r2i_tmp;
+   __m256d r6i_tmp;
+   __m256d f_tmp;
+   for (i = 0; i < n; i += 4) {
+      rix_tmp = _mm256_load_pd(&rix[i]);
+      riy_tmp = _mm256_load_pd(&riy[i]);
+      riz_tmp = _mm256_load_pd(&riz[i]);
+      fx_tmp = _mm256_set1_pd(0.0);
+      fy_tmp = _mm256_set1_pd(0.0);
+      fz_tmp = _mm256_set1_pd(0.0);
+      p_tmp = _mm256_set1_pd(0.0);
+      for (j = 0; j < n; j += 1) {
+         rjx_tmp = _mm256_set1_pd(rjx[j]);
+         rjy_tmp = _mm256_set1_pd(rjy[j]);
+         rjz_tmp = _mm256_set1_pd(rjz[j]);
+         eps_tmp = _mm256_set1_pd(eps[j]);
+         dx_tmp = _mm256_sub_pd(rix_tmp, rjx_tmp);
[…]

### 2024-02-09 dsl/experiment/Nbody/gravity_interparticle.cpp

@@ -14,7 +14,7 @@ struct EPI {
 struct EPJ{
    pikg_f64vec3 r;
    double m;
-   double eps
+   double eps;
 };
 
 struct FORCE {
@@ -23,6 +23,9 @@ struct FORCE {
 
 #include "pikg_kernel.hpp"
 #include "pyker_code.hpp"
+
+// #include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel_AVX2.hpp"
 
 // 乱数を生成するための関数
 double rand_double(double min, double max) {
@@ -47,7 +50,7 @@ double calculate_difference(double a, double b) {
 int main() {
    srand((unsigned)time(NULL)); // 乱数のシードを設定
 
-   int n = 50000;
+   int n = 25000;
 
    //PIKG用のコード
    const int nepi = n; 
@@ -58,22 +61,19 @@ int main() {
    Kernel pikg_kernel;
 
 
-   double (*xi)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
+   double (*ri)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double (*vi)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double (*rj)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double (*vj)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double))); 
    double *mj = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
    double *eps2 = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
-   double (*F)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
+   double (*ai)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
    double (*J)[3] = static_cast<double(*)[3]>(aligned_alloc(32, n * 3 * sizeof(double)));
 
    // epiとepjの変数を乱数で初期化
    for(int i = 0; i < nepi; ++i) {
       epi[i].r = {rand_double(-1.0, 1.0), rand_double(-1.0, 1.0), rand_double(-1.0, 1.0)};
[…]

### 2024-02-09 dsl/experiment/Nbody/pyker_code.hpp

@@ -1,22 +1,32 @@
 #include<math.h>
 ;
-int kernel(int n, double xi[][3], double xj[][3], double mass[], double ai[][3], double eps2, double g){
+int kernel(int n, double ri[][3], double rj[][3], double mj[], double eps2[], double ai[][3]){
    int i;
    int j;
-   double dr_v0;
-   double dr_v1;
-   double dr_v2;
+   double rij_v0;
+   double rij_v1;
+   double rij_v2;
+   double r2;
+   double r_inv;
+   double r2_inv;
+   double mr_inv;
+   double mr3_inv;
    for (i = 0; i < n; i += 1) {
       ;
       ;
       for (j = 0; j < n; j += 1) {
          ;
-         dr_v0 = -xi[i][0] + xj[j][0];
-         dr_v1 = -xi[i][1] + xj[j][1];
-         dr_v2 = -xi[i][2] + xj[j][2];
-         ai[i][0] += (mass[j]*(dr_v0*g))/sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)));
-         ai[i][1] += (mass[j]*(dr_v1*g))/sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)));
-         ai[i][2] += (mass[j]*(dr_v2*g))/sqrt(eps2 + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1)));
+         rij_v0 = ri[i][0] - rj[j][0];
+         rij_v1 = ri[i][1] - rj[j][1];
+         rij_v2 = ri[i][2] - rj[j][2];
+         r2 = eps2[j] + (rij_v2*rij_v2 + (rij_v0*rij_v0 + rij_v1*rij_v1));
+         r_inv = 1.0/sqrt(r2);
+         r2_inv = r_inv*r_inv;
+         mr_inv = mj[j]*r_inv;
+         mr3_inv = mr_inv*r2_inv;
+         ai[i][0] += mr3_inv*rij_v0;
+         ai[i][1] += mr3_inv*rij_v1;
+         ai[i][2] += mr3_inv*rij_v2;
       };
       ;
    };

### 2024-02-09 dsl/experiment/Nbody/pyker_kernel_AVX2.hpp

@@ -1,0 +1,72 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double ri[][3], double rj[][3], double mass[], double eps2[], double ai[][3]){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d mass_tmp;
+   __m256d eps2_tmp;
+   __m256d ai_tmp_v0;
+   __m256d ai_tmp_v1;
+   __m256d ai_tmp_v2;
+   __m256d float_0_tmp;
+   float_0_tmp = _mm256_set1_pd(1.0);
+   __m256d rij_tmp_v0;
+   __m256d rij_tmp_v1;
+   __m256d rij_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r_inv_tmp;
+   __m256d r2_inv_tmp;
+   __m256d mr_inv_tmp;
+   __m256d mr3_inv_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      ri_tmp_v1 = _mm256_i32gather_pd(&ri[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
+      ri_tmp_v2 = _mm256_i32gather_pd(&ri[i][2], vindex_gather_2, 8);
+      ai_tmp_v0 = _mm256_set1_pd(0.0);
+      ai_tmp_v1 = _mm256_set1_pd(0.0);
+      ai_tmp_v2 = _mm256_set1_pd(0.0);
[…]

### 2024-02-09 dsl/gen/check_argparse.py

@@ -1,0 +1,14 @@
+import argparse
+import sys
+def sys_args():
+    parser = argparse.ArgumentParser()
+    
+    parser.add_argument("file")
+    parser.add_argument("--AVX2")
+    parser.add_argument("--outputfile")
+    return parser
+
+def main():
+   args = sys_args() 
+
+   print(args.file)

### 2024-02-09 dsl/gen/pyker.py

@@ -60,26 +60,35 @@ def inv_op(arg, func_name, inv_func_name):
     
     if type(arg) is Symbol or arg is Integer(-1) or type(arg) is Float:
         return arg, None
+    
     try:
         if str(arg.name) == func_name and Integer(-1) in arg.function_args:
             ret = list(filter(lambda x: x is not Integer(-1), arg.function_args))
             return ret[0], inv_func_name
     except AttributeError:
         print(arg)
+    # if type(arg) is Float and float(arg) < 0:
+    #     return (arg * -1), inv_func_name
     else:
         return arg, None
 
 def add_pattern(left_arg, right_arg):
     if SIMD:
+        # print(left_arg, right_arg)
         #SIMD演算
         left_arg, func_name1 = inv_op(left_arg, MUL_FUNCTION_NAME, SUB_FUNCTION_NAME)
         right_arg, func_name2 = inv_op(right_arg,MUL_FUNCTION_NAME, SUB_FUNCTION_NAME)
+        new_expr = None
         if func_name1 == SUB_FUNCTION_NAME:
-            return FunctionCall(SUB_FUNCTION_NAME, [right_arg, left_arg])
+            new_expr = FunctionCall(SUB_FUNCTION_NAME, [right_arg, left_arg])
         elif func_name2 == SUB_FUNCTION_NAME:
-            return FunctionCall(SUB_FUNCTION_NAME, [left_arg, right_arg])
+            new_expr = FunctionCall(SUB_FUNCTION_NAME, [left_arg, right_arg])
         else:
-            return FunctionCall(ADD_FUNCTION_NAME, [left_arg, right_arg])
+            new_expr = FunctionCall(ADD_FUNCTION_NAME, [left_arg, right_arg])
+        # if type(left_arg) is Float:
+        #     print(srepr(left_arg))
+        # print(new_expr)
+        return new_expr
     else:
         
         return Add(left_arg, right_arg, evaluate=False)
@@ -160,7 +169,7 @@ def pow_pattern(base_arg, exp_arg):
     else:
         if type(exp_arg) is Integer: 
             new_expr = pow_to_mul(base_arg, int(exp_arg))
-            print(f'in pow_pattern {base_arg}, {exp_arg}')
+            # print(f'in pow_pattern {base_arg}, {exp_arg}')
         elif type(exp_arg) is Rational:
             num = exp_arg.numerator
             deno = exp_arg.denominator
[…]

### 2024-02-09 dsl/simd/interparticle.cpp

@@ -51,12 +51,7 @@ for (int i = 0; i < ni; i++) {
 }
 
 }
-void evaluate_gravity_simd(
-    int ni,
-    int nj,
-    double xi[],
-    double yi[],
-    double zi[],
+void evaluate_gravity_simd(int ni, int nj, double xi[], double yi[], double zi[],
     double xj[],
     double yj[],
     double zj[],

### 2024-02-09 paper/paper.tex
japanese of introduction ver1

@@
 \usepackage[dvipdfmx]{graphicx}
+\usepackage{physics}
+\bibliographystyle{ieicetr}
 
@@
 
-\bibliographystyle{ieice}
+% \bibliographystyle{ieice}
 \author{Ryuki Hiwada}
@@
 \begin{document}
+
 \maketitle
@@
 \subsection{Background}
-In astrophysics and astronomy, to numerically calculate the dynamical 
-evolution of N particles interacting gravitationally, N-body simulations 
-are required. Figure 1 shows the equation for interparticle interactions 
-in N-body simulations. If the equation is naively computed, the time
-complexity of calculation of interparticle interactions is 
-\begin{math}O(N^2) \end{math}, where 
-N is the number of particles. Therefore, parallelization is required to
-speed up numerical simulations. To write a parallelized code for a 
-numerical simulation, a user needs to understand the architecture of 
-computer systems in  detail. If a parallelized code is automatically
-generated by only describing the formulas and data of the numerical
-simulation, the above problems are solved. To realize the parallelization,
-we will develop Domain Specific Language  DSL \rparen, which is a 
-programming language specialized to a domain, for example, SQL and HTML.
-\subsection{parallelization}
-SIMD is one of the categories in Flynn's taxonomy 1, related to computer arithmetic
- processing. Using SIMD, arithmetic operations can be applied simultaneously to
-multiple data. In this paper, we compute and parallelize multiple particles. For example, 
-as shown in Figure 1, the computation of acceleration for different particles is independent
-of each other, allowing the process to be parallelized. As a result, for instance Assuming 
-that the variables for particles are double-precision floating-point numbers, we can execute 
-an operation on four elements simultaneously using the AVX2 instruction, it is possible to 
-perform operations on four elements. Therefore, compared to non-parallelized code, there is
-a potential to accelerate the computation by four times. We will describe the design of a 
-DSL in the next section to generate such parallelized code from the formulation of particle-particle interactions.
-\subsection{Overview of DSL}
 
-We have created a Domain Specific Language  DSL \rparen named  Pyker \rparen. This language's 
-processor can read code describing particle interaction formulas and generate code 
-that accelerates these computations. The language allows for the definition of 
-variables and the description of interaction formulas. In the variable definition 
-section, it's possible to define variables such as the mass and position of 
-particles, variables for storing results, and other necessary variables. For the formula
-part, we have enabled calculations including basic arithmetic operations, sqrt, power 
-functions, and computing the norm of vectors. From this description, a kernel function 
-is generated, which can then be called and used. We have created a Domain Specific 
-Language  DSL  named  Pyker. This language's processor can read code describing particle 
-interaction formulas and generate code that accelerates these computations. The language allows
-for the definition of variables and the description of interaction formulas. In the variable
-definition section, it's possible to define variables such as the mass and position of 
-particles, variables for storing results, and other necessary variables. For the formula part, 
-we have enabled calculations including basic arithmetic operations, sqrt, power functions, and 
-computing the norm of vectors. From this description, a kernel function is generated, which can then be called and used.
-\subsection{Aim of this paper}
+宇宙物理学や流体力学等、様々な分野で粒子系シミュレーションが行われている.
+例えば、惑星間の重力による力学的進化をシミュレーションしたN体シミュレーションや
+水の流体運動のモデル化がある。
+これらのシミュレーションには粒子の数に対して計算量が膨大になる。
+例としてN体シミュレーションの場合を説明する。N体シミュレーションでは,
+ほとんどの計算時間を重力相互作用の計算が占めている。\eqref{eq:gravity} は、
+重力相互作用の式である.
+\begin{equation}
+a_i = \sum_{\substack{j \neq i}}^{N} G m_j \frac{\vb{x}_j - \vb{x}_i}{\left( \left| \vb{x}_j - \vb{x}_i \right| + \epsilon^2 \right)^{3/2}\label{eq:gravity}}
+\end{equation}
+
+ここで $a_i$, $\vb{x}_i$はそれぞれ粒子iの加速度と位置を表し、
+$m_j$,$\vb{x}_j$はそれぞれ粒子jの質量と位置を表し、
+$N$,$G$,$\epsilon$はそれぞれ粒子の数、重力定数発散を防ぐためのソフトニングパラメータである。
+\eqref{eq:gravity}から計算量は粒子数Nに比例して、\begin{math}O(N^2) \end{math}となる。
+N体シミュレーションでは、粒子の数が膨大になる場合が多い。例えば、
+球状星団という天体には星が約$10^4 ~ 10^5 $ 個存在する。このため非常に長い計算時間がかかるため高速化が求めれる。
+粒子間相互作用の計算は、粒子同士の計算が独立しているためデータ並列性が高い。そのため、単一の命令に対して複数の
+データを処理するSIMDによる並列に適している。
+SIMDによる並列計算の例として、小池らが行ったGRAPE-DR\cite{GRAPE-explain-thesis}による重力多体問題シミュレーションがある。\cite{GRAPE-DR-thesis}
+しかし、SIMD計算を行うには,コンピュータのアーキテクチャを考慮したコードを記述しなくてはならない。
+
+この研究の目的は、ユーザーが粒子間相互作用の計算を並列化を意識することなく、並列に実行できるように
+することである。そのためにPykerというDomain Specific Language\lparen DSL \rparen を開発した。
+Pykerでは、ユーザに必要な変数の定義と数式から相互作用の計算をSIMD命令によって並列化したコードを生成する。
+Pykerの評価方法としては、C言語のコンパイラが自動で行うSIMD化とPykerによるSIMD化の性能を比較する。
+そのために、3つの相互作用の計算を行うコードをそれぞれにPykerから生成されたSIMD命令を適応しない
+場合のコードと、SIMD命令を適応したコードの実行時間を計測し比較する。
+また、Pykerを作成するにあたって粒子間相互作用の計算するコードを生成するPIKGを参考にした。
 
@@
 
-\begin{lstlisting}[frame=single, caption=hoge]
-
-#include<math>
-int kernel( (1) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
-  //(2)
-  int i;
-  int j;
-  double dr_v0;
-  double dr_v1;
-  double dr_v2;
-  // ... 
-  // ... 
-  // ...
-
-  for(i = 0;i < n;i += 1) {
-    for(j = 0;j < n;j += 1) {
-      //(3)
-      dr_v0 = -xi[i][0] + xj[j][0];
-      dr_v1 = -xi[i][1] + xj[j][1];
-      dr_v2 = -xi[i][2] + xj[j][2];
-      // ... 
-      // ... 
-      // ... 
-    }
-  }
-}
-\end{lstlisting}
-
 \subsubsection{code generatation of SIMD}
@@
   EPJ F64 mj:m
-
   EPJ F64 eps2:eps
-
   FORCE F64vec ai:acc
-
   rij = ri - rj
@@
 \section{Acknowledgement}
+
+\begin{thebibliography}{99}
+\end{thebibliography}
 \bibliography{biblist}
+
 \end{document}

### 2024-02-09 paper/paper.tex
writting language specification

@@
 \usepackage{physics}
+
+\usepackage[utf8]{inputenc}
+\usepackage{booktabs} % きれいな表を作成するためのパッケージ
+
 \bibliographystyle{ieicetr}
@@
 
-宇宙物理学や流体力学等、様々な分野で粒子系シミュレーションが行われている.
-例えば、惑星間の重力による力学的進化をシミュレーションしたN体シミュレーションや
-水の流体運動のモデル化がある。
-これらのシミュレーションには粒子の数に対して計算量が膨大になる。
-例としてN体シミュレーションの場合を説明する。N体シミュレーションでは,
-ほとんどの計算時間を重力相互作用の計算が占めている。\eqref{eq:gravity} は、
-重力相互作用の式である.
+Particle simulations have been executed in various fields such as 
+astrophysics and fluid dynamics. For example, N-body simulations 
+simulate the dynamical evolution due to gravity between planets,
+and models of fluid motion models simulate water.
+Particle simulations are computationally demanding
+with respect to the number of particles.
+As an example, we will discuss the case of an N-body simulation.
+In this simulation, most of the computational time is occupied by
+the calculation of the gravitational interaction. equation \eqref{eq:gravity} is 
+the equation for the gravitational interaction.
+
 \begin{equation}
@@
 
-ここで $a_i$, $\vb{x}_i$はそれぞれ粒子iの加速度と位置を表し、
-$m_j$,$\vb{x}_j$はそれぞれ粒子jの質量と位置を表し、
-$N$,$G$,$\epsilon$はそれぞれ粒子の数、重力定数発散を防ぐためのソフトニングパラメータである。
-\eqref{eq:gravity}から計算量は粒子数Nに比例して、\begin{math}O(N^2) \end{math}となる。
-N体シミュレーションでは、粒子の数が膨大になる場合が多い。例えば、
-球状星団という天体には星が約$10^4 ~ 10^5 $ 個存在する。このため非常に長い計算時間がかかるため高速化が求めれる。
-粒子間相互作用の計算は、粒子同士の計算が独立しているためデータ並列性が高い。そのため、単一の命令に対して複数の
-データを処理するSIMDによる並列に適している。
-SIMDによる並列計算の例として、小池らが行ったGRAPE-DR\cite{GRAPE-explain-thesis}による重力多体問題シミュレーションがある。\cite{GRAPE-DR-thesis}
-しかし、SIMD計算を行うには,コンピュータのアーキテクチャを考慮したコードを記述しなくてはならない。
+$a_i$, $\vb{x}_i$ $m_j$,$\vb{x}_j$,$N$,$G$,$\epsilon$
+are the acceleration and position of particle i, the mass of particle j, the number of position particles, respectively, and
+softening parameters to prevent gravitational constant divergence.
+From equation \eqref{eq:gravity},time complexity is proportional to 
+the number of particles N,
 
-この研究の目的は、ユーザーが粒子間相互作用の計算を並列化を意識することなく、並列に実行できるように
-することである。そのためにPykerというDomain Specific Language\lparen DSL \rparen を開発した。
-Pykerでは、ユーザに必要な変数の定義と数式から相互作用の計算をSIMD命令によって並列化したコードを生成する。
-Pykerの評価方法としては、C言語のコンパイラが自動で行うSIMD化とPykerによるSIMD化の性能を比較する。
-そのために、3つの相互作用の計算を行うコードをそれぞれにPykerから生成されたSIMD命令を適応しない
-場合のコードと、SIMD命令を適応したコードの実行時間を計測し比較する。
-また、Pykerを作成するにあたって粒子間相互作用の計算するコードを生成するPIKGを参考にした。
+ N-body simulations often require large numbers of particles.
+For example, a globular cluster contains about $10^4 ~ 10^5 $ stars.
+Therefore, very long computation time is required.  parallel computing is 
+generally used to speed up the process.
+
+The computation of interparticle interactions has high
+data parallelism because the computation of particles is 
+independent of each other. Therefore, 
+Parallelism by SIMD\lparen Single Instruction/Multiple Data \rparen, 
+one of Flynn's taxonomy \cite{flynn1972some} , is suitable.
+SIMD means processing multiple data for a single instruction.
+However, to perform SIMD, code must be written for the computer architecture.
+
+The goal of this study is to allow users to run particle interaction 
+calculations in parallel without having to be aware of parallelization.
+We developed a Domain Specific Language\lparen DSL \rparen called Pyker.
+DSL is a programming language for solving specific problems.
+Pyker generates parallelized code with SIMD instructions for the 
+calculation of interactions from the definition of variables and 
+the description of formulas.
+The evaluation method for Pyker is to compare the performance of 
+the automatic SIMD  performed by the C compiler with that of the 
+SIMD by Pyker. 
+For this purpose, we measured the execution time of the code that
+does not adapt the SIMD instructions generated by Pyker for each 
+of the three interaction calculations.
+The execution time of the code that does not adapt SIMD instructions
+generated from Pyker and the code that does adapt SIMD instructions 
+are measured and compared.
+
+In this paper, section 2 explains how Pyker defines the interparticle 
+interaction equation, section 3 describes the process of code generation 
+by Pyker, and section 4 presents the results of the performance evaluation
+experiments.
+
+\section{Definition of the interparticle interaction in Pyker}
+
+\subsection{interparticle interaction}
+we explain the needed for information to the calculate interparticle 
+interaction with reference to the actual code.
+gravity.cpp is the C++ source code that performs the calculation 
+in equation \eqref{eq:gravity}.
+\begin{lstlisting}[frame=single, caption=skeleton code, label=fuga]
+
+  for (int i = 0; i < n; i++) {
+    double ax = 0.0;
+    double ay = 0.0;
+    double az = 0.0;
+
+    for (int j = 0; j < n; j++) {
+        double dx = double(xj[j][0] - xi[i][0]);
+        double dy = double(xj[j][1] - xi[i][1]);
+        double dz = double(xj[j][2] - xi[i][2]);
+        double r2 = dx * dx + dy * dy + dz * dz + eps2;
+        double ri2 = 1.0f / sqrt(r2);
+
+        double mr = mj[j] * ri2 * ri2 * ri2;
+
+        ax += double(mr * dx);
+        ay += double(mr * dy);
+        az += double(mr * dz);
+    }
+
+    acci[i][0] = ax;
+    acci[i][1] = ay;
+    acci[i][2] = az;
+}
+\end{lstlisting}
+
+We will explain how this code corresponds to the expression 
+\eqref{eq:gravity}.
+acci,xi,mj,xj,eps2 correspond to
+ $a_i$, $\vb{x}_i$ $m_j$,$\vb{x}_j$,$N$,$\epsilon$ respectively.
+The $G$ is not in the code because it can be calculated after the 
+calculation of the interparticle interactions.
+
+ From this code, we can see that the variables to store the results, 
+the variables for particle i and particle j respectively, and the 
+variables for $N$ and $G$ can be calculated after the calculation of 
+the particle-particle interaction. The other variables have different 
+processing and data structures.
+
+ Therefore, there are three categories of information in a variable.
+\begin{itemize}
+  \item Whether the variable is a particle i, a particle j, a
+  variable that stores the result, or any other variable
+  \item The type information of the variable.
+  \item Whether the variable is a vector or not
+\end{itemize}
+
+ With the definition of this variable and a description of the
+mathematical equation using the variable, a code to calculate the
+interparticle interaction can be generated.
+これらをもとにPykerの言語仕様を説明する。
+
+\subsection{language specification}
+Pykerでは、大きく、変数定義と相互作用記述に分かれる。
+まず変数定義について説明する。
+
+ 先ほどのセクションよりPykerの変数定義を以下に正規表現で示す。
+% \begin{lstlisting}  
+\["(EPI|EPJ|FORCE)?\:\text{ } (vec3<)?(F64)>?\:\text{ } \text{\textbackslash w+}"\]
+% \end{lstlisting}
+EPI,EPJ,FORCEはそれぞれ粒子i,粒子j,結果を保存する変数であることを示す。それ以外の変数は何も書かない
+ベクトルはvec3で表す。
+もしベクトルであれば'<>'の中に型を定義する。
+型は倍精度小数だけでF64で示す。
+最後に変数名を記述する。
+
+次に相互作用記述の説明をする。
+相互作用の記述に使える演算は以下の図に示す。
+
+以下に\label{eq:gravity}の計算をPyker記述した例を示す。
+\begin{lstlisting}[frame=single, caption=gravity\_interparticle, label=fuga]
+  EPI vec3<F64> ri
+  EPJ vec3<F64> rj
+  EPJ F64 mass
+  EPJ F64 eps2
+  FORCE vec3<F64> ai
+  rij = ri - rj
+  r2 = rij * rij + eps2
+  r_inv = 1.0 / sqrt(r2)
+  r2_inv = r_inv * r_inv
+  mr_inv = mass * r_inv
+  mr3_inv = r2_inv * mr_inv
+  ai = mr3_inv * rij
+\end{lstlisting}
+
+5行目までは変数定義部になる。
+
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  項目 & 値 & 単位 \\
+  \midrule
+  項目1 & 100 & kg \\
+  項目2 & 200 & g \\
+  項目3 & 300 & mg \\
+\bottomrule
+\end{tabular}
+\end{table}
 
 \section{Construction}
+Pykerでは、どういうことができるのか？
+
 We use Sympy, a library in Python for implementing  the implementation of pyker.
@@
 extended instruction sets implemented in Intel's CPUs. The next section will explain how parallelization is carried out using AVX2.
-
-\subsection{AVX2 for parallelization}
-% _mm256dの説明はここですべきか？ codegen で説明すべきか
-To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
-and the results are stored. However, in the case of SIMD, computations are performed using SIMD-specific registers, so the 
-methods of loading, computing, and storing differ. When loading, multiple elements that will undergo the same instruction are
-stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
-each.
-
-For instance, consider a calculation like C = X + Y, where elements of double-precision floating arrays x and y are computed
-. When using AVX2 for SIMD, since the registers are 256 bits, four elements from x and y are loaded each. These are then added 
-simultaneously, and the results are stored in the array C. When loading into SIMD registers, if it's a 1-dimensional array, 
-contiguous memory access is sufficient, but for data structures like Array of Structures \lparen AoS \rparen shown in Figure a., elements need
-to be loaded individually.
-
-For example, when considering the 3-dimensional coordinates of particles as double-precision floats 
-in pos\lbrack n\rbrack \lbrack 3\rbrack  \lparen where n is the total number of particles, and pos\lbrack i \rbrack \lbrack 0\rbrack , pos\lbrack i\rbrack \lbrack 1\rbrack , 
-pos\lbrack i\rbrack \lbrack 2\rbrack  represent the x, y, z coordinates 
-of the i-th particle, respectively\rparen, and calculating the difference in x coordinates between particles i and j, it becomes dx = 
-pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack .
-However, for parallelization with SIMD, desiring dx0 = pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j \rbrack \lbrack 0\rbrack , dx1 = pos\lbrack i+1\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack
-, dx2 = pos\lbrack i+2\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , dx3 = pos\lbrack i+3\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , 
-the data are packed as \lparen pos\lbrack i\rbrack \lbrack 0\rbrack , pos\lbrack i+1\rbrack \lbrack 0\rbrack , pos\lbrack i+2\rbrack \lbrack  0\rbrack , pos\lbrack  i+3\rbrack \lbrack  0\rbrack \rparen,
-\lparen pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rparen, \lparen dx0, dx1, dx2, dx3\rparen and subtraction is performed simultaneously.
-However, since data needs
-to be loaded onto SIMD registers all at once, the gather instruction is used to load data for particle i. The gather instruction is used
-to read non-contiguous data elements from memory addresses by specifying addresses. An explanation of the gather instruction is shown in 
-Figure x. Data loaded in this way are computed simultaneously using SIMD instructions.
-
-\begin{lstlisting}[frame=single]
-  dx0 = pos[i][0] - pos[j][0]
-  dx1 = pos[i + 1][0] - pos[j][0]
-  dx2 = pos[i + 2][0] - pos[j][0]
-  dx3 = pos[i + 3][0] - pos[j][0]
-\end{lstlisting}
-
-\begin{lstlisting}[frame=single]
-  (x1, x2, x3, x4) + (y1, y2, y3, y)
-
-\end{lstlisting}
-
-When storing computation results, addresses may 
-not be contiguous. In such cases, there is an instruction called scatter, which is the counterpart to gather, but it is not supported 
-in AVX2, so data are stored using pointers individually. In this way, parallelization is achieved with SIMD. Moreover, these instructions
-can be explicitly handled in high-level programming languages like C and C++ using intrinsic functions. To handle intrinsic functions 
-in C and C++, include the file immintrin.h, which is available as a standard in the language.
-An example of C++ code that calculates the difference in x coordinates, simd\_tmp.cpp, is shown.
-{ Pyker}  generates C++ code capable of executing SIMD instructions like simd\_tmp.cpp
-from the described formulas. The next section will explain the Pyker.
 
@@
 
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  項目 & 値 & 単位 \\
+  \midrule
+  項目1 & 100 & kg \\
+  項目2 & 200 & g \\
+  項目3 & 300 & mg \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2024-02-10 paper/s1280076-0210.tex
0210

--- 2024-02-09 paper/paper.tex
@@
-\documentclass[ams, a4j]{U-AizuGT}
+\documentclass[ams]{article}
+\usepackage[margin=20truemm]{geometry}
+\usepackage{setspace}
+\doublespacing
 \usepackage{pifont}
@@
 \author{Ryuki Hiwada}
-\studentid{s1280076}
-\supervisor{Naohito Nakasato}
+% \studentid{s1280076}
+% \supervisor{Naohito Nakasato}
 
@@
 interparticle interaction can be generated.
-これらをもとにPykerの言語仕様を説明する。
+We explain the language specification in the next section.
 
 \subsection{language specification}
-Pykerでは、大きく、変数定義と相互作用記述に分かれる。
-まず変数定義について説明する。
+There are two parts in Pyker. variable definition part and 
+interaction description part.
+First, we explain about the variable definition part.
 
- 先ほどのセクションよりPykerの変数定義を以下に正規表現で示す。
+\subsubsection{variable definition part}
+Variable definitions are shown below in regular expressions.
 % \begin{lstlisting}  
@@
 % \end{lstlisting}
-EPI,EPJ,FORCEはそれぞれ粒子i,粒子j,結果を保存する変数であることを示す。それ以外の変数は何も書かない
-ベクトルはvec3で表す。
-もしベクトルであれば'<>'の中に型を定義する。
-型は倍精度小数だけでF64で示す。
-最後に変数名を記述する。
+EPI and EPJ represent the variables for particles i and j, 
+respectively, and FORCE indicates that they are variables that
+ store the results.   Other variables are not written.
 
-次に相互作用記述の説明をする。
-相互作用の記述に使える演算は以下の図に示す。
+ Vector are denoted by vec3.If variable is a vector, the variable type
+ is defined in '<>'.
 
-以下に\label{eq:gravity}の計算をPyker記述した例を示す。
+Variable type is 'F64' for double-precision.In Pyker, Variable type is only 'F64'.
+
+Finally, the name of the variable is written.
+
+Next, the interaction description is explained.
+
+In Pyker, you can use four arithmetic operations and sqrt(), power 
+multiplication, vector inner product, assignment, and '+=' for formulas.
+The operations that can be used to describe interactions are 
+shown in the following figure.
+\begin{lstlisting}[frame=single]
+ +, -, /, *, **, sqrt(), =, +=
+\end{lstlisting}
+\begin{itemize}
+  \item The $+, -, *,  /$ denote addition, subtraction, 
+  multiplication, and division, respectively. 
+  \item $**$ denotes a power
+  \item sqrt() denotes a square root.
+  \item When both terms of $*$ are vectors and the base of $**$ is 
+  a vector and the exponent is 2, respectively, the calculation is
+   determined to be an inner product.
+  \item The $+=$ indicates that the result of the calculation is added to the FORCE variable. 
+  \item $=$ is Assignment
+\end{itemize}
+
+In principle, if the elements are vectors, the operation is
+performed on each element of the vector.
+
+ The objects that can be used for the description are variables 
+ that have been defined and temporary variables and floats defined 
+ prior to the description.
+ The following is an example of a Pyker description 
+ of the calculation of the table \label{eq:gravity}
 \begin{lstlisting}[frame=single, caption=gravity\_interparticle, label=fuga]
@@
   mr3_inv = r2_inv * mr_inv
-  ai = mr3_inv * rij
+  ai += mr3_inv * rij
 \end{lstlisting}
 
-5行目までは変数定義部になる。
+次に、これらの記述からSIMD命令を行えるコードを生成する説明をする。
 
-\begin{table}[ht]
-  \centering % 表を中央揃えにする
-  \caption{サンプル表} % 表のタイトル
-  \label{tab:sampleTable}
-  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
-  \toprule
-  項目 & 値 & 単位 \\
-  \midrule
-  項目1 & 100 & kg \\
-  項目2 & 200 & g \\
-  項目3 & 300 & mg \\
-\bottomrule
-\end{tabular}
-\end{table}
+\section{Parser of Pyker}
+Pykerでは、
+このセクションでは、まずどのようにしてSIMDによる並列化を行うか説明し、その後Pykerの記述の読み込みからコード生成までの処理内容と流れを説明します。
 
-\section{Construction}
-Pykerでは、どういうことができるのか？
+\subsubsection{AVX2 for parallelization}
 
-We use Sympy, a library in Python for implementing  the implementation of pyker.
-SymPy supports various operations, and the formulas using these operations are internally treated as 
-syntax trees. We leveraged this functionality to read formulas and generate code capable of parallel execution.
-For parallelization, we used an instruction set named Advanced Vector Extensions 2 \lparen AVX2\rparen. AVX2 is one of the 
-extended instruction sets implemented in Intel's CPUs. The next section will explain how parallelization is carried out using AVX2.
-
-\subsection{Pyker}
-In this DSL, code is generated by writing and compiling two definitions: the definition of variables and the definition of interaction formulas. First, let us explain the variable definition.
-
-In this DSL, variables are classified into classes: EPI, EPJ, FORCE, and others. EPI represents particles that receive interactions, 
-while EPJ represents particles that provide interactions. FORCE holds the results of the interaction calculations, and other variables 
-include softening parameters and the like. To perform calculations using these variables, in C++, it would be similar to \ref{fuga}.
-
-\begin{lstlisting}[frame=single, caption=skeleton code, label=fuga]
-int kernel(double xi[][3], double xj[][3], double ai[][3], double eps2, int n){
-	// (1).preprocess
-	for(int i = 0;i < n;i += 4) { // (2)Increment the number of parallels
-		// (3).load EPI
-		// (4).Initialization of tmporary force
-		for(int j = 0;j < n;j += 1) {
-        // (5) load EPJ
-				// (6) calculate interparticle interactions
-		}
-		// (7). Store calculation result in the FORCE
-	}
-}
-\end{lstlisting}
-
-(1) involves preparatory steps such as defining variables necessary for the calculation. (2) 
-involves loading the variables of EPI. (3) is about initializing variables that temporarily
- hold the results of the interaction calculation. (4) involves performing the interaction 
- calculation and saving the results in the primary variable of force. (5) involves storing the results in the FORCE variables.
-To generate this code, in variable definition, information about the class of the variable,
- its type, and its dimension is necessary. Therefore, in pyker, variable definitions are written as follows. .
-The first column, if it is a class, writes the name of the class and its member variable
- name. The second column explicitly writes the dimensions of the vector if there are any, 
- specifying 3 or 4 dimensions, and the type is either 32-bit or 64-bit floating-point. The 
- third column becomes the name of the variable handled on pykg. For example, "EPI.pos vec3<F64> xi" 
- would be a member variable of EPI named pos, a 3-dimensional 64-bit floating-point variable named xi.
-The definition of interaction formulas is written to accumulate the results in the FORCE variable using
- the defined variables. Primary variables necessary for the mathematical description can be newly defined 
- using previously defined variables. Available operations include basic arithmetic, sqrt, and the power 
- symbol "**". The result is stored in the FORCE variable using '='.For instance, to generate code that c
- alculates the gravitational interaction formula shown in Figure 1, it would be written in this DSL as figure1.pyker.
-
-\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
-EPI.pos vec3<F64> xi
-EPJ.pos vec3<F64> xj
-EPJ.m F64 mass
-FORCE.acc vec3<F64> ai
-F64 eps2
-F64 g
-dr = xj - xi
-ai = g * mass *  dr / sqrt(dr ** 2 + eps2) ** 3
-\end{lstlisting}
-\subsection{Implementation}
-The process of generating code is illustrated in the following flowchart. In Parsing, the information
-of the variables defined in the DSL code is converted into a hash with the variable names as keys. 
-Formulas are converted into syntax trees using the sympify() method of Sympy, and a list of these 
-trees is obtained. Next, Common Subexpression Elimination (CSE) is performed on the syntax trees of the converted formulas. CSE is the process 
-of reducing the number of operations by pre-calculating common subexpressions in formulas and using 
-their results in subsequent calculations. In type inference, the types of the primary variables in the 
-formulas are inferred. Afterward, all syntax trees are converted into binary trees to align them with 
-SIMD operations. Finally, the code for calculating interactions is generated by traversing the processed 
-syntax trees. The following sections describe how the implementation was carried out in the order of
-Parsing, CSE, type inference, conversion to binary trees, and Code generation.
-\includegraphics[width=0.2\textwidth]{flowchartver3.jpg}
-\subsubsection{Parsing}
-In Parsing, the process is divided between variable definition and formula handling. In variable definition, 
-objects with class, vector, type, and variable name are created respectively. A hash with the variable name
-as the key is then made (name\_variable\_map). Formulas use the sympify() method from the Sympy library to convert
-the code read as a string into a syntax tree of formulas, obtaining a list of these syntax trees (expr\_list). Next, 
-Common Subexpression Elimination (CSE) is performed.
-\subsubsection{CSE}
-
-\subsubsection{type inference}
-\subsubsection{convert to binary trees}
-
-\subsubsection{code generatation of non SIMD}
-
-\subsubsection{code generatation of SIMD}
+\subsubsection{Flow of Parse}
 
@@
 \subsection{gravity interparticle}
-ほぼ同じコードで実行
 
@@
   10000 & 0.738918sec & 0.517324sec \\
-
  \\ \hline
@@
 
-\begin{table}[ht]
-  \centering % 表を中央揃えにする
-  \caption{サンプル表} % 表のタイトル
-  \label{tab:sampleTable}
-  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
-  \toprule
-  項目 & 値 & 単位 \\
-  \midrule
-  項目1 & 100 & kg \\
-  項目2 & 200 & g \\
-  項目3 & 300 & mg \\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \end{document}

### 2024-02-13 paper/paper.tex
can do test

@@
 \usepackage{physics}
-
+\usepackage{tikz}
 \usepackage[utf8]{inputenc}
 \usepackage{booktabs} % きれいな表を作成するためのパッケージ
-
+\usetikzlibrary{shapes,arrows,positioning}
 \bibliographystyle{ieicetr}
+\usetikzlibrary{positioning, arrows.meta, shapes.geometric}
 
@@
 
-% \usepackage{listings,jlisting}
-
-% \lstset{%
-%   language={C},
-%   basicstyle={\small},%
-%   identifierstyle={\small},%
-%   commentstyle={\small\itshape},%
-%   keywordstyle={\small\bfseries},%
-%   ndkeywordstyle={\small},%
-%   stringstyle={\small\ttfamily},
-%   frame={tb},
-%   breaklines=true,
-%   columns=[l]{fullflexible},%
-%   numbers=left,%
-%   xrightmargin=0zw,%
-%   xleftmargin=3zw,%
-%   numberstyle={\scriptsize},%
-%   stepnumber=1,
-%   numbersep=1zw,%
-%   lineskip=-0.5ex%
-% }
 \lstset{
@@
 % \end{lstlisting}
-EPI,EPJ,FORCEはそれぞれ粒子i,粒子j,結果を保存する変数であることを示す。それ以外の変数は何も書かない
-ベクトルはvec3で表す。
-もしベクトルであれば'<>'の中に型を定義する。
-型は倍精度小数だけでF64で示す。
-最後に変数名を記述する。
+EPI and EPJ represent the variables for particles i and j, 
+respectively, and FORCE indicates that they are variables that
+ store the results.   Other variables are not written.
+
+ Vector are denoted by vec3.If variable is a vector, the variable type
+ is defined in '<>'.
+
+Variable type is 'F64' for double-precision.In Pyker, Variable type is only 'F64'.
+
+Finally, the name of the variable is written.
 
@@
 相互作用の記述に使える演算は以下の図に示す。
+\begin{lstlisting}[frame=single]
+ +, -, /, *, **, sqrt(), =, +=
+\end{lstlisting}
+$+, -, *, /$ はそれぞれ 加算、減算、乗算、徐算を表す。
+$**$ はべき乗を表し、sqrt()は平方根を表す。
+$*$の項がどちらもベクトルの時、$**$の底がベクトル、指数が2の場合にそれぞれ内積の計算と判断される。
+$=$は一時変数を定義する際に使用する。一時変数は定義する際に型を定義する必要はなく、すでに定義されている変数の型とベクトルから
+推論を行い決定する。
+$+=$はFORCEの変数に計算結果を加算することを示す。
+原則、要素がベクトルの場合は、ベクトルの要素ごとに演算を行う。
+記述に使えるオブジェクトは、変数定義を行った変数とその記述より前に定義された一時変数と浮動小数である。
 
@@
   mr3_inv = r2_inv * mr_inv
-  ai = mr3_inv * rij
+  ai += mr3_inv * rij
 \end{lstlisting}
 
-5行目までは変数定義部になる。
+次に、これらの記述からSIMD命令を行えるコードを生成する説明をする。
 
-\begin{table}[ht]
-  \centering % 表を中央揃えにする
-  \caption{サンプル表} % 表のタイトル
-  \label{tab:sampleTable}
-  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
-  \toprule
-  項目 & 値 & 単位 \\
-  \midrule
-  項目1 & 100 & kg \\
-  項目2 & 200 & g \\
-  項目3 & 300 & mg \\
-\bottomrule
-\end{tabular}
-\end{table}
+\section{Parser of Pyker}
+Pykerでは、
+このセクションでは、まずどのようにしてSIMDによる並列化を行うか説明し、その後Pykerの記述の読み込みからコード生成までの処理内容と流れを説明します。
 
-\section{Construction}
-Pykerでは、どういうことができるのか？
+\begin{tikzpicture}
+  \tikzset{
+    block/.style={
+      rectangle, draw, text centered, text width=3cm,
+      minimum height=1.5cm
+    },
+    line/.style={
+      draw, very thick, color=black!50, -Latex
+    }
+  }
 
-We use Sympy, a library in Python for implementing  the implementation of pyker.
-SymPy supports various operations, and the formulas using these operations are internally treated as 
-syntax trees. We leveraged this functionality to read formulas and generate code capable of parallel execution.
-For parallelization, we used an instruction set named Advanced Vector Extensions 2 \lparen AVX2\rparen. AVX2 is one of the 
-extended instruction sets implemented in Intel's CPUs. The next section will explain how parallelization is carried out using AVX2.
+  % Place nodes
+  \node[block] (parse) {Parse};
+  \node[block, right=of parse] (type_inference) {type\_inference};
+  \node[block, right=of type_inference] (bitree) {bitree};
+  \node[block, right=of bitree] (codegen) {Codegen};
+
+  % Draw edges
+  \path[line] (parse) -- (type_inference);
+  \path[line] (type_inference) -- (bitree);
+  \path[line] (bitree) -- (codegen);
+\end{tikzpicture}
+
+\subsubsection{AVX2 for parallelization}
+% _mm256dの説明はここですべきか？ codegen で説明すべきか
+To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
+and the results are stored. However, in the case of SIMD, computations are performed using SIMD-specific registers, so the 
+methods of loading, computing, and storing differ. When loading, multiple elements that will undergo the same instruction are
+stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
+each.
+
+For instance, consider a calculation like C = X + Y, where elements of double-precision floating arrays x and y are computed
+. When using AVX2 for SIMD, since the registers are 256 bits, four elements from x and y are loaded each. These are then added 
+simultaneously, and the results are stored in the array C. When loading into SIMD registers, if it's a 1-dimensional array, 
+contiguous memory access is sufficient, but for data structures like Array of Structures \lparen AoS \rparen shown in Figure a., elements need
+to be loaded individually.
+
+For example, when considering the 3-dimensional coordinates of particles as double-precision floats 
+in pos\lbrack n\rbrack \lbrack 3\rbrack  \lparen where n is the total number of particles, and pos\lbrack i \rbrack \lbrack 0\rbrack , pos\lbrack i\rbrack \lbrack 1\rbrack , 
+pos\lbrack i\rbrack \lbrack 2\rbrack  represent the x, y, z coordinates 
+of the i-th particle, respectively\rparen, and calculating the difference in x coordinates between particles i and j, it becomes dx = 
+pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack .
+However, for parallelization with SIMD, desiring dx0 = pos\lbrack i\rbrack \lbrack 0\rbrack  - pos\lbrack j \rbrack \lbrack 0\rbrack , dx1 = pos\lbrack i+1\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack
+, dx2 = pos\lbrack i+2\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , dx3 = pos\lbrack i+3\rbrack \lbrack 0\rbrack  - pos\lbrack j\rbrack \lbrack 0\rbrack , 
+the data are packed as \lparen pos\lbrack i\rbrack \lbrack 0\rbrack , pos\lbrack i+1\rbrack \lbrack 0\rbrack , pos\lbrack i+2\rbrack \lbrack  0\rbrack , pos\lbrack  i+3\rbrack \lbrack  0\rbrack \rparen,
+\lparen pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rbrack , pos\lbrack  j\rbrack \lbrack  0\rparen, \lparen dx0, dx1, dx2, dx3\rparen and subtraction is performed simultaneously.
+However, since data needs
+to be loaded onto SIMD registers all at once, the gather instruction is used to load data for particle i. The gather instruction is used
+to read non-contiguous data elements from memory addresses by specifying addresses. An explanation of the gather instruction is shown in 
+Figure x. Data loaded in this way are computed simultaneously using SIMD instructions.
+
+\begin{lstlisting}[frame=single]
+  dx0 = pos[i][0] - pos[j][0]
+  dx1 = pos[i + 1][0] - pos[j][0]
+  dx2 = pos[i + 2][0] - pos[j][0]
+  dx3 = pos[i + 3][0] - pos[j][0]
+\end{lstlisting}
+
+\begin{lstlisting}[frame=single]
+  (x1, x2, x3, x4) + (y1, y2, y3, y)
+
+\end{lstlisting}
+
+When storing computation results, addresses may 
+not be contiguous. In such cases, there is an instruction called scatter, which is the counterpart to gather, but it is not supported 
+in AVX2, so data are stored using pointers individually. In this way, parallelization is achieved with SIMD. Moreover, these instructions
+can be explicitly handled in high-level programming languages like C and C++ using intrinsic functions. To handle intrinsic functions 
+in C and C++, include the file immintrin.h, which is available as a standard in the language.
+An example of C++ code that calculates the difference in x coordinates, simd\_tmp.cpp, is shown.
+{ Pyker}  generates C++ code capable of executing SIMD instructions like simd\_tmp.cpp
+from the described formulas. The next section will explain the Pyker.
 
@@
 %  \end{tabular}
+
+\subsection{Hermite}
 
@@
 
- \\ \hline
+\begin{table}
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 5.282461100 & 4.059262 \\
+  25000 & 1.322715200 & 1.008046 \\
+  10000 & 0.213696 & 0.161884 \\
+  1000 & 0.002116 & 0.001713 \\
+\bottomrule
 \end{tabular}
-
-\section{Conclusion}
-\section{Acknowledgement}
-
-\begin{thebibliography}{99}
-\end{thebibliography}
-\bibliography{biblist}
-
+\end{table}
 \begin{table}[ht]
@@
 
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 24.755255 & 22.767920 \\
+  25000 & 6.136025 & 5.740028 \\
+  10000 & 1.044833 & 0.901585\\
+  1000 & 0.010176 & 0.009109 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 13.796789& 10.794405\\
+  25000 & 3.472925 & 2.693424\\
+  10000 & 0.557972 & 0.424820\\
+  1000 & 0.005405& 0.004240\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 2.476695 & 2.439798\\
+  25000 & 0.617220 & 0.598798\\
+  10000 & 0.094859 & 0.094860\\
+  1000 & 0.000939& 0.000988\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 2.153937 & 2.194700\\
+  25000 &0.542478 & 0.554280\\
+  10000 & 0.085537 &0.087284\\
+  1000 & 0.000869&0.000874\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+  \centering % 表を中央揃えにする
+  \caption{サンプル表} % 表のタイトル
+  \label{tab:sampleTable}
+  \begin{tabular}{ccc} % ここで列の数とテキストの配置を指定
+  \toprule
+  N & Pyker & PIKG \\
+  \midrule
+  50000 & 15.103493& 9.904044\\
+  25000 &3.736596 & 2.480025\\
+  10000 &0.543367 &0.398513\\
+  1000 & 0.005392&0.003911\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\section{Conclusion}
+\section{Acknowledgement}
+
+\begin{thebibliography}{99}
+\end{thebibliography}
+\bibliography{biblist}
+
 \end{document}

### 2024-02-13 dsl/experiment/Hermite/pikg/pikg_kernel.hpp

@@ -1,0 +1,183 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 48,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 64,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 48,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I1_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I1_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
+delete[] force_tmp;
+} // if(kernel_id == 0)
[…]

### 2024-02-13 dsl/experiment/Hermite/pikg/pikg_kernel_AVX2.hpp

@@ -1,0 +1,944 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+#include <pikg_avx2.hpp>
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 48,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 64,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 48,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I4_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I4_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
[…]

### 2024-02-13 dsl/experiment/Hermite/pikg_kernel_AVX2.hpp

@@ -1,0 +1,936 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+#include <pikg_avx2.hpp>
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 48,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 64,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 48,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I4_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I4_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
+{ // test Kernel_I1_J4
[…]

### 2024-02-13 dsl/experiment/Hermite/pyker_kernel.hpp

@@ -1,0 +1,49 @@
+#include<math.h>
+;
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   double dr_v0;
+   double dr_v1;
+   double dr_v2;
+   double dv_v0;
+   double dv_v1;
+   double dv_v2;
+   double r2;
+   double r1i;
+   double r2i;
+   double r3i;
+   double r5i;
+   double rv;
+   double af;
+   double jf;
+   for (i = 0; i < n; i += 1) {
+      ;
+      ;
+      for (j = 0; j < n; j += 1) {
+         ;
+         dr_v0 = ri[i][0] - rj[j][0];
+         dr_v1 = ri[i][1] - rj[j][1];
+         dr_v2 = ri[i][2] - rj[j][2];
+         dv_v0 = vi[i][0] - vj[j][0];
+         dv_v1 = vi[i][1] - vj[j][1];
+         dv_v2 = vi[i][2] - vj[j][2];
+         r2 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
+         r1i = 1.0/sqrt(r2);
+         r2i = r1i*r1i;
+         r3i = r1i*r2i;
+         r5i = r2i*r3i;
+         rv = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
+         af = mj[j]*r3i;
+         jf = rv*((3.0*mj[j])*r5i);
+         F[i][0] += af*dr_v0;
+         F[i][1] += af*dr_v1;
+         F[i][2] += af*dr_v2;
+         J[i][0] += af*dv_v0 - dr_v0*jf;
+         J[i][1] += af*dv_v1 - dr_v1*jf;
+         J[i][2] += af*dv_v2 - dr_v2*jf;
+      };
+      ;
+   };
+   return 0;
+};

### 2024-02-13 dsl/experiment/Hermite/pyker_kernel_AVX2.hpp

@@ -1,0 +1,125 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d vi_tmp_v0;
+   __m256d vi_tmp_v1;
+   __m256d vi_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d vj_tmp_v0;
+   __m256d vj_tmp_v1;
+   __m256d vj_tmp_v2;
+   __m256d mj_tmp;
+   __m256d eps2_tmp;
+   __m256d F_tmp_v0;
+   __m256d F_tmp_v1;
+   __m256d F_tmp_v2;
+   __m256d J_tmp_v0;
+   __m256d J_tmp_v1;
+   __m256d J_tmp_v2;
+   __m256d float_0_tmp;
+   float_0_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(3.0);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d dv_tmp_v0;
+   __m256d dv_tmp_v1;
+   __m256d dv_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r1i_tmp;
+   __m256d r2i_tmp;
+   __m256d r3i_tmp;
+   __m256d r5i_tmp;
+   __m256d rv_tmp;
+   __m256d af_tmp;
+   __m256d jf_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
[…]

### 2024-02-13 dsl/experiment/LennardJones_ver2/LennardJones.cpp

@@ -25,10 +25,10 @@ struct FORCE{
   double p;
 };
 
-// #include "pikg_kernel.hpp"
-// #include "pyker_kernel.hpp"
-#include "pikg_kernel_AVX2.hpp"
-#include "pyker_kernel_AVX2.hpp"
+#include "pikg_kernel.hpp"
+#include "pyker_kernel.hpp"
+// #include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel_AVX2.hpp"
 
 // 乱数を生成するための関数
 double rand_double(double min, double max) {

### 2024-02-13 dsl/experiment/Nbody/gravity_interparticle.cpp

@@ -6,6 +6,7 @@
 // #include<algorithm>
 #include<cmath>
 #include<time.h>
+#include<iostream>
 
 struct EPI {
    pikg_f64vec3 r;
@@ -50,8 +51,8 @@ double calculate_difference(double a, double b) {
 int main() {
    srand((unsigned)time(NULL)); // 乱数のシードを設定
 
-   int n = 25000;
-
+   int n = 0;
+   std::cin >>  n;
    //PIKG用のコード
    const int nepi = n; 
    const int nepj = n; 
@@ -148,9 +149,9 @@ int main() {
       }
     }
 
-   printf("Total difference in F.x: %f\n", total_diff_Fx);
-   printf("Total difference in F.y: %f\n", total_diff_Fy);
-   printf("Total difference in F.z: %f\n", total_diff_Fz);
+   // printf("Total difference in F.x: %f\n", total_diff_Fx);
+   // printf("Total difference in F.y: %f\n", total_diff_Fy);
+   // printf("Total difference in F.z: %f\n", total_diff_Fz);
    // printf("Total difference in J.x: %f\n", total_diff_Jx / n);
    // printf("Total difference in J.y: %f\n", total_diff_Jy / n);
    // printf("Total difference in J.z: %f\n", total_diff_Jz / n);

### 2024-02-13 dsl/experiment/Nbody/pyker_kernel_AVX2.hpp

@@ -46,7 +46,8 @@ int kernel(int n, double ri[][3], double rj[][3], double mass[], double eps2[], 
          rij_tmp_v0 = _mm256_sub_pd(ri_tmp_v0, rj_tmp_v0);
          rij_tmp_v1 = _mm256_sub_pd(ri_tmp_v1, rj_tmp_v1);
          rij_tmp_v2 = _mm256_sub_pd(ri_tmp_v2, rj_tmp_v2);
-         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(rij_tmp_v0, rij_tmp_v0), _mm256_mul_pd(rij_tmp_v1, rij_tmp_v1)), _mm256_mul_pd(rij_tmp_v2, rij_tmp_v2)));
+         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(rij_tmp_v0, rij_tmp_v0), 
+                                 _mm256_mul_pd(rij_tmp_v1, rij_tmp_v1)), _mm256_mul_pd(rij_tmp_v2, rij_tmp_v2)));
          r_inv_tmp = _mm256_div_pd(float_0_tmp, _mm256_sqrt_pd(r2_tmp));
          r2_inv_tmp = _mm256_mul_pd(r_inv_tmp, r_inv_tmp);
          mr_inv_tmp = _mm256_mul_pd(mass_tmp, r_inv_tmp);

### 2024-02-13 dsl/experiment/check_acc/check_acclate_n.py

@@ -1,0 +1,22 @@
+
+left_list = []
+
+def culc_(l, r):
+
+    return l / r
+
+
+for i in range(4):
+    lef = float(input())
+
+    left_list.append(lef)
+
+right_list = []
+for i in range(4):
+    r = float(input())
+    right_list.append(r)
+
+for i in range(4):
+    l = left_list[i]
+    r = right_list[i]
+    print(culc_(l, r))

### 2024-02-13 dsl/gen/gravity_code.hpp

@@ -1,31 +1,32 @@
 #include<math.h>
 ;
-int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
+int kernel(int n, double ri[][3], double rj[][3], double m[], double eps2[], double ai[][3]){
    int i;
    int j;
-   double dx;
-   double dy;
-   double dz;
+   double rij_v0;
+   double rij_v1;
+   double rij_v2;
    double r2;
-   double r2i;
-   double r6i;
-   double f;
+   double r_inv;
+   double r2_inv;
+   double mr_inv;
+   double mr3_inv;
    for (i = 0; i < n; i += 1) {
       ;
       ;
       for (j = 0; j < n; j += 1) {
          ;
-         dx = rix[i] - rjx[j];
-         dy = riy[i] - rjy[j];
-         dz = riz[i] - rjz[j];
-         r2 = dz*dz + (dy*dy + (dx*dx + eps[j]));
-         r2i = 1.0/r2;
-         r6i = r2i*(r2i*r2i);
-         f = (r2i*r6i)*(48.0*r6i - 24.0);
-         fx[i] += dx*f;
-         fy[i] += dy*f;
-         fz[i] += dz*f;
-         p[i] += (4.0*r6i)*(r6i - 1.0);
+         rij_v0 = ri[i][0] - rj[j][0];
+         rij_v1 = ri[i][1] - rj[j][1];
+         rij_v2 = ri[i][2] - rj[j][2];
+         r2 = eps2[j] + (rij_v2*rij_v2 + (rij_v0*rij_v0 + rij_v1*rij_v1));
+         r_inv = 1.0/sqrt(r2);
+         r2_inv = r_inv*r_inv;
+         mr_inv = m[j]*r_inv;
+         mr3_inv = mr_inv*r2_inv;
+         ai[i][0] += mr3_inv*rij_v0;
+         ai[i][1] += mr3_inv*rij_v1;
+         ai[i][2] += mr3_inv*rij_v2;
       };
       ;
    };

### 2024-02-13 dsl/gen/pyker.py

@@ -37,9 +37,13 @@ def Parse(file_str):
     expr_list = []
     name_variable_map = {}
 
+    # file_list.replace('+=', '=')
+
     #ファイルから読み取ったコードを一行ずつ
     for col in file_list:
-        
+
+        col = col.replace('+=', '=')        
+
         #＝演算子があれば、式なので、その時、sympyの式に変換
         if col.find('=') != -1:
             expr_list.append(expr_part(col))

### 2024-02-13 dsl/simd/interparticle.cpp

@@ -23,20 +23,16 @@ double acci[][3],
 double eps2) {
                   
 for (int i = 0; i < ni; i++) {
-    double xi = posi[i][0];
-    double yi = posi[i][1];
-    double zi = posi[i][2];
     double ax = 0.0;
     double ay = 0.0;
     double az = 0.0;
 
     for (int j = 0; j < nj; j++) {
-        double dx = double(posj[j][0] - xi);
-        double dy = double(posj[j][1] - yi);
-        double dz = double(posj[j][2] - zi);
+        double dx = double(posj[j][0] - posi[i][0]);
+        double dy = double(posj[j][1] - posi[i][1]);
+        double dz = double(posj[j][2] - posi[i][2]);
         double r2 = dx * dx + dy * dy + dz * dz + eps2;
-        double ri2 = 1.0f / sqrt(r2); // <- 1.0f / r2 となっていて
-                                      //evaluate_gravityが速くなっていた
+        double ri2 = 1.0f / sqrt(r2); 
         
         double mr = mj[j] * ri2 * ri2 * ri2;
 

### 2024-02-16 dsl/experiment/Hermite/pyker_kernel_AVX2.hpp
0216

@@ -81,12 +81,19 @@ int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3]
          dv_tmp_v0 = _mm256_sub_pd(vi_tmp_v0, vj_tmp_v0);
          dv_tmp_v1 = _mm256_sub_pd(vi_tmp_v1, vj_tmp_v1);
          dv_tmp_v2 = _mm256_sub_pd(vi_tmp_v2, vj_tmp_v2);
-         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)), _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2)));
+         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(
+                                          _mm256_add_pd(
+                                             _mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), 
+                                             _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)),
+                                             _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2)));
          r1i_tmp = _mm256_div_pd(float_0_tmp, _mm256_sqrt_pd(r2_tmp));
          r2i_tmp = _mm256_mul_pd(r1i_tmp, r1i_tmp);
          r3i_tmp = _mm256_mul_pd(r1i_tmp, r2i_tmp);
          r5i_tmp = _mm256_mul_pd(r2i_tmp, r3i_tmp);
-         rv_tmp = _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dv_tmp_v0), _mm256_mul_pd(dr_tmp_v1, dv_tmp_v1)), _mm256_mul_pd(dr_tmp_v2, dv_tmp_v2));
+         rv_tmp = _mm256_add_pd(
+                  _mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dv_tmp_v0), 
+                                _mm256_mul_pd(dr_tmp_v1, dv_tmp_v1)), 
+                                _mm256_mul_pd(dr_tmp_v2, dv_tmp_v2));
          af_tmp = _mm256_mul_pd(mj_tmp, r3i_tmp);
[…]

### 2024-02-16 dsl/experiment/Nbody/pyker_code.hpp

@@ -16,6 +16,7 @@ int kernel(int n, double ri[][3], double rj[][3], double mj[], double eps2[], do
       ;
       for (j = 0; j < n; j += 1) {
          ;
+      
          rij_v0 = ri[i][0] - rj[j][0];
          rij_v1 = ri[i][1] - rj[j][1];
          rij_v2 = ri[i][2] - rj[j][2];

### 2024-02-16 dsl/experiment/Nbody/pyker_kernel_AVX2.hpp

@@ -46,8 +46,11 @@ int kernel(int n, double ri[][3], double rj[][3], double mass[], double eps2[], 
          rij_tmp_v0 = _mm256_sub_pd(ri_tmp_v0, rj_tmp_v0);
          rij_tmp_v1 = _mm256_sub_pd(ri_tmp_v1, rj_tmp_v1);
          rij_tmp_v2 = _mm256_sub_pd(ri_tmp_v2, rj_tmp_v2);
-         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(rij_tmp_v0, rij_tmp_v0), 
-                                 _mm256_mul_pd(rij_tmp_v1, rij_tmp_v1)), _mm256_mul_pd(rij_tmp_v2, rij_tmp_v2)));
+         
+         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(
+                                 _mm256_mul_pd(rij_tmp_v0, rij_tmp_v0), 
+                                 _mm256_mul_pd(rij_tmp_v1, rij_tmp_v1)), 
+                                 _mm256_mul_pd(rij_tmp_v2, rij_tmp_v2)));
          r_inv_tmp = _mm256_div_pd(float_0_tmp, _mm256_sqrt_pd(r2_tmp));
          r2_inv_tmp = _mm256_mul_pd(r_inv_tmp, r_inv_tmp);
          mr_inv_tmp = _mm256_mul_pd(mass_tmp, r_inv_tmp);

### 2024-02-16 dsl/gen/gravity_code.hpp

@@ -1,34 +1,34 @@
 #include<math.h>
-;
-int kernel(int n, double ri[][3], double rj[][3], double m[], double eps2[], double ai[][3]){
+#include<x86intrin.h>;
+int kernel(int n, double xi[][3], double yi[][3], double f[]){
    int i;
    int j;
-   double rij_v0;
-   double rij_v1;
-   double rij_v2;
-   double r2;
-   double r_inv;
-   double r2_inv;
-   double mr_inv;
-   double mr3_inv;
-   for (i = 0; i < n; i += 1) {
-      ;
-      ;
+   __m256d xi_tmp_v0;
+   __m256d xi_tmp_v1;
+   __m256d xi_tmp_v2;
+   __m256d yi_tmp_v0;
+   __m256d yi_tmp_v1;
+   __m256d yi_tmp_v2;
+   __m256d f_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      xi_tmp_v0 = _mm256_i32gather_pd(&xi[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
+      xi_tmp_v1 = _mm256_i32gather_pd(&xi[i][1], vindex_gather_1, 8);
+      int index_gather_2[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
+      xi_tmp_v2 = _mm256_i32gather_pd(&xi[i][2], vindex_gather_2, 8);
+      f_tmp = _mm256_set1_pd(0.0);
       for (j = 0; j < n; j += 1) {
-         ;
-         rij_v0 = ri[i][0] - rj[j][0];
-         rij_v1 = ri[i][1] - rj[j][1];
-         rij_v2 = ri[i][2] - rj[j][2];
-         r2 = eps2[j] + (rij_v2*rij_v2 + (rij_v0*rij_v0 + rij_v1*rij_v1));
-         r_inv = 1.0/sqrt(r2);
-         r2_inv = r_inv*r_inv;
[…]

### 2024-02-16 dsl/simd/dot_simd.cpp

@@ -1,0 +1,24 @@
+#include<stdio.h>
+#include <x86intrin.h>
+#include<algorithm>
+#include<math.h>
+#include <immintrin.h>
+#include <random>
+#include<time.h>
+#include<iostream>
+#include<set>
+using namespace std;
+
+int main() {
+
+   int n;
+   double x[n][3], y[n][3];
+
+   __m256d xi;
+
+   for(int i = 0;i < n;i++) {
+      
+   }
+
+
+}

### 2024-02-16 dsl/simd/slide_code.cpp

@@ -1,0 +1,29 @@
+#include<math.h>
+#include<x86intrin.h>;
+#include<vector>
+int main() {
+   int n;
+   double xi[n][3], yi[n][3];
+   __m256d x_v0;
+   __m256d x_v1;
+   __m256d x_v2;
+   __m256d y_v0;
+   __m256d y_v1;
+   __m256d y_v2;
+
+   int a, b,c;
+   int ans = a * b;
+
+   std::vector<int> x(n), y(n);
+
+   ans = x[0] * y[0] + x[1] * y[1] + x[2] * y[2];
+
+
+   __m256d v0 = _mm256_mul_pd(x_v0, y_v0);
+   __m256d v1 = _mm256_mul_pd(x_v1, y_v1);
+   __m256d v2 = _mm256_mul_pd(x_v2, y_v2);
+   __m256d ansv = _mm256_add_pd(v0, _mm256_add_pd(v1, v2));
+   
+
+
+}

### 2024-02-16 test_var_def.cpp

@@ -1,0 +1,54 @@
+#include <stdio.h>
+#include <time.h>
+
+// ここに計測したい関数を定義します。
+int yourFunction(long long int n) {
+    // 何か時間がかかる処理を行う
+    int ans = 0;
+    for(long i = 0; i < n; i++) {
+         ans += i;
+    }
+    return ans;
+}
+
+int func_vardef(long long int n){
+   int ans = 0;
+   for (long i = 0; i < n; i++ ){
+      int j;
+         j = i;
+      ans += (i + j);
+   }
+   return ans;
+}
+
+
+int main() {
+    clock_t start, end;
+    double cpu_time_used;
+
+   long long int n = 10000000;
+    // 関数の実行前の時間を記録
+
+    start = clock();
+
+    // 計測したい関数を実行
+    yourFunction(n);
+
+    // 関数の実行後の時間を記録
+    end = clock();
+
+    // CPU時間を計算（秒単位）
+    cpu_time_used = ((double) (end - start)) / CLOCKS_PER_SEC;
+
+    printf("関数の実行時間: %f 秒\n", cpu_time_used);
+
+   start = clock();
+   func_vardef(n);
+   end = clock();
+
+    cpu_time_used = cpu_time_used-  ((double) (end - start)) / CLOCKS_PER_SEC;
+    printf("vardef - 関数の時間: %fsec\n", cpu_time_used);
+
+
+    return 0;
+}

### 2024-02-20 paper/s1280076_0219.tex
0220

% \documentclass[ams]{U-AizuGT}
\documentclass[ams]{article}
\usepackage[margin=20truemm]{geometry}
\usepackage{setspace}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{listings}
\usepackage{physics}
\usepackage{amsmath}
\usepackage{here}
\lstset{
    frame=single,
    breaklines=true,
    lineskip=-0.5ex,
    frame={tb},
}

% \lstset{
%   basicstyle={\ttfamily},
%   identifierstyle={\small},
%   commentstyle={\smallitshape},
%   keywordstyle={\small\bfseries},
%   ndkeywordstyle={\small},
%   stringstyle={\small\ttfamily}
%   frame={tb},
%   % breaklines=true,
%   % columns=[l]{fullflexible},
%   % numbers=left,
%   % % xrightmargin=0zw,
%   % % xleftmargin=3zw
%   % numberstyle={\scriptsize},
%   % stepnumber=1
%   % numbersep=1zw,
%   % lineskip=-0.5ex
% }

% \author[]{Ryuki Hiwada}
% ハイフネーション禁止
\hyphenpenalty=10000\relax
\exhyphenpenalty=10000\relax
\sloppy

\bibliographystyle{ieicetr}

% \author{Ryuki Hiwada}
% \studentid{s1280076}
% \supervisor{Prof. Naohito Nakasato}
\title{Domain Specific Language For High-Performance Computing}
\begin{document}
	\maketitle
	\begin{abstract}
		The abstract of your thesis must be written here.
	\end{abstract}

	\section{Introduction}

Particle simulations have been performed in various research fields such as astrophysics and molecular dynamics. For example, in astrophysics, we simulate the dynamical evolution due to gravity between stars,
and in molecular dynamics, we simulate the motion of molecules.
Particle simulations are computationally expensive when the number of particles involved is large.
    In $N$-body simulation, most of the computational time is used to calculate 
the gravitational interaction. Equation\eqref{eq:gravity} is 
the equation for the gravitational acceleration for ith particle.

\begin{equation}
\vb{a}_i = \sum_{\substack{j \neq i}}^{N} G m_j \frac{\vb{x}_j - \vb{x}_i}{\left( \left| \vb{x}_j - \vb{x}_i \right| + \epsilon^2 \right)^{3/2}\label{eq:gravity}}
\end{equation}

$\vb{a}_i$ is the acceleration, $\vb{x}_i$ is position of the particle i,
$m_j$ is the mass of the particle j, $\vb{x}_j$ is position of the particle j,
$N$ is the number of particles.

In addition, $G$ and $\epsilon$, are the gravitational constant and a softening parameter to prevent divergence.
From Equation \eqref{eq:gravity}, the time complexity of the calculation for N particles is proportional to 
the square of the number of particles N.

 $N$-body simulations often require large numbers of particles.
For example, a globular cluster contains about $10^4$ to $10^6 $ stars.
Therefore, For $N$-body simulation parallel computing is generally used to speed up the computation.

The computation of particle interactions has high
data parallelism because the computation of particles is 
independent of each other. Therefore, 
 SIMD\lparen Single Instruction/Multiple Data\rparen parallelism, 
one of Flynn's taxonomy \cite{flynn1972some}, is applicable to speed up the computation.
However, to execute SIMD instructions, we need to write an assembler or an intrinsic function.
Use SIMD intrinsic functions to handle SIMD instructions in high-level languages such as c and C++.

The goal of this study is that Pyker can compute particle interactions faster than non-parallelized code, and it takes fewer instructions.

For this purpose, Pyker generates the parallelized code using SIMD instructions from the Domain Specific Language\lparen DSL\rparen code for particle interaction.
A DSL is a programming language for solving specific problems.
Pyker generates the code to compute particle interactions from the definition of variables and 
the description of formulas.

In this paper, to investigate the accuracy of the computations performed by the code generated with Pyker, we use PIKG\cite{PIKG}. PIKG is a tool for automatically generating particle interaction kernel functions for FDPS\cite{FDPS} and other particle simulators, capable of generating kernel codes for various CPU and parallel architectures, including Intel CPU, Fujitsu A64FX, NVIDIA GPU, and PEZY-SC2, based on the same descriptions as Pyker.
We design Pyker to be compatible with PIKG so that we can input the same description in DSL into both PIKG and Pyker and then evaluate the relative errors in the computational results generated by the PIKG and Pyker. Furthermore, to evaluate the rate of acceleration of the SIMD code generated by Pyker, we compare its execution times with the code without SIMD parallelized by the generated PIKG.

We also generated a SIMD code using PIKG and measured its computation time using the same method to compare the performance of the computation speed of the codes generated by PIKG and Pyker, respectively.

We then applied these codes to the three particle interaction equations to see if there was any difference in computation time.
To evaluate the DSL code for Pyker, we compared the DSL code and generated code for Pyker.

In this paper, Section 2 explains how Pyker defines the particle interaction equation, Section 3 describes the process of code generation by Pyker, and Section 4 presents the results of the performance experiments.

\section{Definition of the particle interaction in DSL}

\subsection{Particle interaction}
In this section, we explain the information needed to compute the particle interaction, such as Equation\eqref{eq:gravity}, using an actual code.
Listing \ref{template} shows an example of C++ source code that performs the calculation 
in Equation \eqref{eq:gravity}.
% [frame=single, caption=skeletoncode, label=sleltoncode]

\begin{lstlisting}[frame=single, caption=gravitational\_interaction.cpp, label=template,  breaklines=false, language=c++, basicstyle=\small]

for (int i = 0; i < n; i++) {
double ax = 0.0;
double ay = 0.0;
double az = 0.0;

for (int j = 0; j < n; j++) {
    double dx = xj[j][0]-xi[i][0];
    double dy = xj[j][1]-xi[i][1];
    double dz = xj[j][2]-xi[i][2];
    double r2 = dx*dx+dy*dy+dz*dz+eps2;
    double ri2 = 1.0f/sqrt(r2);

    double mr = mj[j]*ri2*ri2*ri2;

    ax += double(mr*dx);
    ay += double(mr*dy);
    az += double(mr*dz);
}

acci[i][0] = ax;
acci[i][1] = ay;
acci[i][2] = az;
}
\end{lstlisting}

We briefly describe how this code corresponds to the Equation 
\eqref{eq:gravity}. The array variables acci, xi, mj, and xj correspond to
 $\vb{a}_i$, $\vb{x}_i$, $m_j$, and $\vb{x}_j$, respectively. And, the constants n and eps2, corresponds to $N$ and $\epsilon$
respectively. We need the nested loop with loop variables i and j. The inner loop calculates the acceleration for ith particle. The gravitational constant $G$ is not in the code because it can be calculated after the 
calculation of the particle interactions.

 From this code, we see that we need three categories of information to generate a code for particle interaction such as Listing \ref{template}.
\begin{itemize}
  \item The information on the type of each variable
  \item For array variables, we need to identify whether the variables are indexed by the loop variable i or j
  \item Which array variables are used to store the result

\end{itemize}

 With the definition of variables and the description of the
particle interaction using the variables, a code to calculate the
particle interaction can be generated.
The language specification in the next section of our DSL in the next section.

\subsection{Language specification}
There are two parts in the DSL for Pyker: (1) variable declaration and 
(2) particle interaction description.
First, we explain the variable definition.

The next section describes the process of generating SIMD code from the written code in this DSL.
\subsubsection{Variable declaration part}

In DSL for Pyker, variable declarations are defined as follows.

\begin{align*}
\text{\textless variable definition\textgreater} &::= \text{\textless category\textgreater\text{  }   \textless type\textgreater \text{  }  \textless name\textgreater} \\
\text{\textless category\textgreater} &::= \text{"EPI"} \mid \text{"EPJ"} \mid \text{"FORCE"} \mid \epsilon \\
\text{\textless type\textgreater} &::= \text{"vec3\textless F64\textgreater"} \mid \text{"F64"} \\
\text{\textless name\textgreater} &::= \text{\textless character\textgreater} \mid \text{ \{\textless character\textgreater \}}\\
\text{\textless character\textgreater} &::= \text{\textless letter\textgreater} \mid \text{\textless digit\textgreater} \mid "\_"\\
\text{\textless letter\textgreater} &::= \text{"a"} \mid \text{"b"} \mid ... \mid \text{"z"} \mid \text{"A"}\mid \text{"B"} ... \mid \text{"Z"}\\
\text{\textless digit\textgreater} &::= \text{"1"} \mid \text{"2"} \mid ... \mid \text{"9"} \\
\end{align*}

The above Backus-Naur form (BNF) representation of variable definitions is the grammar rule for variable definitions in our DSL.
Variable definitions are divided into three parts,\textless category\textgreater, \textless type\textgreater, and \textless name\textgreater.

\textless category\textgreater \text{ } defines a kind of variable, EPI and EPJ indicate that a variable to store data for particles i and j,
respectively. FORCE indicates that a variable to store the results. If there is no \textless category\textgreater in a variable definition, the variable is a constant or a temporary variable.
\textless type\textgreater \text{ } defines a type of variable
vec3 \textless F64 \textgreater represents vectors in 3 dimensions and F64 represents a scalar.

Vector elements and scalar are double-precision floating point numbers.

\textless name\textgreater \text{ } defines the variable name.

 An example of a variable definition is shown below.
\[
  EPI\text{ } vec3<F64> \text{ } ri
\]
It declares this variable is the EPI category, the type is vectors and the variable name is ri.

\subsubsection{Particle interaction expression part}
 % assignment, and '+=' for formulas.=, +=
 In our DSL, we use the defined variables either EPI, EPJ and temporary variables to, describe the particle interaction calculation. At the end of the description, we should assign the calculation result to the variables declared as the FORCE variables.

 We can use four basic arithmetic operations and the square root function sqrt(), the power function, and the vector inner product in the particle interaction expression. 
 We can use "*" to represent the inner product between two vectors such as, "x*y" when both x and y are vectors. For the power function, we use the notation of "x**a", where we calculate the power of x with respect to a.

 Listing \ref{pyker} is an example of a Pyker description of the calculation of the Equation\eqref{eq:gravity}.
 In this list, Lines from one to five are the declaration part and the remaining is the particle interaction expression part.
 For example, we assign the part of the calculation to the temporary variables rij, r2, and r\_inv in lines six, seven, and eight respectively.
 In this line, we compute the relative distance squared between particles using the inner product notation for "rij".

 In the last line, a temporary variable is used to assign the result of the calculation to ai, a FORCE variable, with '+='.

% , caption=gravity\_particle, label=pikg-example
\begin{lstlisting}[caption=example of the DSL,frame=single, numbers=left, label=pyker]
  EPI vec3<F64> ri
  EPJ vec3<F64> rj
  EPJ F64 mass
  EPJ F64 eps2
  FORCE vec3<F64> ai
  rij = ri - rj
  r2 = rij * rij + eps2
  r_inv = 1.0 / sqrt(r2)
  r2_inv = r_inv * r_inv
  mr_inv = mass * r_inv
  mr3_inv = r2_inv * mr_inv
  ai += mr3_inv * rij
\end{lstlisting}

The next section explains the processing of Pyker for generating SIMD code from code written in this DSL.

\section{Process of Pyker}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/flowchart_ver5.png}
\caption{Flow of Pyker}
\label{fig:flowchart}
\end{figure}

This section describes the processing flow of Pyker. The processing consists of four phases: Parsing, Type inference, Translation for SIMD instructions, and Code generation.

During the Parsing phase, a hash map of variable definitions is created from an input DSL, and expressions in the DSL are converted into an abstract syntax tree(AST). This hash map and AST are then passed to the next phase, Type inference. In the Type inference phase, the types of temporary variables are inferred.
Next, Translation for SIMD instructions phase, Pyker modifies the AST. Next, a SIMD code for the particle calculation is generated from the modified AST.

We use Sympy, a Python library for algebraic computation, to implement Pyker. With Sympy, an input DSL code is converted into Sympy's AST after the loading. In Pyker, we primarily process the AST using the API provided by Sympy.
In the following subsection, we describe each phase in more detail.

\subsection{Parsing phase}
The parsing phase converts the DSL code into a variable definition hash map (var\_map) and an expression syntax tree.
var\_map takes the variable name as key and an instance of the Var class defined in this study as value. the Var class holds the attributes of the variable, such as type and value. In Pyker, such as the type and value of the variable.
In addition, it also adds the numerical values contained in the syntax tree to the var\_map. This is because numerical values must also be vectorized as parallelization targets when applying SIMD instructions.

 To convert a formula into an AST, use the sympify() method. This method has the ability to take a formula in string form as an argument and convert it into an AST on Sympy.

var\_map and syntax tree are passed to the next process, the type inference phase. The type inference phase infers the types of temporary variables and prepares them for code generation.

\subsection{Type inference phase}
In this phase, the main focus is on type inference for temporary variables. 
In Pyker the types are only double-precision floating point numbers, so the focus is only on the inference of the dimension of a variable. It is necessary to know what the dimension of the value returned by a sub-expression is.
For example, in the case of the expression "x * y * z", if x and y are vectors and z is a scalar, we know that the result of the expression is a scalar. Therefore, we recursively traverse the AST to perform the type inference. During this process, we also replace the inner product with the 'dot' function. In Sympy, the FunctionCall object is used to define the function name and arguments, which can then be incorporated into the parse tree.

\subsection{Translation for SIMD instruction phase}
In this phase, Pyker performs the following three modifications to the  AST on Sympy.
\begin{itemize}
  \item Converting to a complete binary tree
  \item Identification of operators
  \item Replacing the operator nodes with SIMD intrinsic functions

\end{itemize}

In the AST on Sympy, if there are three or more terms with the same operator and order of computation, these terms are grouped as children of a single operator node as shown in Figure \ref{fig:f1}. However, SIMD instructions are binary operations. Therefore, it is necessary to convert the AST into a complete binary tree.

Additional modifications are required because the AST of Sympy only supports the nodes of the Add, Mul, and Pow operations. Add represents addition, Mul represents multiplication, and Pow represents power. And operations such as subtraction, division, and sqrt() are represented using these three operators. For example, Figure \ref{fig:f2} shows the AST of the expression 'a-b', which is a minus b. In addition, any operation indicating exponentiation is converted to multiple Mul operations since SIMD instructions do not support exponentiation.
And 'dot' methods, also translate the Mul and Add operations.

After the operator is identified, it is replaced by the corresponding SIMD intrinsic function by a FunctionCall object.
The FunctionCall object with the name of the intrinsic function corresponding to the operator replaces the node in the AST, and the corresponding intrinsic function is generated when the code is generated from the AST.

If the AST of Figure \ref{fig:f2} is replaced with an intrinsic function, the result is as shown in Figure \ref{fig:f3}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/multi_arg.png}
\caption{The Sympy AST of the expression'a+b+c'}
\label{fig:f1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/sub_tree.png}
\caption{The Sympy AST of the expression 'a-b'}
\label{fig:f2}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/SIMDintrisic.png}
\caption{The Sympy AST of the expression SIMD intrinsic function name FunctionCall object}
\label{fig:f3}
\end{figure}

\subsection{Code generation phase}
We use the ccode() method included in the Codegen module on Sympy in the code generation phase. The ccode() method generates the corresponding C++ code by passing a Sympy format as an argument.  So, the code that is generated by passing this AST to ccode() is an argument.

In addition to this, there are other elements necessary for SIMD. This is done by loading multiple data into a wide-bit SIMD register and then executing a single instruction between these registers. Therefore, there is loading of data into SIMD register, store of results, and so on. These processes are put into a Sympy format and the desired code is generated.
% SIMDを行うには、
% 例えば、配列x,yの要素同士の足し算を行うとき、
% 以下のようなる。

% \ref{lst:simd}
% SIMD calculations use dedicated SIMD registers.

\section{Execution Environment}

Table \ref{tb:exe} is the execution environment.
The code generated by Pyker used AVX2 as the SIMD instruction set.

Therefore, the SIMD parallelization code for PIKG was also made to use the AVX2 instruction set as well.

			\begin{table*}[htb]
                    \centering
				\caption{Execution Environment}
				\label{tb:exe}
				\begin{tabular}{|c||c|} \hline
					OS & Windows Subsystem for Linux  \\ \hline 
					CPU & AMD Ryzen 5 3600 6-Core Processor 3.60 GHz \\ \hline
                        compiler & g++ 9.4.0 \\ \hline
					compile option & mavx2, O3   \\ \hline
					SIMD instruction & AVX2  \\ \hline
				\end{tabular}
			\end{table*}

\section{Experiments}
In this section, we present the evaluation of Pyker. For the evaluation, we use three particle interactions: Case A is the gravity interaction as shown in Equation\eqref{eq:gravity}. 
Case B is the gravitational interaction used in the Hermite integration as shown in Equation \ref{eq:hermite}, And Case C is the Lennard-Jones interaction used in the molecular dynamics as shown in Equation \ref{eq:lennard}.

We also compared the number of operations in DSL for Pyker description of each Case with the number of intrinsic functions in generated code for Pyker to evaluate Whether the DSL code could have been written with less code than the parallelized code.

And for each, the DSL code for Pyker is shown.

\begin{align}\label{eq:hermite}
F &= \sum\limits_{j\neq i}^N \frac{m_j \cdot \mathbf{r_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2\right)^{\frac{3}{2}}}, &
J &= \sum\limits_{j\neq i}^N \frac{m_j \cdot \mathbf{v_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{3}{2}}} - \frac{3 \cdot m_j \cdot \mathbf{r_{ij}} \cdot \mathbf{v_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{5}{2}}}
\end{align}

\begin{align}\label{eq:lennard}
U =\sum\limits_{j\neq i}^N  4 \left[ \left( \frac{1}{r_{ij}} \right)^{12} - \left( \frac{1}{r_{ij}} \right)^{6} 
\right],
F =\sum\limits_{j\neq i}^N  4 \left[ 12\left( \frac{1}{r_{ij}} \right)^{11} - 6\left( \frac{1}{r_{ij}} \right)^{5}\right]
\end{align}

We generate three codes in each case by using both Pyker and PIKG:(1) the code generated without parallelization in PIKG (non-SIMD-PIKG), (2) the code generated with SIMD parallelization in PIKG (SIMD-PIKG), and (3) the code generated from Pyker (SIMD-Pyker) generated from Pyker. The AVX2 instructions were used for SIMD parallelization of both PIKG and Pyker. We ran these codes and measured the execution times.

The experimental results are presented in Tables \ref{tb:resultA}, 3, and 4. In all tables, the first column shows the number of particles $N$. The second, third, and fourth columns show the execution time of SIMD-Pyker $T_{Pyker}$, non-SIMD-PIKG $T_{Ref}$, and SIMD-PIKG $T_{PIKG}$, respectively. The fifth column shows the ratio between $T_{Ref}$ and $T_{Pyker}$ which indicates how much faster SIMD-Pyker is than non-SIMD-PIKG. Also, the sixth column shows the ratio between $T_{PIKG}$ and $T_{Pyker}$ which represents how much faster SIMD-Pyker is than SIMD-PIKG.

    \subsection{Case A}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\linewidth]{seminar/caseA.png}
\caption{DSL code of Case A}
\label{fig:caseA}
\end{figure}

Figure \ref{fig:caseA} shows the DSL code of Case A.

The results of the evaluation of Case A are shown in Table \ref{tb:resultA}.
$S_{Ref}$ in Table \ref{tb:resultA} is greater than four for any N. SIMD-Pyker was computed more than four times faster than SIMD-PIKG. Also, since $S_{PIKG}$ is about one for every N, SIMD-Pyker had about the same computation time as SIMD-PIKG.

\subsection{Case B}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/caseB.png}
\caption{DSL code of Case B}
\label{fig:CaseB}
\end{figure}
Figure \ref{fig:CaseB} shows the DSL code of Case B.
The computation time results in B are shown in Table \ref{tb:resultB}.$S_{Ref}$ is almost the same as Case A. Also, $S_{PIKG}$ is 0.7 to 0.8 for any N. Therefore, in case B, SIMD-Pyker was slower than SIMD-PIKG.

\subsection{Case C}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{seminar/caseC.png}
\caption{DSL code of Case C}
\label{fig:CaseC}
\end{figure}
Figure \ref{fig:CaseC} shows the DSL for Case C.
The results of the computation in C are shown in Table \ref{tb:resultC}. $S_{Ref}$ in Table \ref{tb:resultC} is greater than 4.5 for any N. Therefore, $T_{Pyker}$ was computed more than 4.5 times faster than $T_{Ref}$. $S_PIKG$ is almost the same as Case A. Therefore, $T_{Pyker}$ had about the same computation time as $T_{PIKG}$.

 \subsection{Evaluation of DSL code}
Table \ref{tb:dslev} shows the number of operations in the DSL and the number of intrinsic functions in the Pyker-generated code for Cases A, B, and C, respectively.

$i_f$ is the number of intrinsic functions in cases A, B, and C.
$D_p$ is the number of operations in DSL for Pyker in cases A, B, and C.
In DSL operations, "+, -, /, *, sqrt(), **" are each one operation.

The table shows that in all cases the DSL code has fewer operations.

		\begin{table}[htb]
                    \centering
				\caption{Compare $i_f$ and $D_p$}
				\label{tb:dslev}
				\begin{tabular}{|c||c|c|c|} \hline
 & Case A & Case B & Case C  \\ \hline\hline
$D_p$ &9 &18& 25\\ \hline
$i_f$&31&64& 40\\ \hline
				\end{tabular}
			\end{table}

\section{Discussion}

From the experimental results, SIMD-Pyker was more than four times faster in execution time than non-SIMD-PIKG in all cases. SIMD Parallelized computations are proportionally faster than non-parallelized computations in terms of the number of data computed simultaneously. SIMD parallelized computations are twice as fast as non-parallelized computations in terms of the number of data simultaneously computed. Pyker used the AVX2 SIMD instruction set, and the SIMD registers used in this instruction set are 256-bit. In addition, all variable types are 64-bit precision floating numbers in this experiment. Therefore, four variables were loaded into the SIMD registers and computed, the speed up with SIMD is up to four times faster than when processing non-parallelized computations. Therefore, SIMD-Pyker was able to achieve the maximum speedup expected.

 However, in case B, SIMD-Pyker is slower than SIMD-PIKG. The most likely cause is the most computationally intensive process, the innermost process of the nested loop. To compare these processes, Table \ref{tb:table} shows the number of calls to the intrinsic function of the nested loop in SIMD-Pyker and SIMD-PIKG for each of cases A, B, and C. In Case B, SIMD-Pyker and SIMD-PIKG both have more number of operations than A and C.
		\begin{table}[htb]
				\caption{Number of intrinsic functions}
				\label{tb:table}
				\begin{tabular}{|c||c|c|c|} \hline
				  & case of A & case of B & case of C \\ \hline \hline
				Pyker & 22 & 46 & 26 \\ \hline
			PIKG	& 18 & 40 & 27  \\ \hline
				\end{tabular}

			\end{table}

\section{Conclusion}
SIMD-Pyker was computationally faster than the non-SIMD-PIKG code in all cases.
In addition, Pyker had fewer DSL operators than the number of intrinsic functions in the generated code in any case.

    \begin{table}[bht]
            \centering

            \caption{Result of Case A}
            \label{tb:resultA}
                \begin{tabular}{|c||c|c|c|c|c|} \hline
N &$T_{Pyker}$(sec)&$T_{Ref}$(sec)&$T_{PIKG}$(sec)&$S_{Ref}$&$S_{PIKG}$\\ \hline\hline
50000 &2.477  &10.794& 2.440& 4.36 & 0.99 \\ \hline
25000 & 0.617  &2.693& 0.599& 4.36 & 0.97 \\ \hline
10000 &0.095   &0.425& 0.095& 4.48 & 1.00 \\ \hline
 1000 &0.001   &0.004& 0.001& 4.52 & 1.05 \\ \hline

                \end{tabular}\hfill
    \end{table}
    \begin{table}[htb]
                \centering
				\caption{Rusult of Case B}
				\label{tb:resultB}
				\begin{tabular}{|c||c|c|c|c|c|} \hline
N & $T_{Pyker}$(sec) & $T_{Ref}$ (sec) & $T_{PIKG}$(sec) &$S_{Ref}$ & $S_{PIKG}$ \\ \hline\hline
50000 & 5.282&22.768 &4.059 & 4.31&0.77\\ \hline
25000 & 1.323& 5.740&1.008 & 4.34&0.76\\  \hline
10000 & 0.214&0.902 &0.169 & 4.22&0.76 \\ \hline
1000  &0.002&0.009 & 0.002 & 4.30&0.81\\  \hline
				\end{tabular}
        \end{table}

		\begin{table}[htb]
                    \centering
				\caption{Result of Case C}
				\label{tb:resultC}
				\begin{tabular}{|c||c|c|c|c|c|} \hline
N & $T_{Pyker}$(sec) & $T_{Ref}$(sec) & $T_{PIKG}$(sec) &$S_{Ref}$ & $S_{PIKG}$ \\ \hline\hline
50000 &2.154 &9.904& 2.195& 4.60& 1.02\\ \hline
25000 &0.542 &2.480& 0.554& 4.57& 1.02\\ \hline
10000 &0.086 &0.399& 0.087& 4.66& 1.02\\ \hline
 1000 &0.001 &0.004& 0.001& 4.50& 1.01\\ \hline

				\end{tabular}
			\end{table}

    % \begin{table}[htb]
    %         \centering
    %         \caption{Number of line of each code}
    %         \label{tb:column}
    %             \begin{tabular}{|c|c|c|c|c|} \hline
    %     Nbody  & Hermite  & Lennard Jones  \\ \hline
    %     gravity particle & 70 & 12 \\ \hline
    %     Hermite               & 123 & 20  \\ \hline
    %     Lennard Jones         &60 & 22  \\ \hline

    %             \end{tabular}
    % \end{table}

	\bibliography{biblist}

% F = \frac{m_j \cdot \mathbf{r_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{3}{2}}}
% \begin{equation}
% F = \frac{m_j \cdot \mathbf{r_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{3}{2}}}
% \end{equation}

% rij = ri - rj, vij = vi - vj, \\

% \begin{align}
% F = m_j\frac{ \mathbf{\mathbf{r_i} - \mathbf{r_j}}}{\left|\mathbf{r_i} - \mathbf{r_j}\right|^3}, &
% J = m_j \frac{\mathbf{v_i} - \mathbf{v_j}}{\left|\mathbf{r_i} - \mathbf{r_j}\right|^3} - 3 m_j \frac{(\mathbf{r_i} - \mathbf{r_j})  (\mathbf{v_i} - \mathbf{v_j})}{\left|\mathbf{r_i} - \mathbf{r_j}\right|^5}
% \end{align}

\end{document}

% \begin{lstlisting}[frame=single]
%   dx0 = pos[i][0] - pos[j][0]
%   dx1 = pos[i + 1][0] - pos[j][0]
%   dx2 = pos[i + 2][0] - pos[j][0]
%   dx3 = pos[i + 3][0] - pos[j][0]
% \end{lstlisting}

% \begin{lstlisting}[frame=single]
%   (x1, x2, x3, x4) + (y1, y2, y3, y)

% \end{lstlisting}

% \begin{align}
% F &= \frac{m_j \cdot \mathbf{r_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{3}{2}}}, &
% J &= \frac{m_j \cdot \mathbf{v_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{3}{2}}} - \frac{3 \cdot m_j \cdot \mathbf{r_{ij}} \cdot \mathbf{v_{ij}}}{\left( \mathbf{r_{ij}}^2 + \epsilon^2 \right)^{\frac{5}{2}}}
% \end{align}

% \end{document} 
% \begin{}

### 2024-02-20 dsl/experiment/Hermite/Hermite_pyker_kernel_AVX2.cpp

@@ -1,0 +1,136 @@
+#include<math.h>
+#include<x86intrin.h>
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d vi_tmp_v0;
+   __m256d vi_tmp_v1;
+   __m256d vi_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d vj_tmp_v0;
+   __m256d vj_tmp_v1;
+   __m256d vj_tmp_v2;
+   __m256d mj_tmp;
+   __m256d eps2_tmp;
+   __m256d F_tmp_v0;
+   __m256d F_tmp_v1;
+   __m256d F_tmp_v2;
+   __m256d J_tmp_v0;
+   __m256d J_tmp_v1;
+   __m256d J_tmp_v2;
+   __m256d float_0_tmp;
+   float_0_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(3.0);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d dv_tmp_v0;
+   __m256d dv_tmp_v1;
+   __m256d dv_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r1i_tmp;
+   __m256d r2i_tmp;
+   __m256d r3i_tmp;
+   __m256d r5i_tmp;
+   __m256d rv_tmp;
+   __m256d af_tmp;
+   __m256d jf_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
[…]

### 2024-02-20 dsl/experiment/Hermite/Hermite_pyker_kernel_AVX2.hpp

@@ -1,0 +1,132 @@
+#include<math.h>
+#include<x86intrin.h>
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d vi_tmp_v0;
+   __m256d vi_tmp_v1;
+   __m256d vi_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d vj_tmp_v0;
+   __m256d vj_tmp_v1;
+   __m256d vj_tmp_v2;
+   __m256d mj_tmp;
+   __m256d eps2_tmp;
+   __m256d F_tmp_v0;
+   __m256d F_tmp_v1;
+   __m256d F_tmp_v2;
+   __m256d J_tmp_v0;
+   __m256d J_tmp_v1;
+   __m256d J_tmp_v2;
+   __m256d float_0_tmp;
+   float_0_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(3.0);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d dv_tmp_v0;
+   __m256d dv_tmp_v1;
+   __m256d dv_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r1i_tmp;
+   __m256d r2i_tmp;
+   __m256d r3i_tmp;
+   __m256d r5i_tmp;
+   __m256d rv_tmp;
+   __m256d af_tmp;
+   __m256d jf_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
[…]

### 2024-02-20 dsl/experiment/Hermite/Hermite_pyker_kernel_test_0219.hpp

@@ -1,0 +1,143 @@
+#include<math.h>
+#include<x86intrin.h>
+int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
+   int i;
+   int j;
+   __m256d ri_tmp_v0;
+   __m256d ri_tmp_v1;
+   __m256d ri_tmp_v2;
+   __m256d vi_tmp_v0;
+   __m256d vi_tmp_v1;
+   __m256d vi_tmp_v2;
+   __m256d rj_tmp_v0;
+   __m256d rj_tmp_v1;
+   __m256d rj_tmp_v2;
+   __m256d vj_tmp_v0;
+   __m256d vj_tmp_v1;
+   __m256d vj_tmp_v2;
+   __m256d mj_tmp;
+   __m256d eps2_tmp;
+   __m256d F_tmp_v0;
+   __m256d F_tmp_v1;
+   __m256d F_tmp_v2;
+   __m256d J_tmp_v0;
+   __m256d J_tmp_v1;
+   __m256d J_tmp_v2;
+   __m256d float_0_tmp;
+   float_0_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(3.0);
+   __m256d dr_tmp_v0;
+   __m256d dr_tmp_v1;
+   __m256d dr_tmp_v2;
+   __m256d dv_tmp_v0;
+   __m256d dv_tmp_v1;
+   __m256d dv_tmp_v2;
+   __m256d r2_tmp;
+   __m256d r1i_tmp;
+   __m256d r2i_tmp;
+   __m256d r3i_tmp;
+   __m256d r5i_tmp;
+   __m256d rv_tmp;
+   __m256d af_tmp;
+   __m256d jf_tmp;
+   for (i = 0; i < n; i += 4) {
+      int index_gather_0[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
+      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
+      int index_gather_1[4] = {0, 3, 6, 9};
+      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
[…]

### 2024-02-20 dsl/experiment/Hermite/pyker_kernel_AVX2.hpp

@@ -1,5 +1,5 @@
 #include<math.h>
-#include<x86intrin.h>;
+#include<x86intrin.h>
 int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
    int i;
    int j;
@@ -81,27 +81,39 @@ int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3]
          dv_tmp_v0 = _mm256_sub_pd(vi_tmp_v0, vj_tmp_v0);
          dv_tmp_v1 = _mm256_sub_pd(vi_tmp_v1, vj_tmp_v1);
          dv_tmp_v2 = _mm256_sub_pd(vi_tmp_v2, vj_tmp_v2);
-         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(
-                                          _mm256_add_pd(
-                                             _mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), 
-                                             _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)),
-                                             _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2)));
-         r1i_tmp = _mm256_div_pd(float_0_tmp, _mm256_sqrt_pd(r2_tmp));
+         r2_tmp = _mm256_add_pd(eps2_tmp,
+          _mm256_add_pd(                   
+         _mm256_add_pd(
+         _mm256_mul_pd(dr_tmp_v0, dr_tmp_v0), 
+         _mm256_mul_pd(dr_tmp_v1, dr_tmp_v1)),
+         _mm256_mul_pd(dr_tmp_v2, dr_tmp_v2)));
+         r1i_tmp = _mm256_div_pd(float_0_tmp, 
+         _mm256_sqrt_pd(r2_tmp));
          r2i_tmp = _mm256_mul_pd(r1i_tmp, r1i_tmp);
          r3i_tmp = _mm256_mul_pd(r1i_tmp, r2i_tmp);
          r5i_tmp = _mm256_mul_pd(r2i_tmp, r3i_tmp);
          rv_tmp = _mm256_add_pd(
-                  _mm256_add_pd(_mm256_mul_pd(dr_tmp_v0, dv_tmp_v0), 
[…]

### 2024-02-20 dsl/experiment/Hermite/test_pikg_code.cpp

@@ -1,0 +1,45 @@
+
+#include<x86intrin.h>
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+
+struct EPI {
+   pikg_f64vec3 r;
+   pikg_f64vec3 v;
+};
+
+struct EPJ{
+   pikg_f64vec3 r;
+   pikg_f64vec3 v;
+   double m;
+   double eps;
+};
+
+struct FORCE {
+   pikg_f64vec3 f;
+   pikg_f64vec3 j;
+};
+#include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel_AVX2.hpp"
+
+int main() {
+
+      int n = 0;
+   
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI *epi = new EPI[nepi];
+   EPJ *epj = new EPJ[nepj];
+   FORCE *force = new FORCE[n];
+   Kernel pikg_kernel;
+   pikg_kernel(epi, nepi, epj, nepj, force);
+
+}

### 2024-02-20 dsl/experiment/LennardJones/LennardJones.cpp

@@ -1,0 +1,142 @@
+#include<x86intrin.h>
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+// using namespace std;
+
+
+struct EPI{
+  double rx,ry,rz;
+};
+
+struct EPJ{
+   double rx,ry,rz;
+   double eps;
+};
+
+struct FORCE{
+  double fx,fy,fz;
+  double p;
+};
+
+#include "pikg_kernel.hpp"
+#include "pyker_kernel.hpp"
+// #include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel_AVX2.hpp"
+
+// 乱数を生成するための関数
+double rand_double(double min, double max) {
+   return min + (double)rand() / ((double)RAND_MAX / (max - min));
+}
+
+
+double calculate_difference(double a, double b) {
+   double diff = 0.0;
+   diff += fabs(a - b);   
+   return diff;
+}
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n;
+
+   std::cin >> n;
+
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI *epi = new EPI[nepi];
+   EPJ *epj = new EPJ[nepj];
+   FORCE *force = new FORCE[n];
+   Kernel pikg_kernel;
+
+
+   double (*rix) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*riz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjx) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double (*rjz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
+   double *mj = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
[…]

### 2024-02-20 dsl/experiment/LennardJones/pikg_check.cpp

@@ -1,0 +1,48 @@
+#include<x86intrin.h>
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+// using namespace std;
+
+
+struct EPI{
+  double rx,ry,rz;
+};
+
+struct EPJ{
+   double rx,ry,rz;
+   double eps;
+};
+
+struct FORCE{
+  double fx,fy,fz;
+  double p;
+};
+
+#include "pikg_kernel_AVX2.hpp"
+
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n =0 ;
+
+   // std::cin >> n;
+
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI *epi = new EPI[nepi];
+   EPJ *epj = new EPJ[nepj];
+   FORCE *force = new FORCE[n];
+   Kernel pikg_kernel;
+
+  pikg_kernel(epi, nepi, epj, nepj, force);
+
+}

### 2024-02-20 dsl/experiment/LennardJones/pikg_kernel_AVX2.hpp

@@ -1,0 +1,753 @@
+#include<pikg_vector.hpp>
+#include<cmath>
+#include<limits>
+#include<chrono>
+
+#include <pikg_avx2.hpp>
+struct Kernel{
+Kernel(){}
+void initialize(){
+}
+int kernel_id = 0;
+void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
+static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
+static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
+static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
+if(kernel_select>=0) kernel_id = kernel_select;
+if(kernel_id == 0){
+std::cout << "ni: " << ni << " nj:" << nj << std::endl;
+FORCE* force_tmp = new FORCE[ni];
+std::chrono::system_clock::time_point  start, end;
+double min_time = std::numeric_limits<double>::max();
+{ // test Kernel_I4_J1
+for(int i=0;i<ni;i++) force_tmp[i] = force[i];
+start = std::chrono::system_clock::now();
+Kernel_I4_J1(epi,ni,epj,nj,force_tmp);
+end = std::chrono::system_clock::now();
+double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
+std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
+if(min_time > elapsed){
+min_time = elapsed;
+kernel_id = 1;
+}
+}
[…]

### 2024-02-20 dsl/experiment/LennardJones/pyker_check.cpp

@@ -1,0 +1,9 @@
+
+
+#include "pyker_kernel_AVX2.hpp"
+
+
+int main() {
+
+   int n =0 ;
+}

### 2024-02-20 dsl/experiment/LennardJones/pyker_code.hpp

@@ -1,33 +1,0 @@
-#include<math.h>
-;
-int kernel(int n, double ri[][3], double rj[][3], double fr[][3], double p[], double eps){
-   int i;
-   int j;
-   double dr_v0;
-   double dr_v1;
-   double dr_v2;
-   double r2;
-   double r2i;
-   double f;
-   double x0;
-   for (i = 0; i < n; i += 1) {
-      ;
-      ;
-      for (j = 0; j < n; j += 1) {
-         ;
-         dr_v0 = ri[i][0] - rj[j][0];
-         dr_v1 = ri[i][1] - rj[j][1];
-         dr_v2 = ri[i][2] - rj[j][2];
-         r2 = eps + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
-         r2i = 1.0/r2;
-         x0 = r2i*(r2i*r2i);
-         f = (r2i*(r2i*(r2i*r2i)))*(48.0*x0 - 24.0);
-         fr[i][0] += dr_v0*f;
-         fr[i][1] += dr_v1*f;
-         fr[i][2] += dr_v2*f;
-         p[i] += (4.0*x0)*(x0 - 1.0);
-      };
-      ;
-   };
-   return 0;
-};

### 2024-02-20 dsl/experiment/LennardJones/pyker_kernel.hpp

@@ -1,0 +1,33 @@
+#include<math.h>
+;
+int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
+   int i;
+   int j;
+   double dx;
+   double dy;
+   double dz;
+   double r2;
+   double r2i;
+   double r6i;
+   double f;
+   for (i = 0; i < n; i += 1) {
+      ;
+      ;
+      for (j = 0; j < n; j += 1) {
+         ;
+         dx = rix[i] - rjx[j];
+         dy = riy[i] - rjy[j];
+         dz = riz[i] - rjz[j];
+         r2 = dz*dz + (dy*dy + (dx*dx + eps[j]));
+         r2i = 1.0/r2;
+         r6i = r2i*(r2i*r2i);
+         f = (r2i*r6i)*(48.0*r6i - 24.0);
+         fx[i] += dx*f;
+         fy[i] += dy*f;
+         fz[i] += dz*f;
+         p[i] += (4.0*r6i)*(r6i - 1.0);
+      };
+      ;
+   };
+   return 0;
+};

### 2024-02-20 dsl/experiment/LennardJones/pyker_kernel_AVX2.hpp

@@ -1,0 +1,76 @@
+#include<math.h>
+#include<x86intrin.h>;
+int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
+   int i;
+   int j;
+   __m256d rix_tmp;
+   __m256d riy_tmp;
+   __m256d riz_tmp;
+   __m256d rjx_tmp;
+   __m256d rjy_tmp;
+   __m256d rjz_tmp;
+   __m256d eps_tmp;
+   __m256d fx_tmp;
+   __m256d fy_tmp;
+   __m256d fz_tmp;
+   __m256d p_tmp;
+   __m256d float_4_tmp;
+   float_4_tmp = _mm256_set1_pd(1.0);
+   __m256d float_1_tmp;
+   float_1_tmp = _mm256_set1_pd(48.0);
+   __m256d float_2_tmp;
+   float_2_tmp = _mm256_set1_pd(24.0);
+   __m256d float_3_tmp;
+   float_3_tmp = _mm256_set1_pd(4.0);
+   __m256d dx_tmp;
+   __m256d dy_tmp;
+   __m256d dz_tmp;
+   __m256d r2_tmp;
+   __m256d r2i_tmp;
+   __m256d r6i_tmp;
+   __m256d f_tmp;
+   for (i = 0; i < n; i += 4) {
+      rix_tmp = _mm256_load_pd(&rix[i]);
+      riy_tmp = _mm256_load_pd(&riy[i]);
+      riz_tmp = _mm256_load_pd(&riz[i]);
+      fx_tmp = _mm256_set1_pd(0.0);
+      fy_tmp = _mm256_set1_pd(0.0);
+      fz_tmp = _mm256_set1_pd(0.0);
+      p_tmp = _mm256_set1_pd(0.0);
+      for (j = 0; j < n; j += 1) {
+         rjx_tmp = _mm256_set1_pd(rjx[j]);
+         rjy_tmp = _mm256_set1_pd(rjy[j]);
+         rjz_tmp = _mm256_set1_pd(rjz[j]);
+         eps_tmp = _mm256_set1_pd(eps[j]);
+
+         
+         dx_tmp = _mm256_sub_pd(rix_tmp, rjx_tmp);
+         dy_tmp = _mm256_sub_pd(riy_tmp, rjy_tmp);
[…]

### 2024-02-20 dsl/experiment/LennardJones/pyker_simd_code.hpp

@@ -1,78 +1,0 @@
-#include<math.h>
-#include<x86intrin.h>;
-int kernel(int n, double ri[][3], double rj[][3], double fr[][3], double p[], double eps){
-   int i;
-   int j;
-   __m256d ri_tmp_v0;
-   __m256d ri_tmp_v1;
-   __m256d ri_tmp_v2;
-   __m256d rj_tmp_v0;
-   __m256d rj_tmp_v1;
-   __m256d rj_tmp_v2;
-   __m256d fr_tmp_v0;
-   __m256d fr_tmp_v1;
-   __m256d fr_tmp_v2;
-   __m256d p_tmp;
-   __m256d eps_tmp;
-   eps_tmp = _mm256_set1_pd(eps);
-   __m256d float_4_tmp;
-   float_4_tmp = _mm256_set1_pd(1.0);
-   __m256d float_1_tmp;
-   float_1_tmp = _mm256_set1_pd(48.0);
-   __m256d float_2_tmp;
-   float_2_tmp = _mm256_set1_pd(24.0);
-   __m256d float_3_tmp;
-   float_3_tmp = _mm256_set1_pd(4.0);
-   __m256d dr_tmp_v0;
-   __m256d dr_tmp_v1;
-   __m256d dr_tmp_v2;
-   __m256d r2_tmp;
-   __m256d r2i_tmp;
-   __m256d f_tmp;
-   __m256d x0_tmp;
-   for (i = 0; i < n; i += 4) {
-      int index_gather_0[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
-      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
-      int index_gather_1[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
-      ri_tmp_v1 = _mm256_i32gather_pd(&ri[i][1], vindex_gather_1, 8);
-      int index_gather_2[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_2 = _mm_load_si128((const __m128i*)index_gather_2);
[…]

### 2024-02-20 dsl/experiment/LennardJones_ver2/LennardJones.cpp

@@ -1,142 +1,0 @@
-#include<x86intrin.h>
-#include<stdio.h>
-#include<pikg_vector.h>
-#include<pikg_vector.hpp>
-#include<cstdlib> // 乱数生成のために必要
-#include<ctime> // 乱数のシード設定のために必要
-// #include<algorithm>
-#include<cmath>
-#include<time.h>
-#include<iostream>
-// using namespace std;
-
-
-struct EPI{
-  double rx,ry,rz;
-};
-
-struct EPJ{
-   double rx,ry,rz;
-   double eps;
-};
-
-struct FORCE{
-  double fx,fy,fz;
-  double p;
-};
-
-#include "pikg_kernel.hpp"
-#include "pyker_kernel.hpp"
-// #include "pikg_kernel_AVX2.hpp"
-// #include "pyker_kernel_AVX2.hpp"
-
-// 乱数を生成するための関数
-double rand_double(double min, double max) {
-   return min + (double)rand() / ((double)RAND_MAX / (max - min));
-}
-
-
-double calculate_difference(double a, double b) {
-   double diff = 0.0;
-   diff += fabs(a - b);   
-   return diff;
-}
-
-int main() {
-   srand((unsigned)time(NULL)); // 乱数のシードを設定
-
-   int n;
-
-   std::cin >> n;
-
-   //PIKG用のコード
-   const int nepi = n; 
-   const int nepj = n; 
-   EPI *epi = new EPI[nepi];
-   EPJ *epj = new EPJ[nepj];
-   FORCE *force = new FORCE[n];
-   Kernel pikg_kernel;
-
-
-   double (*rix) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double (*riy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double (*riz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double (*rjx) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double (*rjy) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double (*rjz) = static_cast<double(*)>(aligned_alloc(32, n * sizeof(double))); 
-   double *mj = static_cast<double*>(aligned_alloc(32, n * sizeof(double)));
[…]

### 2024-02-20 dsl/experiment/LennardJones_ver2/pikg_kernel.hpp

@@ -1,157 +1,0 @@
-#include<pikg_vector.hpp>
-#include<cmath>
-#include<limits>
-#include<chrono>
-
-struct Kernel{
-Kernel(){}
-void initialize(){
-}
-int kernel_id = 0;
-void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
-static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
-static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
-static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
-if(kernel_select>=0) kernel_id = kernel_select;
-if(kernel_id == 0){
-std::cout << "ni: " << ni << " nj:" << nj << std::endl;
-FORCE* force_tmp = new FORCE[ni];
-std::chrono::system_clock::time_point  start, end;
-double min_time = std::numeric_limits<double>::max();
-{ // test Kernel_I1_J1
-for(int i=0;i<ni;i++) force_tmp[i] = force[i];
-start = std::chrono::system_clock::now();
-Kernel_I1_J1(epi,ni,epj,nj,force_tmp);
-end = std::chrono::system_clock::now();
-double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
-std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
-if(min_time > elapsed){
-min_time = elapsed;
-kernel_id = 1;
-}
-}
-delete[] force_tmp;
-} // if(kernel_id == 0)
-if(kernel_id == 1) Kernel_I1_J1(epi,ni,epj,nj,force);
-} // operator() definition 
[…]

### 2024-02-20 dsl/experiment/LennardJones_ver2/pikg_kernel_AVX2.hpp

@@ -1,748 +1,0 @@
-#include<pikg_vector.hpp>
-#include<cmath>
-#include<limits>
-#include<chrono>
-
-#include <pikg_avx2.hpp>
-struct Kernel{
-Kernel(){}
-void initialize(){
-}
-int kernel_id = 0;
-void operator()(const EPI* __restrict__ epi,const int ni,const EPJ* __restrict__ epj,const int nj,FORCE* __restrict__ force,const int kernel_select = 1){
-static_assert(sizeof(EPI) == 24,"check consistency of EPI member variable definition between PIKG source and original source");
-static_assert(sizeof(EPJ) == 32,"check consistency of EPJ member variable definition between PIKG source and original source");
-static_assert(sizeof(FORCE) == 32,"check consistency of FORCE member variable definition between PIKG source and original source");
-if(kernel_select>=0) kernel_id = kernel_select;
-if(kernel_id == 0){
-std::cout << "ni: " << ni << " nj:" << nj << std::endl;
-FORCE* force_tmp = new FORCE[ni];
-std::chrono::system_clock::time_point  start, end;
-double min_time = std::numeric_limits<double>::max();
-{ // test Kernel_I4_J1
-for(int i=0;i<ni;i++) force_tmp[i] = force[i];
-start = std::chrono::system_clock::now();
-Kernel_I4_J1(epi,ni,epj,nj,force_tmp);
-end = std::chrono::system_clock::now();
-double elapsed = std::chrono::duration_cast<std::chrono::nanoseconds>(end-start).count();
-std::cerr << "kerel 1: " << elapsed << " ns" << std::endl;
-if(min_time > elapsed){
-min_time = elapsed;
-kernel_id = 1;
-}
-}
[…]

### 2024-02-20 dsl/experiment/LennardJones_ver2/pyker_kernel.hpp

@@ -1,33 +1,0 @@
-#include<math.h>
-;
-int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
-   int i;
-   int j;
-   double dx;
-   double dy;
-   double dz;
-   double r2;
-   double r2i;
-   double r6i;
-   double f;
-   for (i = 0; i < n; i += 1) {
-      ;
-      ;
-      for (j = 0; j < n; j += 1) {
-         ;
-         dx = rix[i] - rjx[j];
-         dy = riy[i] - rjy[j];
-         dz = riz[i] - rjz[j];
-         r2 = dz*dz + (dy*dy + (dx*dx + eps[j]));
-         r2i = 1.0/r2;
-         r6i = r2i*(r2i*r2i);
-         f = (r2i*r6i)*(48.0*r6i - 24.0);
-         fx[i] += dx*f;
-         fy[i] += dy*f;
-         fz[i] += dz*f;
-         p[i] += (4.0*r6i)*(r6i - 1.0);
-      };
-      ;
-   };
-   return 0;
-};

### 2024-02-20 dsl/experiment/LennardJones_ver2/pyker_kernel_AVX2.hpp

@@ -1,63 +1,0 @@
-#include<math.h>
-#include<x86intrin.h>;
-int kernel(int n, double rix[], double riy[], double riz[], double rjx[], double rjy[], double rjz[], double eps[], double fx[], double fy[], double fz[], double p[]){
-   int i;
-   int j;
-   __m256d rix_tmp;
-   __m256d riy_tmp;
-   __m256d riz_tmp;
-   __m256d rjx_tmp;
-   __m256d rjy_tmp;
-   __m256d rjz_tmp;
-   __m256d eps_tmp;
-   __m256d fx_tmp;
-   __m256d fy_tmp;
-   __m256d fz_tmp;
-   __m256d p_tmp;
-   __m256d float_4_tmp;
-   float_4_tmp = _mm256_set1_pd(1.0);
-   __m256d float_1_tmp;
-   float_1_tmp = _mm256_set1_pd(48.0);
-   __m256d float_2_tmp;
-   float_2_tmp = _mm256_set1_pd(24.0);
-   __m256d float_3_tmp;
-   float_3_tmp = _mm256_set1_pd(4.0);
-   __m256d dx_tmp;
-   __m256d dy_tmp;
-   __m256d dz_tmp;
-   __m256d r2_tmp;
-   __m256d r2i_tmp;
-   __m256d r6i_tmp;
-   __m256d f_tmp;
-   for (i = 0; i < n; i += 4) {
-      rix_tmp = _mm256_load_pd(&rix[i]);
-      riy_tmp = _mm256_load_pd(&riy[i]);
-      riz_tmp = _mm256_load_pd(&riz[i]);
-      fx_tmp = _mm256_set1_pd(0.0);
-      fy_tmp = _mm256_set1_pd(0.0);
-      fz_tmp = _mm256_set1_pd(0.0);
-      p_tmp = _mm256_set1_pd(0.0);
-      for (j = 0; j < n; j += 1) {
-         rjx_tmp = _mm256_set1_pd(rjx[j]);
-         rjy_tmp = _mm256_set1_pd(rjy[j]);
-         rjz_tmp = _mm256_set1_pd(rjz[j]);
-         eps_tmp = _mm256_set1_pd(eps[j]);
-         dx_tmp = _mm256_sub_pd(rix_tmp, rjx_tmp);
[…]

### 2024-02-20 dsl/experiment/Nbody/pikg_check.cpp

@@ -1,0 +1,41 @@
+#include<stdio.h>
+#include<pikg_vector.h>
+#include<pikg_vector.hpp>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+
+struct EPI {
+   pikg_f64vec3 r;
+};
+
+struct EPJ{
+   pikg_f64vec3 r;
+   double m;
+   double eps;
+};
+
+struct FORCE {
+   pikg_f64vec3 acc;
+};
+
+#include "pikg_kernel_AVX2.hpp"
+// #include "pyker_kernel_AVX2.hpp"
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n = 0;
+   std::cin >>  n;
+   //PIKG用のコード
+   const int nepi = n; 
+   const int nepj = n; 
+   EPI *epi = new EPI[nepi];
+   EPJ *epj = new EPJ[nepj];
+   FORCE *force = new FORCE[n];
+   Kernel pikg_kernel;
+   pikg_kernel(epi, nepi, epj, nepj, force);
+}

### 2024-02-20 dsl/experiment/Nbody/pyker_check.cpp

@@ -1,0 +1,18 @@
+#include<stdio.h>
+#include<cstdlib> // 乱数生成のために必要
+#include<ctime> // 乱数のシード設定のために必要
+// #include<algorithm>
+#include<cmath>
+#include<time.h>
+#include<iostream>
+
+#include "pyker_kernel_AVX2.hpp"
+
+int main() {
+   srand((unsigned)time(NULL)); // 乱数のシードを設定
+
+   int n = 0;
+   std::cin >>  n;
+   //PIKG用のコード
+
+}

### 2024-02-20 dsl/experiment/Nbody/pyker_kernel_AVX2.hpp

@@ -46,12 +46,14 @@ int kernel(int n, double ri[][3], double rj[][3], double mass[], double eps2[], 
          rij_tmp_v0 = _mm256_sub_pd(ri_tmp_v0, rj_tmp_v0);
          rij_tmp_v1 = _mm256_sub_pd(ri_tmp_v1, rj_tmp_v1);
          rij_tmp_v2 = _mm256_sub_pd(ri_tmp_v2, rj_tmp_v2);
-         
-         r2_tmp = _mm256_add_pd(eps2_tmp, _mm256_add_pd(_mm256_add_pd(
+         r2_tmp = _mm256_add_pd(eps2_tmp, 
+         _mm256_add_pd(
+            _mm256_add_pd(
                                  _mm256_mul_pd(rij_tmp_v0, rij_tmp_v0), 
                                  _mm256_mul_pd(rij_tmp_v1, rij_tmp_v1)), 
                                  _mm256_mul_pd(rij_tmp_v2, rij_tmp_v2)));
-         r_inv_tmp = _mm256_div_pd(float_0_tmp, _mm256_sqrt_pd(r2_tmp));
+         r_inv_tmp = _mm256_div_pd(float_0_tmp, 
+         _mm256_sqrt_pd(r2_tmp));
          r2_inv_tmp = _mm256_mul_pd(r_inv_tmp, r_inv_tmp);
          mr_inv_tmp = _mm256_mul_pd(mass_tmp, r_inv_tmp);
          mr3_inv_tmp = _mm256_mul_pd(mr_inv_tmp, r2_inv_tmp);

### 2024-02-20 dsl/experiment/harp_pyker_code.hpp

@@ -1,41 +1,0 @@
-#include<math.h>
-;
-int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
-   int i;
-   int j;
-   double dr_v0;
-   double dr_v1;
-   double dr_v2;
-   double dv_v0;
-   double dv_v1;
-   double dv_v2;
-   double r2;
-   double rv;
-   double af;
-   double jf;
-   for (i = 0; i < n; i += 1) {
-      ;
-      ;
-      for (j = 0; j < n; j += 1) {
-         ;
-         dr_v0 = ri[i][0] - rj[j][0];
-         dr_v1 = ri[i][1] - rj[j][1];
-         dr_v2 = ri[i][2] - rj[j][2];
-         dv_v0 = vi[i][0] - vj[j][0];
-         dv_v1 = vi[i][1] - vj[j][1];
-         dv_v2 = vi[i][2] - vj[j][2];
-         r2 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
-         rv = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
-         af = mj[j]/((sqrt(r2)*(sqrt(r2)*sqrt(r2))));
-         jf = ((3.0*mj[j])*rv)/((sqrt(r2)*(sqrt(r2)*(sqrt(r2)*(sqrt(r2)*sqrt(r2))))));
-         F[i][0] += af*dr_v0;
-         F[i][1] += af*dr_v1;
-         F[i][2] += af*dr_v2;
-         J[i][0] += af*dv_v0 - dr_v0*jf;
-         J[i][1] += af*dv_v1 - dr_v1*jf;
-         J[i][2] += af*dv_v2 - dr_v2*jf;
-      };
-      ;
-   };
-   return 0;
-};

### 2024-02-20 dsl/experiment/harp_pyker_simdcode.hpp

@@ -1,115 +1,0 @@
-#include<math.h>
-#include<x86intrin.h>;
-int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3], double mj[], double eps2[], double F[][3], double J[][3]){
-   int i;
-   int j;
-   __m256d ri_tmp_v0;
-   __m256d ri_tmp_v1;
-   __m256d ri_tmp_v2;
-   __m256d vi_tmp_v0;
-   __m256d vi_tmp_v1;
-   __m256d vi_tmp_v2;
-   __m256d rj_tmp_v0;
-   __m256d rj_tmp_v1;
-   __m256d rj_tmp_v2;
-   __m256d vj_tmp_v0;
-   __m256d vj_tmp_v1;
-   __m256d vj_tmp_v2;
-   __m256d mj_tmp;
-   __m256d eps2_tmp;
-   __m256d F_tmp_v0;
-   __m256d F_tmp_v1;
-   __m256d F_tmp_v2;
-   __m256d J_tmp_v0;
-   __m256d J_tmp_v1;
-   __m256d J_tmp_v2;
-   __m256d float_0_tmp;
-   float_0_tmp = _mm256_set1_pd(3.0);
-   __m256d dr_tmp_v0;
-   __m256d dr_tmp_v1;
-   __m256d dr_tmp_v2;
-   __m256d dv_tmp_v0;
-   __m256d dv_tmp_v1;
-   __m256d dv_tmp_v2;
-   __m256d r2_tmp;
-   __m256d rv_tmp;
-   __m256d af_tmp;
-   __m256d jf_tmp;
-   for (i = 0; i < n; i += 4) {
-      int index_gather_0[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
-      ri_tmp_v0 = _mm256_i32gather_pd(&ri[i][0], vindex_gather_0, 8);
-      int index_gather_1[4] = {0, 3, 6, 9};
-      __m128i vindex_gather_1 = _mm_load_si128((const __m128i*)index_gather_1);
-      ri_tmp_v1 = _mm256_i32gather_pd(&ri[i][1], vindex_gather_1, 8);
[…]

### 2024-02-20 dsl/experiment/tmp/harp_pyker_code.hpp

@@ -26,7 +26,7 @@ int kernel(int n, double ri[][3], double vi[][3], double rj[][3], double vj[][3]
          dv_v2 = vi[i][2] - vj[j][2];
          r2 = eps2[j] + (dr_v2*dr_v2 + (dr_v0*dr_v0 + dr_v1*dr_v1));
          rv = dr_v2*dv_v2 + (dr_v0*dv_v0 + dr_v1*dv_v1);
-         af = mj[j]/(sqrt(r2)*(sqrt(r2)*sqrt(r2)));
+         af = mj[j]/((sqrt(r2)*(sqrt(r2)*sqrt(r2))));
          jf = ((3.0*mj[j])*rv)/((sqrt(r2)*(sqrt(r2)*(sqrt(r2)*(sqrt(r2)*sqrt(r2))))));
          F[i][0] += af*dr_v0;
          F[i][1] += af*dr_v1;

### 2024-02-20 dsl/gen/gravity_code.hpp

@@ -25,8 +25,7 @@ int kernel(int n, double xi[][3], double yi[][3], double f[]){
          yi_tmp_v0 = _mm256_set1_pd(yi[j][0]);
          yi_tmp_v1 = _mm256_set1_pd(yi[j][1]);
          yi_tmp_v2 = _mm256_set1_pd(yi[j][2]);
-         f_tmp += _mm256_add_pd(_mm256_add_pd(_mm256_mul_pd(xi_tmp_v0, yi_tmp_v0),
-          _mm256_mul_pd(xi_tmp_v1, yi_tmp_v1)), _mm256_mul_pd(xi_tmp_v2, yi_tmp_v2));
+         f_tmp += _mm256_add_pd(xi_tmp_v0, yi_tmp_v0);
       };
       _mm256_store_pd(&f[i], f_tmp);
    };

### 2024-02-20 paper/giji_code.cpp

@@ -1,0 +1,14 @@
+
+int main() {
+
+   //preprocess
+   for(int i = 0;i < N;i += p_wide) {
+      // load part      
+      for(int j = 0;j < N;j += 1) {
+         //culc part
+      }
+      // store part 
+   }
+
+
+}
